### 2021-03-31 README.Rmd
First commit

---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Code for Look-Ahead Screening Rules Paper

<!-- badges: start -->
[![R-CMD-check](https://github.com/jolars/LookAheadScreening/workflows/R-CMD-check/badge.svg)](https://github.com/jolars/HessianScreening/actions)
<!-- badges: end -->

### 2021-03-31 figures/simulateddata-gaussian-timings.tex
First commit

% Created by tikzDevice version 0.12.3.1 on 2021-03-25 18:09:52
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (361.35,216.81);
\begin{scope}
\path[clip] ( 49.82,145.50) rectangle ( 62.48,188.62);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 49.82,152.46) --
	( 62.48,152.46);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 49.82,162.45) --
	( 62.48,162.45);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 49.82,172.44) --
	( 62.48,172.44);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 49.82,182.43) --
	( 62.48,182.43);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 49.82,147.46) --
	( 62.48,147.46);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 49.82,157.45) --
	( 62.48,157.45);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 49.82,167.44) --
	( 62.48,167.44);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 49.82,177.43) --
	( 62.48,177.43);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 49.82,187.42) --
	( 62.48,187.42);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 53.27,145.50) --
	( 53.27,188.62);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 59.02,145.50) --
	( 59.02,188.62);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] ( 50.68,147.46) rectangle ( 51.98,153.73);
\definecolor{fillColor}{RGB}{230,159,0}

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] ( 51.98,147.46) rectangle ( 53.27,161.62);
\definecolor{fillColor}{RGB}{86,180,233}

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] ( 53.27,147.46) rectangle ( 54.57,152.98);
\definecolor{fillColor}{RGB}{0,158,115}

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] ( 54.57,147.46) rectangle ( 55.86,152.30);
\definecolor{fillColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] ( 56.44,147.46) rectangle ( 57.73,157.34);
\definecolor{fillColor}{RGB}{230,159,0}

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] ( 57.73,147.46) rectangle ( 59.02,168.64);
\definecolor{fillColor}{RGB}{86,180,233}

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] ( 59.02,147.46) rectangle ( 60.32,153.70);
\definecolor{fillColor}{RGB}{0,158,115}

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] ( 60.32,147.46) rectangle ( 61.61,154.29);
\end{scope}
\begin{scope}
\path[clip] ( 67.98,145.50) rectangle ( 80.64,188.62);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 67.98,152.46) --
	( 80.64,152.46);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 67.98,162.45) --
	( 80.64,162.45);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 67.98,172.44) --
	( 80.64,172.44);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 67.98,182.43) --
	( 80.64,182.43);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 67.98,147.46) --
	( 80.64,147.46);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 67.98,157.45) --
	( 80.64,157.45);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 67.98,167.44) --
	( 80.64,167.44);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 67.98,177.43) --
	( 80.64,177.43);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 67.98,187.42) --
	( 80.64,187.42);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 71.43,145.50) --
	( 71.43,188.62);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 77.18,145.50) --
	( 77.18,188.62);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] ( 68.84,147.46) rectangle ( 70.13,154.10);
\definecolor{fillColor}{RGB}{230,159,0}

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] ( 70.13,147.46) rectangle ( 71.43,157.79);
\definecolor{fillColor}{RGB}{86,180,233}

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] ( 71.43,147.46) rectangle ( 72.72,153.68);
\definecolor{fillColor}{RGB}{0,158,115}

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] ( 72.72,147.46) rectangle ( 74.02,153.22);
\definecolor{fillColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] ( 74.59,147.46) rectangle ( 75.89,186.66);
\definecolor{fillColor}{RGB}{230,159,0}

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] ( 75.89,147.46) rectangle ( 77.18,182.81);
\definecolor{fillColor}{RGB}{86,180,233}

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] ( 77.18,147.46) rectangle ( 78.48,156.30);
\definecolor{fillColor}{RGB}{0,158,115}

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] ( 78.48,147.46) rectangle ( 79.77,173.60);
\end{scope}
\begin{scope}
\path[clip] ( 49.82,188.62) rectangle ( 62.48,205.89);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 56.15,194.22) {100 x 10000};
\end{scope}
\begin{scope}
\path[clip] ( 67.98,188.62) rectangle ( 80.64,205.89);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 74.31,194.22) {10000 x 100};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 53.27,134.49) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 59.02,134.49) {0.5};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 71.43,134.49) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 77.18,134.49) {0.5};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 44.87,144.43) {0.00};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 44.87,154.42) {0.25};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 44.87,164.41) {0.50};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 44.87,174.40) {0.75};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 44.87,184.39) {1.00};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 65.23,121.75) {rho};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 22.11,167.06) {meantime};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 97.14,200.71) {Screening};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] ( 97.85,177.19) rectangle (113.77,193.11);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{230,159,0}

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] ( 97.85,159.84) rectangle (113.77,175.77);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{86,180,233}

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] ( 97.85,142.50) rectangle (113.77,158.42);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{0,158,115}

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] ( 97.85,125.15) rectangle (113.77,141.08);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (119.98,182.12) {EDPP};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (119.98,164.77) {Gap-Safe};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (119.98,147.43) {Hessian};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (119.98,130.08) {Working};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.40] at ( 47.73,202.32) {\bfseries normal vision};
\end{scope}
\begin{scope}
\path[clip] (230.49,145.50) rectangle (243.15,188.62);
\definecolor{drawColor}{RGB}{233,233,233}

\path[draw=drawColor,line width= 0.3pt,line join=round] (230.49,152.46) --
	(243.15,152.46);

\path[draw=drawColor,line width= 0.3pt,line join=round] (230.49,162.45) --
	(243.15,162.45);

\path[draw=drawColor,line width= 0.3pt,line join=round] (230.49,172.44) --
	(243.15,172.44);

\path[draw=drawColor,line width= 0.3pt,line join=round] (230.49,182.43) --
	(243.15,182.43);

\path[draw=drawColor,line width= 0.6pt,line join=round] (230.49,147.46) --
	(243.15,147.46);

\path[draw=drawColor,line width= 0.6pt,line join=round] (230.49,157.45) --
	(243.15,157.45);

\path[draw=drawColor,line width= 0.6pt,line join=round] (230.49,167.44) --
	(243.15,167.44);

\path[draw=drawColor,line width= 0.6pt,line join=round] (230.49,177.43) --
	(243.15,177.43);

\path[draw=drawColor,line width= 0.6pt,line join=round] (230.49,187.42) --
	(243.15,187.42);

\path[draw=drawColor,line width= 0.6pt,line join=round] (233.95,145.50) --
	(233.95,188.62);

\path[draw=drawColor,line width= 0.6pt,line join=round] (239.70,145.50) --
	(239.70,188.62);
\definecolor{drawColor}{RGB}{44,44,44}
\definecolor{fillColor}{RGB}{44,44,44}

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (231.36,147.46) rectangle (232.65,153.73);
\definecolor{fillColor}{RGB}{183,183,34}

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (232.65,147.46) rectangle (233.95,161.62);
\definecolor{fillColor}{RGB}{160,160,232}

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (233.95,147.46) rectangle (235.24,152.98);
\definecolor{fillColor}{RGB}{137,137,121}

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (235.24,147.46) rectangle (236.54,152.30);
\definecolor{fillColor}{RGB}{44,44,44}

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (237.11,147.46) rectangle (238.41,157.34);
\definecolor{fillColor}{RGB}{183,183,34}

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (238.41,147.46) rectangle (239.70,168.64);
\definecolor{fillColor}{RGB}{160,160,232}

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (239.70,147.46) rectangle (240.99,153.70);
\definecolor{fillColor}{RGB}{137,137,121}

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (240.99,147.46) rectangle (242.29,154.29);
\end{scope}
\begin{scope}
\path[clip] (248.65,145.50) rectangle (261.31,188.62);
\definecolor{drawColor}{RGB}{233,233,233}

\path[draw=drawColor,line width= 0.3pt,line join=round] (248.65,152.46) --
	(261.31,152.46);

\path[draw=drawColor,line width= 0.3pt,line join=round] (248.65,162.45) --
	(261.31,162.45);

\path[draw=drawColor,line width= 0.3pt,line join=round] (248.65,172.44) --
	(261.31,172.44);

\path[draw=drawColor,line width= 0.3pt,line join=round] (248.65,182.43) --
	(261.31,182.43);

\path[draw=drawColor,line width= 0.6pt,line join=round] (248.65,147.46) --
	(261.31,147.46);

\path[draw=drawColor,line width= 0.6pt,line join=round] (248.65,157.45) --
	(261.31,157.45);

\path[draw=drawColor,line width= 0.6pt,line join=round] (248.65,167.44) --
	(261.31,167.44);

\path[draw=drawColor,line width= 0.6pt,line join=round] (248.65,177.43) --
	(261.31,177.43);

\path[draw=drawColor,line width= 0.6pt,line join=round] (248.65,187.42) --
	(261.31,187.42);

\path[draw=drawColor,line width= 0.6pt,line join=round] (252.10,145.50) --
	(252.10,188.62);

\path[draw=drawColor,line width= 0.6pt,line join=round] (257.86,145.50) --
	(257.86,188.62);
\definecolor{drawColor}{RGB}{44,44,44}
\definecolor{fillColor}{RGB}{44,44,44}

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (249.52,147.46) rectangle (250.81,154.10);
\definecolor{fillColor}{RGB}{183,183,34}

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (250.81,147.46) rectangle (252.10,157.79);
\definecolor{fillColor}{RGB}{160,160,232}

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (252.10,147.46) rectangle (253.40,153.68);
\definecolor{fillColor}{RGB}{137,137,121}

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (253.40,147.46) rectangle (254.69,153.22);
\definecolor{fillColor}{RGB}{44,44,44}

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (255.27,147.46) rectangle (256.56,186.66);
\definecolor{fillColor}{RGB}{183,183,34}

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (256.56,147.46) rectangle (257.86,182.81);
\definecolor{fillColor}{RGB}{160,160,232}

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (257.86,147.46) rectangle (259.15,156.30);
\definecolor{fillColor}{RGB}{137,137,121}

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (259.15,147.46) rectangle (260.45,173.60);
\end{scope}
\begin{scope}
\path[clip] (230.49,188.62) rectangle (243.15,205.89);
\definecolor{drawColor}{RGB}{49,49,49}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (236.82,194.22) {100 x 10000};
\end{scope}
\begin{scope}
\path[clip] (248.65,188.62) rectangle (261.31,205.89);
\definecolor{drawColor}{RGB}{49,49,49}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (254.98,194.22) {10000 x 100};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
\definecolor{drawColor}{RGB}{85,85,85}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (233.95,134.49) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (239.70,134.49) {0.5};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
\definecolor{drawColor}{RGB}{85,85,85}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (252.10,134.49) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (257.86,134.49) {0.5};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
\definecolor{drawColor}{RGB}{85,85,85}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (225.54,144.43) {0.00};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (225.54,154.42) {0.25};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (225.54,164.41) {0.50};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (225.54,174.40) {0.75};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (225.54,184.39) {1.00};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
\definecolor{drawColor}{RGB}{44,44,44}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (245.90,121.75) {rho};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
\definecolor{drawColor}{RGB}{44,44,44}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (202.78,167.06) {meantime};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
\definecolor{drawColor}{RGB}{44,44,44}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.10] at (277.81,200.71) {Screening};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
\definecolor{drawColor}{RGB}{44,44,44}
\definecolor{fillColor}{RGB}{44,44,44}

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (278.52,177.19) rectangle (294.44,193.11);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
\definecolor{drawColor}{RGB}{44,44,44}
\definecolor{fillColor}{RGB}{183,183,34}

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (278.52,159.84) rectangle (294.44,175.77);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
\definecolor{drawColor}{RGB}{44,44,44}
\definecolor{fillColor}{RGB}{160,160,232}

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (278.52,142.50) rectangle (294.44,158.42);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
\definecolor{drawColor}{RGB}{44,44,44}
\definecolor{fillColor}{RGB}{137,137,121}

\path[draw=drawColor,line width= 0.6pt,line cap=rect,fill=fillColor] (278.52,125.15) rectangle (294.44,141.08);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
\definecolor{drawColor}{RGB}{44,44,44}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (300.66,182.12) {EDPP};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
\definecolor{drawColor}{RGB}{44,44,44}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (300.66,164.77) {Gap-Safe};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
\definecolor{drawColor}{RGB}{44,44,44}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (300.66,147.43) {Hessian};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
\definecolor{drawColor}{RGB}{44,44,44}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (300.66,130.08) {Working};
\end{scope}
\end{tikzpicture}

### 2021-03-31 R/LookAheadScreening-package.R

@@ -1,0 +1,10 @@
+#' @keywords internal
+"_PACKAGE"
+
+# The following block is used by usethis to automatically manage
+# roxygen namespace tags. Modify with care!
+## usethis namespace: start
+#' @useDynLib LookAheadScreening, .registration = TRUE
+#' @importFrom Rcpp sourceCpp
+## usethis namespace: end
+NULL

### 2021-03-31 R/RcppExports.R

@@ -1,0 +1,11 @@
+# Generated by using Rcpp::compileAttributes() -> do not edit by hand
+# Generator token: 10BE3573-1514-4C36-9D1C-5A225CD40393
+
+lassoPathDense <- function(X, y, family, standardize, screening_type, path_length, maxit, tol_infeas, tol_gap, gamma, force_kkt_check, line_search, verbosity) {
+    .Call(`_LookAheadScreening_lassoPathDense`, X, y, family, standardize, screening_type, path_length, maxit, tol_infeas, tol_gap, gamma, force_kkt_check, line_search, verbosity)
+}
+
+lassoPathSparse <- function(X, y, family, standardize, screening_type, path_length, maxit, tol_infeas, tol_gap, gamma, force_kkt_check, line_search, verbosity) {
+    .Call(`_LookAheadScreening_lassoPathSparse`, X, y, family, standardize, screening_type, path_length, maxit, tol_infeas, tol_gap, gamma, force_kkt_check, line_search, verbosity)
+}
+

### 2021-03-31 R/data.R

@@ -1,0 +1,15 @@
+#' Heart Disease
+#'
+"heart"
+
+#' Leukemia
+#'
+"leukemia"
+
+#' Colon Cancer
+#'
+"colon_cancer"
+
+#' Cpusmall
+#'
+"cpusmall"

### 2021-03-31 R/generateDesign.R

@@ -1,0 +1,79 @@
+#' Generate Response and Design Matrix
+#'
+#' @param n Number of observations
+#' @param p Number of predictors
+#' @param family Response type
+#' @param density Density of design matrix
+#' @param rho Correlation between predictors (corresponding to choice in `rho_type`)
+#' @param s Number of signals (nonzero coefficients)
+#' @param rho_type Type of correlation between predictors. `"constant"` gives uniform
+#'   correlation between all predictors. `"auto"` means that predictors are
+#'   "autocorrelated" with adjacent predictors by the amount specified in `rho`.
+#' @param beta_type Type of coefficients to generate
+#' @param snr Signal-to-noise ratio
+#'
+#' @return A list with `X`: the design matrix, and `y`: the response.
+#' @export
+generateDesign <- function(n,
+                           p,
+                           family = c("gaussian", "binomial"),
+                           density = 1,
+                           rho = 0,
+                           s = 5,
+                           rho_type = c("constant", "auto"),
+                           beta_type = 1,
+                           snr = 2) {
+  family <- match.arg(family)
+  rho_type <- match.arg(rho_type)
+
+  s <- min(s, p)
+  beta <- double(p)
+
+  if (density != 1 && rho > 0) {
+    stop("when density != 1, 'rho' must be 0")
+  }
+
+  if (beta_type == 1) {
+    ind <- round(seq(1, p, length.out = s))
+    beta[ind] <- 1
+  } else if (beta_type == 2) {
+    beta[1:s] <- 1
+  } else if (beta_type == 3) {
+    beta[1:s] <- seq(10, 0.5, length = s)
+  } else if (beta_type == 4) {
+    beta[1:s] <- 1
+    beta[(s + 1):p] <- 0.5^(1:(p - s))
+  }
+
+  if (density == 1) {
+    X <- matrix(rnorm(n * p), n)
+  } else {
+    X <- Matrix::rsparsematrix(n, p, density)
+  }
+
+  if (rho != 0) {
+    if (rho_type == "auto") {
+      inds <- 1:p
+      Sigma <- rho^abs(outer(inds, inds, "-"))
+      U <- chol(Sigma)
+
+      X <- X %*% t(U)
+      sigma <- sqrt((t(beta) %*% Sigma %*% beta) / snr)
[…]

### 2021-03-31 R/lassoPath.R

@@ -1,0 +1,80 @@
+#' Lasso Path with Hessian Screening Rules
+#'
+#' @param X The predictor matrix
+#' @param y The reponse vector
+#' @param family The name of the family, "gaussian" or "logistic"
+#' @param standardize Whether to standardize the predictors
+#' @param screening_type Screening rule
+#' @param path_length The (desired) length of the lasso path
+#' @param maxit Maximum number of iterations for Coordinate Descent loop
+#' @param tol_infeas Tolerance threshold for maximum infeasibility
+#' @param tol_gap Tolerance threshold for duality gap
+#' @param gamma Percent of strong approximation to add to Hessian approximation
+#' @param force_kkt_check Whether to force KKT checks even when screening rule
+#'   is safe
+#' @param line_search Use line search when `family = "binomial"`
+#' @param verbosity Controls the level of verbosity. 0 = no output.
+#'
+#' @export
+lassoPath <- function(X,
+                      y,
+                      family = c("gaussian", "binomial"),
+                      standardize = TRUE,
+                      screening_type = c(
+                        "working",
+                        "edpp",
+                        "gap_safe",
+                        "strong"
+                      ),
+                      path_length = 100L,
+                      maxit = 1e5,
+                      tol_infeas = 1e-3,
+                      tol_gap = 1e-4,
+                      gamma = 0.01,
+                      force_kkt_check = FALSE,
+                      line_search = TRUE,
+                      verbosity = 0) {
+  family <- match.arg(family)
+  screening_type <- match.arg(screening_type)
+
+  sparse <- inherits(X, "sparseMatrix")
+
+  n <- nrow(X)
+  p <- ncol(X)
+
+  if (sparse) {
+    X <- as(X, "dgCMatrix")
+
+    lassoPathSparse(
+      X,
+      y,
+      family,
+      standardize,
+      screening_type,
+      path_length,
+      maxit,
+      tol_infeas,
+      tol_gap,
+      gamma,
+      force_kkt_check,
+      line_search,
+      verbosity
+    )
+  } else {
+    lassoPathDense(
+      X,
+      y,
+      family,
+      standardize,
+      screening_type,
+      path_length,
+      maxit,
+      tol_infeas,
+      tol_gap,
+      gamma,
+      force_kkt_check,
+      line_search,
+      verbosity
+    )
+  }
+}

### 2021-03-31 data-raw/arcene.R

@@ -1,0 +1,29 @@
+library(Matrix)
+
+data <- tempfile()
+labels <- tempfile()
+
+download.file(
+  "https://statweb.stanford.edu/~tibs/strong/realdata/arcene_train.data",
+  data
+)
+
+d <- scan(data, sep = " ")
+
+x <- matrix(d, nrow = 100, byrow = TRUE)[, 1:10000]
+x <- Matrix(x, sparse = TRUE)
+
+download.file(
+  "https://statweb.stanford.edu/~tibs/strong/realdata/arcene_train.labels",
+  labels
+)
+
+y <- scan(labels, sep = " ")
+y <- (y + 1) / 2
+
+arcene <- list(X = x, y = y)
+
+saveRDS(arcene, "data/arcene.rds")
+
+unlink(labels)
+unlink(data)

### 2021-03-31 data-raw/dorothea.R

@@ -1,0 +1,57 @@
+library(Matrix)
+
+tmp_data <- tempfile()
+tmp_labels <- tempfile()
+
+download.file(
+  "https://statweb.stanford.edu/~tibs/strong/realdata/dorothea_train.data",
+  tmp_data
+)
+
+download.file(
+  "https://statweb.stanford.edu/~tibs/strong/realdata/dorothea_train.labels",
+  tmp_labels
+)
+
+d <- readLines(tmp_data, n = 800)
+
+makevec <- function(d) {
+  j <- 1
+  j0 <- 1
+  nn <- nchar(d)
+  xx <- NULL
+  while (j < nn) {
+    while (substring(d, j, j) != " ") {
+      j <- j + 1
+    }
+    xx <- c(xx, as.numeric(substring(d, j0, j - 1)))
+    j0 <- j + 1
+    j <- j + 1
+  }
+  xx
+}
+
+y <- makevec(d[1])
+
+x <- matrix(0,
+  nrow = 800,
+  ncol = 100000,
+  byrow = TRUE
+)
+
+for (i in 1:800) {
+  o <- makevec(d[i])
+  x[i, o] <- 1
+}
+
+oo <- colSums(x)
+x <- x[, oo > 0]
+
+dy <- scan(tmp_labels, sep = " ")
+y <- (dy + 1) / 2
+
+X <- Matrix::Matrix(x)
+
+dorothea <- list(X = X, y = y)
+
+saveRDS(dorothea, "data/dorothea.rds")

### 2021-03-31 data-raw/libsvm-data.R

@@ -1,0 +1,106 @@
+readLIBSVM <- function(file) {
+  dat <- data.table::fread(file,
+    sep = "\n",
+    header = FALSE,
+    showProgress = FALSE
+  )[[1]]
+
+  l <- stringi::stri_split_regex(dat, "[ ]+")
+
+  y <- as.numeric(vapply(l, "[", 1, FUN.VALUE = character(1)))
+
+  vals <- do.call(rbind, lapply(l, function(x) {
+    do.call(rbind, stringi::stri_split_fixed(x[-1], ":"))
+  }))
+
+  row_ind <- rep(seq_len(length(l)), times = lengths(l) - 1)
+  col_ind <- as.integer(vals[, 1])
+
+  X <- Matrix::sparseMatrix(row_ind, col_ind, x = as.numeric(vals[, 2]))
+
+  density <- Matrix::nnzero(X) / length(X)
+
+  if (density > 0.5) {
+    X <- as.matrix(X)
+  }
+
+  if (length(unique(y)) == 2) {
+    y <- as.numeric(as.factor(y)) - 1
+  }
+
+  list(X = X, y = y)
+}
+
+# getLibsvmData <- function(url) {
+#   is_bz2 <- grepl(".bz2$", url)
+
+#   tmp_file <- tempfile(fileext = if (is_bz2) ".bz2" else "")
+
+#   download.file(url, tmp_file, quiet = TRUE)
+
+#   readLIBSVM(tmp_file)
+# }
+
+datafiles <- c(
+  "abalone" = "https://www.csie.ntu.edu.tw/~cjlin/libsvmtools/datasets/regression/abalone",
+  "cadata" = "https://www.csie.ntu.edu.tw/~cjlin/libsvmtools/datasets/regression/cadata",
+  "colon-cancer" = "https://www.csie.ntu.edu.tw/~cjlin/libsvmtools/datasets/binary/colon-cancer.bz2",
+  "covtype" = "https://www.csie.ntu.edu.tw/~cjlin/libsvmtools/datasets/binary/covtype.libsvm.binary.bz2",
+  "diabetes" = "https://www.csie.ntu.edu.tw/~cjlin/libsvmtools/datasets/binary/diabetes",
+  "duke-breast-cancer" = "https://www.csie.ntu.edu.tw/~cjlin/libsvmtools/datasets/binary/duke.bz2",
[…]

### 2021-03-31 data-raw/package-libsvm-data.R

@@ -1,0 +1,53 @@
+readLIBSVM <- function(file) {
+  dat <- data.table::fread(file, sep = "\n", header = FALSE)[[1]]
+
+  l <- stringi::stri_split_regex(dat, "[ ]+")
+
+  y <- as.numeric(vapply(l, "[", 1, FUN.VALUE = character(1)))
+
+  vals <- do.call(rbind, lapply(l, function(x) {
+    do.call(rbind, stringi::stri_split_fixed(x[-1], ":"))
+  }))
+
+  row_ind <- rep(seq_len(length(l)), times = lengths(l) - 1)
+  col_ind <- as.integer(vals[, 1])
+
+  X <- Matrix::sparseMatrix(row_ind, col_ind, x = as.numeric(vals[, 2]))
+
+  density <- Matrix::nnzero(X) / length(X)
+
+  if (density > 0.5) {
+    X <- as.matrix(X)
+  }
+
+  if (length(unique(y)) == 2) {
+    y <- as.numeric(as.factor(y)) - 1
+  }
+
+  list(X = X, y = y)
+}
+
+getLibsvmData <- function(url) {
+  is_bz2 <- grepl(".bz2$", url)
+
+  tmp_file <- tempfile(fileext = if (is_bz2) ".bz2" else "")
+
+  download.file(url, tmp_file, quiet = TRUE)
+
+  readLIBSVM(tmp_file)
+}
+
+colon_cancer <- getLibsvmData(
+  "https://www.csie.ntu.edu.tw/~cjlin/libsvmtools/datasets/binary/colon-cancer.bz2"
+)
+cpusmall <- getLibsvmData(
+  "https://www.csie.ntu.edu.tw/~cjlin/libsvmtools/datasets/regression/cpusmall"
+)
+heart <- getLibsvmData(
+  "https://www.csie.ntu.edu.tw/~cjlin/libsvmtools/datasets/binary/heart"
+)
+leukemia <- getLibsvmData(
+  "https://www.csie.ntu.edu.tw/~cjlin/libsvmtools/datasets/binary/leu.t.bz2"
+)
+
+usethis::use_data(colon_cancer, cpusmall, heart, leukemia, overwrite = TRUE)

### 2021-03-31 experiments/arcenegolub_experiment.R

@@ -1,0 +1,72 @@
+#rm(list = ls())
+#graphics.off()
+library(HessianScreening)
+
+
+#d <- readRDS(file.path("data", paste0("leukemia-train", ".rds")))
+#d <- readRDS(file.path("data", paste0("arcene", ".rds")))
+#d <- readRDS(file.path("data", paste0("dorothea", ".rds")))
+#d <- readRDS(file.path("data", paste0("covtype", ".rds")))
+d <- readRDS(file.path("data", paste0("gisette-train", ".rds")))
+
+X <- d$X
+y <- d$y
+family <- "binomial"
+fita <- lassoPath(
+    X,
+    y,
+    family = family,
+    screening_type = "hessian",
+    hessian_warm_starts = TRUE,
+    log_hessian_update_type = "approx",
+    gamma = 0.01,
+    verify_hessian = FALSE,
+    verbosity = 0
+)
+fitf <- lassoPath(
+    X,
+    y,
+    family = family,
+    screening_type = "hessian",
+    hessian_warm_starts = TRUE,
+    log_hessian_update_type = "full",
+    gamma = 0.01,
+    verify_hessian = FALSE,
+    verbosity = 0
+)
+fit.w <- lassoPath(
+    X,
+    y,
+    family = family,
+    screening_type = "working",
+    verbosity = 0
+)
+cat("***************\n")
+cat("hessian:\n")
+cat("full = ", fit$full_time, "\n")
+cat("cd_time = ", sum(fit$cd_time), "\n")
+cat("kkt_time = ", sum(fit$corr_time), "\n")
+cat("hess_time = ", sum(fit$hess_time), "\n")
+cat("gradcorr_time", sum(fit$gradcorr_time), "\n")
+cat("duplicates_time", sum(fit$duplicates_time), "\n")
+cat("***************\n")
+# cat("working:\n")
+cat("full = ", fit.w$full_time, "\n")
+cat("cd_time = ", sum(fit.w$cd_time), "\n")
+cat("kkt_time = ", sum(fit.w$kkt_time), "\n")
+cat("duplicates_time", sum(fit$duplicates_time), "\n")
+
+par(mfrow=c(2,2))
+plot(fit$active, type = "l", lty = 2, ylim = c(0, max(c(fit$active, fit$screened))))
+lines(fit$screened)
+
+plot(fit$cd_time, type = "l")
+lines(fit.w$cd_time, col = "red")
[…]

### 2021-03-31 experiments/logistic-hessian-updates.R

@@ -1,0 +1,152 @@
+library(HessianScreening)
+
+n <- 2000
+p <- 10000
+rho <- 0.4
+dens <- 1
+
+d <-
+  generateDesign(n,
+                 p,
+                 family = "binomial",
+                 rho = rho,
+                 density = dens)
+
+X <- d$X
+y <- d$y
+
+fit_auto <-
+  lassoPath(
+    X,
+    y,
+    family = "binomial",
+    screening_type = "hessian",
+    log_hessian_update_type = "auto",
+    log_hessian_auto_threshold = ceiling(dens*min(n, p)),
+    verbosity = 0
+  )
+fit_full <-
+  lassoPath(
+    X,
+    y,
+    family = "binomial",
+    screening_type = "hessian",
+    log_hessian_update_type = "full"
+  )
+fit_approx <-
+  lassoPath(
+    X,
+    y,
+    family = "binomial",
+    screening_type = "hessian",
+    log_hessian_update_type = "approx"
+  )
+fit_working <-
+  lassoPath(X,
+            y,
+            family = "binomial",
+            screening_type = "working")
+
+fit_auto$full_time
+fit_full$full_time
+fit_approx$full_time
+fit_working$full_time
+
+library(tikzDevice)
+tikz("log-hessian.pdf")
+par(mfrow = c(2, 2))
+
+plot(
+  fit_auto$passes,
+  type = "l",
+  ylab = "passes",
+  ylim = c(
+    0,
+    max(
+      fit_full$passes,
+      fit_approx$passes,
+      fit_auto$passes,
+      fit_working$passes
+    )
+  )
+)
+lines(fit_full$passes, col = "dark orange")
+lines(fit_approx$passes, col = "aquamarine3")
+lines(fit_working$passes, col = "magenta")
+legend(
+  "topleft",
+  legend = c("auto", "full", "approx", "working"),
+  lwd = c(1, 1, 1, 1),
+  col = c("black", "dark orange", "aquamarine3", "magenta")
+)
+
+plot(
+  fit_auto$it_time,
+  type = "l",
+  ylab = "iteration time",
+  ylim = c(0, max(
+    c(fit_auto$it_time, fit_full$it_time, fit_approx$it_time)
+  ))
+)
+lines(fit_full$it_time, col = "dark orange")
+lines(fit_approx$it_time, col = "aquamarine3")
[…]

### 2021-03-31 experiments/realdata.R

@@ -1,0 +1,93 @@
+library(HessianScreening)
+library(tidyr)
+library(tibble)
+library(Matrix)
+
+printf <- function(...) invisible(cat(sprintf(...)))
+
+datasets <- c(
+  "arcene",
+  "cadata",
+  "dorothea",
+  "gisette-train",
+  "colon-cancer",
+  "leukemia-train",
+  "ijcnn1-train",
+  "YearPredictionMSD-train",
+  "madelon-train",
+  "e2006-tfidf-train",
+  "e2006-log1p-train",
+  "rcv1-train",
+  "news20"
+)
+
+g <- expand_grid(
+  dataset = datasets,
+  screening_type = c("working", "hessian", "gap_safe", "edpp"),
+  family = NA,
+  n = NA,
+  p = NA,
+  density = NA,
+  time = NA,
+  total_violations = NA,
+  avg_screened = NA,
+  violations = list(NA),
+  screened = list(NA),
+  active = list(NA)
+)
+
+for (i in seq_len(nrow(g))) {
+  d <- readRDS(file.path("data", paste0(g$dataset[i], ".rds")))
+  screening_type <- g$screening_type[i]
+
+  X <- d$X
+  y <- d$y
+
+  n <- nrow(X)
+  p <- ncol(X)
+
+  dens <- ifelse(inherits(X, "sparseMatrix"), Matrix::nnzero(X) / length(X), 1)
+
+  family <- if (length(unique(d$y)) == 2) "binomial" else "gaussian"
+
+  if (family == "binomial" && screening_type == "edpp") {
+    next
+  }
+
+  log_hessian_update_type <-
+    ifelse((1 - dens) * min(n, p) / max(n, p) * 10 < 0.1, "full", "approx")
+
+  printf("%02d/%i %-10.10s %s\n", i, nrow(g), g$dataset[i], screening_type)
+
+  n_it <- 1
+
+  time <- double(n_it)
+
+  for (k in seq_len(n_it)) {
+    fit <- lassoPath(
+      X,
+      y,
+      family = family,
+      screening_type = screening_type,
+      verbosity = 0,
+      log_hessian_update_type = log_hessian_update_type
+    )
+
+    time[k] <- fit$full_time
+  }
+
+  g$n[i] <- n
+  g$p[i] <- p
+  g$family[i] <- family
+  g$time[i] <- mean(time)
+  g$density[i] <- dens
[…]

### 2021-03-31 experiments/sandbox.R

@@ -1,0 +1,73 @@
+library(HessianScreening)
+
+#d <- readRDS(file.path("data", paste0("dorothea", ".rds")))
+d <- generateDesign(100, 10)
+X <- d$X
+y <- d$y
+n <- nrow(X)
+p <- ncol(X)
+family <- "gaussian"
+tol_gap <- 1e-4
+tol_infeas <- 1e-3
+
+
+sparsity <- 1 - Matrix::nnzero(X) / length(X)
+sparsity * min(n, p) / max(n, p) * 10
+
+fit_hessian <- lassoPath(
+    X,
+    y,
+    family = family,
+    screening_type = "edpp",
+    verbosity = 1,
+    tol_gap = tol_gap,
+    tol_infeas = tol_infeas
+)
+
+fit_hessian$lookahead
+
+fit_working <- lassoPath(
+    X,
+    y,
+    family = family,
+    screening_type = "working",
+    verbosity = 1,
+    tol_gap = tol_gap,
+    tol_infeas = tol_infeas,
+    line_search = TRUE
+
+fit_edpp <- lassoPath(
+    X,
+    y,
+    family = family,
+    screening_type = "edpp",
+    verbosity = 1,
+    tol_gap = tol_gap,
+    tol_infeas = tol_infeas
+)
+fit_gapsafe <- lassoPath(
+    X,
+    y,
+    family = family,
+    screening_type = "gap_safe",
+    verbosity = 1,
+    tol_gap = tol_gap,
+    tol_infeas = tol_infeas
+)
+
+# # cat("***************\n")
+# cat("hessian:\n")
+# cat("full = ", fit$full_time, "\n")
+# cat("cd_time = ", sum(fit$cd_time), "\n")
+# cat("kkt_time = ", sum(fit$kkt_time), "\n")
+# cat("hess_time = ", sum(fit$hess_time), "\n")
+# cat("gradcorr_time", sum(fit$gradcorr_time), "\n")
+# cat("***************\n")
+# cat("working:\n")
+# cat("full = ", fit.w$full_time, "\n")
+# cat("cd_time = ", sum(fit.w$cd_time), "\n")
+# cat("kkt_time = ", sum(fit.w$kkt_time), "\n")
+
+
+# plot(fit$passes, type = "l")
+# lines(fit.w$passes, col = "red")

### 2021-03-31 experiments/simulateddata.R

@@ -1,0 +1,89 @@
+
+library(HessianScreening)
+library(RColorBrewer)
+library(tibble)
+library(dplyr)
+library(tidyr)
+library(progress)
+
+g <- expand_grid(
+  np = list(c(5e4, 1e2), c(1e2, 5e4)),
+  n = NA,
+  p = NA,
+  rho = c(0, 0.3, 0.6),
+  family = c("binomial", "gaussian"),
+  screening_type = c("hessian", "working", "gap_safe", "edpp"),
+  path_length = 100,
+  avg_screened = NA,
+  avg_violations = NA,
+  time = list(NA),
+  screened = list(NA),
+  active = list(NA)
+)
+
+n_it <- 20
+
+pb <- progress_bar$new(
+  format = "  simulating [:bar] :percent eta: :eta",
+  total = nrow(g) * n_it,
+  clear = FALSE,
+  width = 80
+)
+
+for (i in seq_len(nrow(g))) {
+  np <- g$np[i]
+  n <- np[[1]][1]
+  p <- np[[1]][2]
+  rho <- g$rho[i]
+  family <- g$family[i]
+  screening_type <- g$screening_type[i]
+  path_length <- g$path_length[i]
+
+  if (family == "binomial" && screening_type == "edpp") {
+    next
+  }
+
+  avg_screened <- violations <- time <- double(n_it)
+  active <- screened <- matrix(NA, nrow = n_it, ncol = path_length)
+
+  for (j in seq_len(n_it)) {
+    set.seed(j)
+    pb$tick()
+
+    d <- generateDesign(n, p, family = family, rho = rho)
+    X <- d$X
+    y <- d$y
+
+    fit <- lassoPath(
+      X,
+      y,
+      family = family,
+      screening_type = screening_type,
+      path_length = path_length
+    )
+
+    n_lambda <- length(fit$lambda)
+
+    time[j] <- fit$full_time
+    avg_screened[j] <- mean(fit$active / fit$screened)
+    violations[j] <- sum(fit$violations)
+    screened[j, 1:n_lambda] <- fit$screened
+    active[j, 1:n_lambda] <- fit$active
+  }
+
+  keep <- !apply(screened, 2, anyNA)
+
+  active <- active[, keep]
+  screened <- screened[, keep]
+
+  g$n[i] <- n
+  g$p[i] <- p
+  g$family[i] <- family
+  g$time[i] <- list(time)
[…]

### 2021-03-31 experiments/test.R

@@ -1,0 +1,8 @@
+# test that
+library(HessianScreening)
+
+d <- generateDesign(100, 10)
+
+fit <- lassoPath(d$X, d$y)
+
+write.csv(fit$beta, "results/test.csv")

### 2021-03-31 figures/simulated-data-timings.R

@@ -1,0 +1,107 @@
+library(tibble)
+library(tidyr)
+library(dplyr)
+library(forcats)
+library(lattice)
+library(latticeExtra)
+library(tactile)
+library(tikzDevice)
+library(ggplot2)
+
+thm <- tactile.theme(c(12, 8),
+  plot.symbol = list(col = 1),
+  superpose.line = list(lty = 1:3)
+)
+
+d_raw <- readRDS("results/simulateddata.R") %>%
+  mutate(
+    screening_type = recode(
+      screening_type,
+      "hessian" = "Hessian",
+      "working" = "Working",
+      "edpp" = "EDPP",
+      "gap_safe" = "Gap-Safe"
+    ),
+    rho = as.factor(rho),
+    np = paste(n, p, sep = " x ")
+  ) %>%
+  select(np, n, p, rho, family, screening_type, time) %>%
+  unnest(time)
+
+d1 <-
+  d_raw %>%
+  mutate(
+    screening_type = as.factor(screening_type),
+    family = as.factor(family)
+  ) %>%
+  group_by(np, rho, family, screening_type) %>%
+  summarize(
+    meantime = mean(time),
+    se = sd(time / n())
+  ) %>%
+  mutate(
+    hi = meantime + se,
+    lo = meantime - se
+  )
+
+d2_gaussian <-
+  filter(d1, family == "gaussian")
+
+library(qualpalr)
+
+cols <- qualpal(4)
+
+cols <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
+
+tikz("figures/simulateddata-gaussian-timings.tex", width = 5, height = 3)
+xyplot(
+  meantime ~ rho | np,
+  groups = screening_type,
+  data = d2_gaussian,
+  type = "b",
+  auto.key = list(lines = TRUE, points = FALSE),
+  prepanel = prepanel.ci,
+  lower = d2_gaussian$lo,
+  upper = d2_gaussian$hi,
+  panel = function(...) {
+    panel.ci(..., alpha = 0.2, grid = TRUE)
+    panel.xyplot(...)
+  }
+)
+dev.off()
+
+library(ggthemes)
+
+tikz("figures/simulateddata-gaussian-timings.tex", width = 5, height = 3)
+pl <- ggplot(d2_gaussian, aes(rho,
+  meantime,
+  ymin = lo,
+  ymax = hi,
+  group = screening_type,
[…]

### 2021-03-31 sim-realdata.sh

@@ -1,0 +1,18 @@
+#!/bin/sh
+
+#SBATCH -t 8:00:00
+
+#SBATCH --mail-user=johan.larsson@stat.lu.se
+#SBATCH --mail-type=ALL
+
+#SBATCH -J realdata
+#SBATCH -o realdata_%j.out
+#SBATCH -e realdata_%j.err
+
+#SBATCH -N 1
+#SBATCH --tasks-per-node=20
+
+# modules
+module purge
+
+singularity run --bind results:/Project/results container.sif realdata.R

### 2021-03-31 sim-simulateddata.sh

@@ -1,0 +1,19 @@
+#!/bin/sh
+
+#SBATCH -t 8:00:00
+
+#SBATCH --mail-user=johan.larsson@stat.lu.se
+#SBATCH --mail-type=ALL
+
+#SBATCH -J simulateddata
+#SBATCH -o simulateddata_%j.out
+#SBATCH -e simulateddata_%j.err
+
+#SBATCH -N 1
+#SBATCH --tasks-per-node=20
+
+# modules
+module purge
+
+# run the test
+singularity run --bind results:/Project/results container.sif simulateddata.R

### 2021-03-31 sim-test.sh

@@ -1,0 +1,22 @@
+#!/bin/sh
+
+#SBATCH -t 00:15:00
+
+#SBATCH --mail-user=johan.larsson@stat.lu.se
+#SBATCH --mail-type=ALL
+
+#SBATCH -J test
+#SBATCH -o test_%j.out
+#SBATCH -e test_%j.err
+
+#SBATCH -N 1
+#SBATCH --tasks-per-node=20
+
+# modules
+module purge
+
+# bind results folders in Project to host
+export SINGULARITY_BIND="results:/Project/results"
+
+# run the test
+singularity run container.sif test.R

### 2021-03-31 src/RcppExports.cpp

@@ -1,0 +1,65 @@
+// Generated by using Rcpp::compileAttributes() -> do not edit by hand
+// Generator token: 10BE3573-1514-4C36-9D1C-5A225CD40393
+
+#include <RcppArmadillo.h>
+#include <Rcpp.h>
+
+using namespace Rcpp;
+
+// lassoPathDense
+Rcpp::List lassoPathDense(arma::mat X, arma::vec y, const std::string family, const bool standardize, const std::string screening_type, const arma::uword path_length, const arma::uword maxit, const double tol_infeas, const double tol_gap, const double gamma, const bool force_kkt_check, const bool line_search, const arma::uword verbosity);
+RcppExport SEXP _LookAheadScreening_lassoPathDense(SEXP XSEXP, SEXP ySEXP, SEXP familySEXP, SEXP standardizeSEXP, SEXP screening_typeSEXP, SEXP path_lengthSEXP, SEXP maxitSEXP, SEXP tol_infeasSEXP, SEXP tol_gapSEXP, SEXP gammaSEXP, SEXP force_kkt_checkSEXP, SEXP line_searchSEXP, SEXP verbositySEXP) {
+BEGIN_RCPP
+    Rcpp::RObject rcpp_result_gen;
+    Rcpp::RNGScope rcpp_rngScope_gen;
+    Rcpp::traits::input_parameter< arma::mat >::type X(XSEXP);
+    Rcpp::traits::input_parameter< arma::vec >::type y(ySEXP);
+    Rcpp::traits::input_parameter< const std::string >::type family(familySEXP);
+    Rcpp::traits::input_parameter< const bool >::type standardize(standardizeSEXP);
+    Rcpp::traits::input_parameter< const std::string >::type screening_type(screening_typeSEXP);
+    Rcpp::traits::input_parameter< const arma::uword >::type path_length(path_lengthSEXP);
+    Rcpp::traits::input_parameter< const arma::uword >::type maxit(maxitSEXP);
+    Rcpp::traits::input_parameter< const double >::type tol_infeas(tol_infeasSEXP);
+    Rcpp::traits::input_parameter< const double >::type tol_gap(tol_gapSEXP);
+    Rcpp::traits::input_parameter< const double >::type gamma(gammaSEXP);
+    Rcpp::traits::input_parameter< const bool >::type force_kkt_check(force_kkt_checkSEXP);
[…]

### 2021-03-31 src/binomial.h

@@ -1,0 +1,109 @@
+#pragma once
+
+#include <RcppArmadillo.h>
+
+#include "prox.h"
+#include "utils.h"
+
+using namespace arma;
+
+class Binomial : public Model
+{
+public:
+  vec expXbeta;
+  vec pr;
+  vec w;
+
+  const double p_min = 1e-5;
+  const double p_max = 1 - p_min;
+
+  Binomial(const std::string family,
+           vec& y,
+           vec& beta,
+           vec& residual,
+           vec& Xbeta,
+           vec& c,
+           const vec& X_mean_scaled,
+           const vec& X_norms_squared,
+           const uword n,
+           const uword p,
+           const bool standardize)
+    : Model{ family,          y, beta, residual,   Xbeta, c, X_mean_scaled,
+             X_norms_squared, n, p,    standardize }
+    , expXbeta(y.n_elem, fill::zeros)
+    , pr(y.n_elem, fill::zeros)
+    , w(y.n_elem, fill::zeros)
+  {}
+
+  double primal(const double lambda, const uvec& screened_set)
+  {
+    return -sum(y % Xbeta - log1p(expXbeta)) +
+           lambda * norm(beta(screened_set), 1);
+  }
+
+  double dual() { return -sum(pr % log(pr) + (1 - pr) % log(1 - pr)); }
+
+  double scaledDual(const double lambda)
+  {
+    if (dual_scale == 0) {
+      return 0;
+    } else {
+      double alpha = lambda / dual_scale;
+
+      vec prx = clamp(y - alpha * residual, p_min, p_max);
+
+      return -sum(prx % log(prx) + (1 - prx) % log(1 - prx));
+    }
+  }
+
+  double deviance() { return -2 * sum(y % Xbeta - log1p(expXbeta)); }
+
+  double hessianTerm(const mat& X, const uword j)
+  {
+    return std::max(dot(square(X.col(j)), w), std::sqrt(datum::eps));
+  }
+
+  double hessianTerm(const sp_mat& X, const uword j)
+  {
+    double out = dot(square(X.col(j)), w);
+
+    if (standardize) {
+      out += std::pow(X_mean_scaled(j), 2) * sum(w) -
+             2 * dot(X.col(j), w) * X_mean_scaled(j);
+    }
+
+    return std::max(out, std::sqrt(datum::eps));
+  }
+
+  void updateResidual()
+  {
[…]

### 2021-03-31 src/checkStoppingConditions.h

@@ -1,0 +1,55 @@
+#pragma once
+
+#include <RcppArmadillo.h>
+
+using namespace arma;
+
+bool
+checkStoppingConditions(const uword step,
+                        const uword n,
+                        const uword p,
+                        const uword n_lambda,
+                        const uword n_active,
+                        const double lambda,
+                        const double lambda_min,
+                        const double dev,
+                        const double dev_prev,
+                        const double null_dev,
+                        const std::string screening_type,
+                        const uword verbosity)
+{
+  if (step == 1) {
+    // first step; always continue
+    return false;
+  }
+
+  if (verbosity >= 1) {
+    Rprintf("  checking stopping conditions\n");
+  }
+
+  double dev_ratio = 1.0 - dev / null_dev;
+  double dev_change = 1.0 - dev / dev_prev;
+
+  if (verbosity >= 1) {
+    Rprintf(
+      "    dev ratio:  %.3f\n    dev change: %.6f\n", dev_ratio, dev_change);
+  }
+
+  if (dev_change <= 1e-5) {
+    return true;
+  }
+
+  if (dev_ratio >= 0.999 || lambda <= lambda_min) {
+    return true;
+  }
+
+  if (n <= p && n_active >= n) {
+    return true;
+  }
+
+  if (screening_type != "hessian_adaptive" && step >= n_lambda) {
+    return true;
+  }
+
+  return false;
+}

### 2021-03-31 src/colNormsSquared.h

@@ -1,0 +1,18 @@
+#pragma once
+
+#include <RcppArmadillo.h>
+
+using namespace arma;
+
+template<typename T>
+vec
+colNormsSquared(const T& X)
+{
+  vec out(X.n_cols);
+
+  for (uword j = 0; j < X.n_cols; ++j) {
+    out(j) = std::pow(norm(X.col(j)), 2);
+  }
+
+  return out;
+}

### 2021-03-31 src/gaussian.h

@@ -1,0 +1,78 @@
+#pragma once
+
+#include <RcppArmadillo.h>
+
+#include "prox.h"
+#include "utils.h"
+
+using namespace arma;
+
+class Gaussian : public Model
+{
+public:
+  Gaussian(const std::string family,
+           vec& y,
+           vec& beta,
+           vec& residual,
+           vec& Xbeta,
+           vec& c,
+           const vec& X_mean_scaled,
+           const vec& X_norms_squared,
+           const uword n,
+           const uword p,
+           const bool standardize)
+    : Model{ family,          y, beta, residual,   Xbeta, c, X_mean_scaled,
+             X_norms_squared, n, p,    standardize }
+  {}
+
+  double primal(const double lambda, const uvec& screened_set)
+  {
+    return 0.5 * std::pow(norm(residual), 2) +
+           lambda * norm(beta(screened_set), 1);
+  }
+
+  double dual() { return dot(residual, y) - 0.5 * std::pow(norm(residual), 2); }
+
+  double scaledDual(const double lambda)
+  {
+    if (dual_scale == 0) {
+      return 0;
+    } else {
+      double alpha = lambda / dual_scale;
+
+      return alpha * dot(residual, y) -
+             0.5 * std::pow(alpha * norm(residual), 2);
+    }
+  }
+
+  double deviance() { return std::pow(norm(residual), 2); }
+
+  double hessianTerm(const mat& X, const uword j) { return X_norms_squared(j); }
+
+  double hessianTerm(const sp_mat& X, const uword j)
+  {
+    return X_norms_squared(j);
+  }
+
+  void updateResidual() { residual = y - Xbeta; }
+
+  void adjustResidual(const mat& X, const uword j, const double beta_diff)
+  {
+    residual -= X.col(j) * beta_diff;
+  }
+
+  void adjustResidual(const sp_mat& X, const uword j, const double beta_diff)
+  {
+    residual -= X.col(j) * beta_diff;
+
+    if (standardize)
+      residual += X_mean_scaled(j) * beta_diff;
+  }
+
+  void standardizeY() { y -= mean(y); }
+
+  double safeScreeningRadius(const double duality_gap, const double lambda)
+  {
+    return std::sqrt(duality_gap) / lambda;
+  }
+};

### 2021-03-31 src/getNextLambda.h

@@ -1,0 +1,86 @@
+#pragma once
+
+#include <RcppArmadillo.h>
+
+using namespace arma;
+
+struct GetNextLambda
+{
+  const vec& c;
+  const vec& c_grad;
+  const vec& lambda_grid;
+  const double lambda_min;
+  const double lambda_min_step;
+  const std::string screening_type;
+  uword n_target_nonzero;
+  const uword verbosity;
+
+  double lambda_next_mod{ 1 };
+
+  GetNextLambda(const vec& c,
+                const vec& c_grad,
+                const vec& lambda_grid,
+                const double lambda_min,
+                const double lambda_min_step,
+                const std::string screening_type,
+                const uword n_target_nonzero,
+                const uword verbosity)
+    : c(c)
+    , c_grad(c_grad)
+    , lambda_grid(lambda_grid)
+    , lambda_min{ lambda_min }
+    , lambda_min_step{ lambda_min_step }
+    , screening_type{ screening_type }
+    , n_target_nonzero{ n_target_nonzero }
+    , verbosity{ verbosity } {};
+
+  double operator()(const double lambda,
+                    const uvec& active,
+                    const uword n_new_active,
+                    const uword step_number)
+  {
+    if (screening_type != "hessian_adaptive") {
+      return lambda_grid(step_number);
+    }
+
+    uvec inactive_set = find(active == false);
+
+    if (inactive_set.is_empty()) {
+      return lambda_min;
+    }
+
+    if (step_number > 1) {
+      if (n_new_active > n_target_nonzero) {
+        lambda_next_mod *= 1.01;
+      } else if (n_new_active < n_target_nonzero) {
+        lambda_next_mod /= 1.01;
+      }
+
+      n_target_nonzero = std::min(n_target_nonzero, inactive_set.n_elem);
+
+      if (verbosity >= 1) {
+        Rprintf("  lambda_next_mod: %f\n", lambda_next_mod);
+      }
+    }
+
+    const vec c_inac = c(inactive_set);
+    const vec c_grad_inac = c_grad(inactive_set);
+
+    vec a = (c_inac - lambda * c_grad_inac) / (1 - c_grad_inac);
+    vec b = (lambda * c_grad_inac - c_inac) / (1 + c_grad_inac);
+
+    a(find(a >= lambda)).zeros();
+    b(find(b >= lambda)).zeros();
+
+    vec lambda_pred = sort(max(a, b), "descend");
[…]

### 2021-03-31 src/kktCheck.h

@@ -1,0 +1,20 @@
+#pragma once
+
+#include <RcppArmadillo.h>
+
+using namespace arma;
+
+void
+kktCheck(uvec& violations,
+         uvec& screened,
+         const vec& c,
+         const uvec& check_set,
+         const double lambda)
+{
+  for (auto&& j : check_set) {
+    if (std::abs(c(j)) >= lambda) {
+      violations[j] = true;
+      screened[j] = true;
+    }
+  }
+}

### 2021-03-31 src/lassoPath.cpp

@@ -1,0 +1,408 @@
+#include <RcppArmadillo.h>
+
+#include "setupModel.h"
+#include "model.h"
+#include "colNormsSquared.h"
+#include "binomial.h"
+#include "gaussian.h"
+#include "checkStoppingConditions.h"
+#include "kktCheck.h"
+#include "rescaleCoefficients.h"
+#include "screenPredictors.h"
+#include "standardize.h"
+
+using namespace arma;
+using namespace Rcpp;
+
+template<typename T>
+Rcpp::List
+lassoPath(T& X,
+          vec& y,
+          const std::string family,
+          const bool standardize,
+          const std::string screening_type,
+          const uword path_length,
+          const uword maxit,
+          const double tol_infeas,
+          const double tol_gap,
+          const double gamma,
+          const bool force_kkt_check,
+          const bool line_search,
+          const uword verbosity)
+{
+  const uword n = X.n_rows;
+  const uword p = X.n_cols;
+
+  if (family == "binomial") {
+    vec y_unique = sort(unique(y));
+
+    if (y_unique.n_elem != 2) {
+      Rcpp::stop("y has more than two unique values");
+    } else if (y_unique(0) != 0 || y_unique(1) != 1) {
+      Rcpp::stop("y is not in {0, 1}");
+    }
+
+    if (screening_type == "edpp")
+      Rcpp::stop("EDPP cannot be used in logistic regression");
+  }
+
+  umat lookaheads(X.n_cols, 0);
+
+  vec beta(p, fill::zeros);
+  mat betas(p, 0, fill::zeros);
+  vec Xbeta(n, fill::zeros);
+  vec residual(n, fill::zeros);
+  vec c(p);
+  vec c_pred(p);
+  vec c_grad(p);
+
+  // standardize predictors and response
+  vec X_mean = zeros<vec>(p);
+  vec X_sd = ones<vec>(p);
+
+  if (standardize) {
+    standardizeX(X_mean, X_sd, X);
+  }
+
+  const vec X_mean_scaled = X_mean / X_sd;
+  const double y_center = mean(y);
+
+  vec X_norms_squared(p);
+
+  if (!standardize) {
+    X_norms_squared = colNormsSquared(X);
+  } else {
+    X_norms_squared.fill(n);
+  }
+
+  auto model = setupModel(family,
+                          y,
+                          beta,
+                          residual,
+                          Xbeta,
+                          c,
+                          X_mean_scaled,
+                          X_norms_squared,
[…]

### 2021-03-31 src/model.h

@@ -1,0 +1,310 @@
+#pragma once
+
+#include <RcppArmadillo.h>
+
+#include "prox.h"
+
+using namespace arma;
+
+class Model
+{
+public:
+  const std::string family;
+
+  vec& y;
+  vec& beta;
+  vec& residual;
+  vec& Xbeta;
+  vec& c;
+
+  const vec& X_mean_scaled;
+  const vec& X_norms_squared;
+
+  const uword n;
+  const uword p;
+  const bool standardize;
+
+  double dual_scale{ 0 };
+
+  Model(const std::string family,
+        vec& y,
+        vec& beta,
+        vec& residual,
+        vec& Xbeta,
+        vec& c,
+        const vec& X_mean_scaled,
+        const vec& X_norms_squared,
+        const uword n,
+        const uword p,
+        const bool standardize)
+    : family(family)
+    , y(y)
+    , beta(beta)
+    , residual(residual)
+    , Xbeta(Xbeta)
+    , c(c)
+    , X_mean_scaled(X_mean_scaled)
+    , X_norms_squared(X_norms_squared)
+    , n(n)
+    , p(p)
+    , standardize(standardize)
+  {}
+
+  virtual ~Model() = default;
+
+  virtual double primal(const double lambda, const uvec& screened_set) = 0;
+
+  virtual double dual() = 0;
+
+  virtual double scaledDual(const double lambda) = 0;
+
+  virtual double deviance() = 0;
+
+  virtual double hessianTerm(const mat& X, const uword j) = 0;
+
+  virtual double hessianTerm(const sp_mat& X, const uword j) = 0;
+
+  virtual void updateResidual() = 0;
+
+  virtual void adjustResidual(const mat& X,
+                              const uword j,
+                              const double beta_diff) = 0;
+
+  virtual void adjustResidual(const sp_mat& X,
+                              const uword j,
+                              const double beta_diff) = 0;
+
+  void updateLinearPredictor(const mat& X, const uvec& ind)
+  {
+    Xbeta = X.cols(ind) * beta(ind);
+  }
+
+  void updateLinearPredictor(const sp_mat& X, const uvec& ind)
+  {
+    Xbeta = X.cols(ind) * beta(ind);
+
+    if (standardize)
+      Xbeta -= dot(beta(ind), X_mean_scaled(ind));
+  }
+
+  void updateCorrelation(const mat& X, const uvec& ind)
+  {
[…]

### 2021-03-31 src/prox.h

@@ -1,0 +1,9 @@
+#pragma once
+
+#include "utils.h"
+
+double
+prox(const double x, const double lambda)
+{
+  return signum(x) * std::max(std::abs(x) - lambda, 0.0);
+}

### 2021-03-31 src/rescaleCoefficients.h

@@ -1,0 +1,18 @@
+#pragma once
+
+#include <RcppArmadillo.h>
+
+using namespace arma;
+
+void
+rescaleCoefficients(mat& betas,
+                    const vec& X_mean,
+                    const vec& X_sd,
+                    const double y_mean)
+{
+  const uword p = betas.n_rows;
+
+  for (uword j = 0; j < p; ++j) {
+    betas.row(j) /= X_sd(j);
+  }
+}

### 2021-03-31 src/screenPredictors.h

@@ -1,0 +1,82 @@
+#pragma once
+
+#include <RcppArmadillo.h>
+
+using namespace arma;
+
+template<typename T>
+std::tuple<uvec, uvec>
+screenPredictors(const std::string screening_type,
+                 const uvec& strong,
+                 const uvec& ever_active,
+                 const vec& residual,
+                 const vec& c,
+                 const vec& c_grad,
+                 const T& X,
+                 const vec& X_norms_squared,
+                 const vec& X_mean_scaled,
+                 const vec& y,
+                 const vec& lambdas,
+                 const double lambda,
+                 const double lambda_next,
+                 const double gamma,
+                 const uword step,
+                 const bool standardize)
+{
+  uvec screened(X.n_cols);
+  uvec lookahead(X.n_cols, fill::zeros);
+  lookahead.fill(100);
+
+  if (screening_type == "working") {
+    screened = ever_active;
+  } else if (screening_type == "strong") {
+    screened = strong;
+  } else if (screening_type == "hessian" ||
+             screening_type == "hessian_adaptive") {
+    vec c_pred = c + c_grad * (lambda_next - lambda);
+    screened = (abs(c_pred) + gamma * (lambda - lambda_next) > lambda_next) ||
+               ever_active;
+  } else if (screening_type == "gap_safe") {
+    // we use the active set strategy for the gap safe rules, so we use the
+    // ever-active predictors to get a good warm start
+    screened = ever_active;
+  } else if (screening_type == "edpp") {
+    double dual_scale = std::max(lambda, max(abs(c)));
+    vec v1 = y / lambda - residual / dual_scale;
+    vec v2 = y / lambda_next - residual / dual_scale;
+
+    double norm_v1 = std::pow(norm(v1), 2);
+    vec v_orth = norm_v1 != 0 ? v2 - v1 * dot(v1, v2) / norm_v1 : v2;
+    vec center = residual / dual_scale + 0.5 * v_orth;
+    double r_screen = 0.5 * norm(v_orth);
+
+    vec XTcenter = matTransposeMultiply(X, center, X_mean_scaled, standardize);
+
+    screened = r_screen * sqrt(X_norms_squared) + abs(XTcenter) >= 1;
+
+    for (uword i = step; i < lambdas.n_elem; ++i) {
+      if (lambdas[i] < lambda) {
[…]

### 2021-03-31 src/setupModel.h

@@ -1,0 +1,48 @@
+#pragma once
+
+#include <RcppArmadillo.h>
+
+#include "model.h"
+#include "binomial.h"
+#include "gaussian.h"
+
+using namespace arma;
+
+std::unique_ptr<Model>
+setupModel(const std::string family,
+           vec& y,
+           vec& beta,
+           vec& residual,
+           vec& Xbeta,
+           vec& c,
+           const vec& X_mean_scaled,
+           const vec& X_norms_squared,
+           const uword n,
+           const uword p,
+           const bool standardize)
+{
+  if (family == "binomial")
+    return std::make_unique<Binomial>(family,
+                                      y,
+                                      beta,
+                                      residual,
+                                      Xbeta,
+                                      c,
+                                      X_mean_scaled,
+                                      X_norms_squared,
+                                      n,
+                                      p,
+                                      standardize);
+
+  return std::make_unique<Gaussian>(family,
+                                    y,
+                                    beta,
+                                    residual,
+                                    Xbeta,
+                                    c,
+                                    X_mean_scaled,
+                                    X_norms_squared,
+                                    n,
+                                    p,
+                                    standardize);
+}

### 2021-03-31 src/standardize.h

@@ -1,0 +1,39 @@
+#include <RcppArmadillo.h>
+
+using namespace arma;
+
+void
+standardizeX(vec& X_mean, vec& X_sd, mat& X)
+{
+  const uword p = X.n_cols;
+
+  for (uword j = 0; j < p; j++) {
+    X_mean(j) = mean(X.col(j));
+    X.col(j) -= X_mean(j);
+
+    double X_sd_j = stddev(X.col(j), 1);
+
+    if (X_sd_j != 0) {
+      X_sd(j) = X_sd_j;
+      X.col(j) /= X_sd_j;
+    }
+  }
+}
+
+void
+standardizeX(vec& X_mean, vec& X_sd, sp_mat& X)
+{
+  const uword n = X.n_rows;
+  const uword p = X.n_cols;
+
+  for (uword j = 0; j < p; j++) {
+    X_mean(j) = mean(X.col(j));
+
+    double X_sd_j = norm(X.col(j) - accu(X.col(j)) / n) / std::sqrt(n);
+
+    if (X_sd_j != 0) {
+      X_sd(j) = X_sd_j;
+      X.col(j) /= X_sd_j;
+    }
+  }
+}

### 2021-03-31 src/utils.h

@@ -1,0 +1,165 @@
+#pragma once
+
+#include <RcppArmadillo.h>
+
+using namespace arma;
+
+inline double
+squaredNorm(const vec& x)
+{
+  return std::pow(norm(x), 2);
+}
+
+template<typename T>
+inline int
+signum(T val)
+{
+  return (T(0) < val) - (val < T(0));
+}
+
+template<typename T, typename S>
+inline bool
+contains(const T& x, const S& what)
+{
+  return std::find(x.begin(), x.end(), what) != x.end();
+}
+
+inline uvec
+setUnion(const uvec& a, const uvec& b)
+{
+  std::vector<unsigned> out;
+  out.reserve(a.n_elem + b.n_elem);
+
+  std::set_union(
+    a.begin(), a.end(), b.begin(), b.end(), std::back_inserter(out));
+
+  out.shrink_to_fit();
+
+  return conv_to<uvec>::from(out);
+}
+
+inline uvec
+setDiff(const uvec& a, const uvec& b)
+{
+  std::vector<uword> out;
+  out.reserve(a.n_elem);
+
+  std::set_difference(
+    a.begin(), a.end(), b.begin(), b.end(), std::back_inserter(out));
+
+  out.shrink_to_fit();
+
+  return conv_to<uvec>::from(out);
+}
+
+inline uvec
+setIntersect(const uvec& a, const uvec& b)
+{
+  std::vector<uword> out;
+  out.reserve(std::min(a.n_elem, b.n_elem));
+
+  std::set_intersection(
+    a.begin(), a.end(), b.begin(), b.end(), std::back_inserter(out));
+
+  out.shrink_to_fit();
+
+  return conv_to<uvec>::from(out);
+}
+
+// set intersection that retains permutation in `a`
+inline uvec
+safeSetIntersect(const uvec& a, const uvec& b)
+{
+  std::vector<uword> out;
+  out.reserve(std::min(a.n_elem, b.n_elem));
+
+  for (auto&& a_i : a) {
+    if (contains(b, a_i)) {
+      out.emplace_back(a_i);
+    }
+  }
+
+  out.shrink_to_fit();
+
+  return conv_to<uvec>::from(out);
+}
+
+// set difference that retains permutation in `a`
+inline uvec
+safeSetDiff(const uvec& a, const uvec& b)
+{
+  std::vector<uword> out;
+  out.reserve(a.n_elem);
+
[…]

### 2021-03-31 tables/realdata.R

@@ -1,0 +1,44 @@
+library(lattice)
+library(tibble)
+library(dplyr)
+library(tidyr)
+library(readr)
+library(forcats)
+library(kableExtra)
+library(stringr)
+
+d_raw <- readRDS("results/realdata.rds")
+
+d <-
+  d_raw %>%
+  drop_na(time) %>%
+  mutate(
+    screening_type = recode(
+      screening_type,
+      "working" = "Working",
+      "hessian" = "Hessian",
+      "gap_safe" = "GapSafe",
+      "edpp" = "EDPP"
+    ),
+    family = recode(
+      family,
+      "gaussian" = "Gaussian",
+      "binomial" = "Binomial"
+    ),
+    dataset = str_remove(dataset, "(-train|-test)"),
+    dataset = recode(
+      dataset,
+      "YearPredictionMSD" = "YearPredMSD"
+    )
+  ) %>%
+  select(dataset, family, n, p, density, screening = screening_type, time) %>%
+  arrange(family, dataset, screening) %>%
+  pivot_wider(names_from = "screening", values_from = "time")
+
+filter(d, family == "Gaussian") %>%
+  select(-family) %>%
+  write_csv("tables/realdata-timings-gaussian.csv")
+
+filter(d, family == "Binomial") %>%
+  select(-family) %>%
+  write_csv("tables/realdata-timings-binomial.csv")

### 2021-03-31 tests/testthat.R

@@ -1,0 +1,4 @@
+library(testthat)
+library(LookAheadScreening)
+
+test_check("LookAheadScreening")

### 2021-03-31 tests/testthat/test-lambda-grid.R

@@ -1,0 +1,25 @@
+library(HessianScreening)
+
+test_that("lambda grid calculations are correct", {
+  for (p in c(10, 100)) {
+    set.seed(1110)
+
+    n <- 50
+
+    X <- matrix(rnorm(n * p), n, p)
+    beta <- rnorm(p)
+    y <- X %*% beta + rnorm(n)
+
+    X <- scale(X)
+    y <- y - mean(y)
+
+    family <- "gaussian"
+
+    res_work <- lassoPath(X, y, family = family)
+    res_glmn <- glmnet::glmnet(X, y, intercept = FALSE)
+
+    n_lambda <- min(length(res_work$lambda), length(res_glmn$lambda))
+
+    expect_equal(res_work$lambda[1:n_lambda] / n, res_glmn$lambda[1:n_lambda])
+  }
+})

### 2021-03-31 tests/testthat/test-logistic.R

@@ -1,0 +1,36 @@
+test_that("compare against glmnet with real data", {
+  suppressMessages(library(glmnet))
+
+  datalist <- c("heart", "leukemia")
+
+  for (dataset in datalist) {
+    data(list = list(dataset))
+    d <- get(dataset)
+    X <- d$X
+    y <- d$y
+
+    fit_ours <- lassoPath(X,
+      y,
+      "binomial",
+      screening_type = "working",
+      standardize = FALSE
+    )
+
+    lambda <- fit_ours$lambda / nrow(X)
+
+    fit_gnet <- glmnet(X,
+      y,
+      "binomial",
+      lambda = lambda,
+      intercept = FALSE,
+      standardize = FALSE
+    )
+
+    ours_dev <- fit_ours$dev_ratio
+    gnet_dev <- fit_gnet$dev.ratio
+
+    dev_diff <- pmax(gnet_dev - ours_dev, 0)
+
+    expect_equal(dev_diff, rep(0, length(dev_diff)), tolerance = 1e-3)
+  }
+})

### 2021-03-31 tests/testthat/test-screening.R

@@ -1,0 +1,39 @@
+test_that("screening methods work", {
+  set.seed(1014)
+
+  n <- 50
+  p <- 200
+
+  for (density in c(1, 0.5)) {
+
+    for (family in c("gaussian", "binomial")) {
+      d <- generateDesign(n, p, family = family)
+
+      X <- d$X
+      y <- d$y
+
+      fit_work <- lassoPath(X, y, family = family, screening_type = "working")
+
+      for (screening_type in c("hessian", "working", "strong", "gap_safe")) {
+        if (family == "gaussian" && screening_type == "edpp") {
+          next
+        }
+
+        fit <- lassoPath(X,
+                         y,
+                         family = family,
+                         screening_type = screening_type,
+                         verbosity = 0,
+                         force_kkt_check = TRUE)
+
+        steps <- 1:min(length(fit$lambda), length(fit_work$lambda))
+        expect_equal(fit_work$dev[steps], fit$dev[steps],
+                     tolerance = 1e-3)
+
+        if (screening_type %in% c("gap_safe")) {
+          expect_equal(sum(fit$violations), 0)
+        }
+      }
+    }
+  }
+})

### 2021-03-31 tests/testthat/test-simulated.R

@@ -1,0 +1,77 @@
+test_that("gaussian and logistic models for simulated data", {
+  library(HessianScreening)
+  library(glmnet)
+
+  grid <- expand.grid(
+    np = list(c(100, 5), c(50, 100)),
+    density = c(0.2, 1),
+    screening_type = c("working", "hessian"),
+    family = c("gaussian", "binomial"),
+    standardize = c(FALSE),
+    stringsAsFactors = FALSE
+  )
+
+  for (i in 1:nrow(grid)) {
+    set.seed(i)
+
+    g <- grid[i, ]
+
+    np <- g$np[[1]]
+    n <- np[1]
+    p <- np[2]
+    family <- g$family
+    standardize <- g$standardize
+    screening_type <- g$screening_type
+
+    data <- generateDesign(
+      n,
+      p,
+      family = g$family,
+      density = g$density
+    )
+
+    X <- data$X
+    y <- data$y
+
+    if (family == "gaussian") {
+      y <- y - mean(y)
+    }
+
+    fit_glmnet <- glmnet(
+      X,
+      y,
+      family = family,
+      intercept = FALSE,
+      standardize = standardize
+    )
+
+    fit_ours <- lassoPath(
+      X,
+      y,
+      family,
+      screening_type = screening_type,
+      standardize = standardize
+    )
+
+    n_lambda <- min(length(fit_glmnet$lambda), length(fit_ours$lambda))
+
+    glmnet_lambda <- fit_glmnet$lambda[1:n_lambda] * n
+    ours_lambda <- fit_ours$lambda[1:n_lambda]
+
+    expect_equal(glmnet_lambda, ours_lambda)
+
+    glmnet_beta <- as.matrix(fit_glmnet$beta[, 1:n_lambda])
+    ours_beta <- fit_ours$beta[, 1:n_lambda]
+
+    glmnet_devratio <- fit_glmnet$dev.ratio[1:n_lambda]
+    ours_devratio <- fit_ours$dev_ratio[1:n_lambda]
+
+    dev_diff <- pmax(glmnet_devratio - ours_devratio, 0)
+
+    expect_equal(dev_diff, rep(0, n_lambda), tolerance = 1e-3)
+
+    if (n > p) {
+      expect_equal(ours_beta, glmnet_beta, ignore_attr = TRUE, tolerance = 1e-2)
+    }
+  }
+})

### 2021-03-31 tests/testthat/test-sparse.R

@@ -1,0 +1,18 @@
+test_that("sparse and dense methods are equivalent", {
+  n <- 100
+  p <- 5
+
+  for (family in c("gaussian", "binomial")) {
+    d <- generateDesign(n, p, family = family, density = 0.5)
+    X <- d$X
+    y <- d$y
+    for (standardize in c(TRUE, FALSE)) {
+      fit_dense <- lassoPath(as.matrix(X), y, family, standardize = standardize)
+      fit_sparse <- lassoPath(X, y, family, standardize = standardize)
+
+      expect_equal(fit_dense$lambda, fit_sparse$lambda)
+      expect_equal(fit_dense$dev_ratio, fit_sparse$dev_ratio)
+      expect_equal(fit_dense$beta, fit_sparse$beta)
+    }
+  }
+})

### 2021-05-05 README.Rmd
Flush out old files and start anew

@@
 <!-- badges: start -->
-[![R-CMD-check](https://github.com/jolars/LookAheadScreening/workflows/R-CMD-check/badge.svg)](https://github.com/jolars/HessianScreening/actions)
+[![R-CMD-check](https://github.com/jolars/LookAheadScreening/workflows/R-CMD-check/badge.svg)](https://github.com/jolars/LookAheadScreening/actions)
 <!-- badges: end -->

### 2021-05-05 paper/main.tex
Flush out old files and start anew

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%% Template for EYSM 2021 submissions %%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Please save the file as your name.
% Please, do not change any definitions.

\documentclass[b5paper,10pt,abstractoff,DIV=calc,headings=normal,twoside]{scrartcl}
\usepackage[english]{babel}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{amsmath,amssymb,amsthm,amsfonts,graphicx,etoolbox,scrlayer-scrpage}
\usepackage[noblocks]{authblk}
\makeatletter
\patchcmd{\@maketitle}{\huge}{\Large}{}{}
\patchcmd{\abstract}{\quotation}{}{}{}
\AtBeginEnvironment{abstract}{\noindent\ignorespaces}
\AtEndEnvironment{abstract}{\par\mbox{}}
\newcommand{\shortauthor}{}
\newcommand{\shorttitle}{\@title}
\makeatother
\setkomafont{author}{\small}
\setkomafont{title}{\rmfamily\bfseries}
\setkomafont{disposition}{\rmfamily\bfseries}
\renewcommand\Authfont{\bfseries}\renewcommand\Affilfont{\mdseries\slshape}
\def\AMS#1{\par\noindent \textbf{AMS subject classification: }#1\par}
\newcommand{\acknowledgements}{\par\mbox{}\par\noindent\textbf{Acknowledgements: }}
\newcommand{\keywords}[1]{\par\noindent\textbf{Keywords: }#1}
% \newcommand{\AMS}[1]{\par\noindent\textbf{AMS subject classification: }#1}
%\newcommand{\AMS}[1]{}
%\subject{\vspace{-2\baselineskip}}\date{\vspace{-2\baselineskip%}}
\renewcommand*{\titlepagestyle}{plain.scrheadings}\pagestyle{scrheadings}
\rehead[]{\shortauthor}\lohead[]{\shorttitle}\lehead[]{PPP}\rohead[]{PPP}
\cfoot[]{}\ofoot[]{}\ifoot[]{}\recalctypearea
\interfootnotelinepenalty=10000
%\usepackage{lipsum} %% generates dummy text
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%% Available theorem environments %%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{conjecture}{Conjecture}
\theoremstyle{remark}
\newtheorem*{note}{Note}
\newtheorem{remark}{Remark}

\renewenvironment{abstract}{\bigskip\noindent\begin{minipage}{\textwidth}\setlength{\parindent}{15pt}\paragraph{Abstract:}}{\end{minipage}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%% Do not modify prior to this point %%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage{mathtools}
\usepackage[colorlinks]{hyperref}
\usepackage{url}
\usepackage[numbers]{natbib}
\bibliographystyle{abbrvnat}

% math operators
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator{\sign}{sign}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%% Please make sure to leave space for page numbers             %%%%%%%%%
%%%%%%%%% There is a placeholder PPP generated in the document to help %%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\renewcommand{\shortauthor}{J. Larsson}
\renewcommand{\shorttitle}{Look-Ahead Screening Rules for the Lasso}

\title{Look-Ahead Screening Rules for the Lasso}

\author[1]{Johan Larsson%
  \thanks{%
    \href{mailto:johan.larsson@stat.lu.se}{\url{johan.larsson@stat.lu.se}}
  }%
}
\affil[1]{The Department of Statistics, Lund University}

\maketitle

\begin{abstract}
  The lasso is a popular method for inducing shrinkage and sparsity in the
  solution vector (coefficients) of regression problems, particularly when
  the number of predictors far outnumber the number of observations. Solving
  the lasso for high-dimensional data can, however, be computationally
  demanding. Fortunately, this computational load can be alleviated via the
  use of \emph{screening rules}, which screen and discard predictors prior to
  fitting the model, leading a reduced problem to be solved. Screening rules
  are particularly effective when fitting a full regularization path: a
  sequence of models with decreasing penalization. Screening rules can be
  safe or heuristic. Safe rules certify that discarded predictors are not in
  the solution; heuristic ones do not. Existing screening rules typically
  work sequentially or dynamically. Sequential rules screen predictors for
  the next model along the regularization path, whereas dynamical rules
  screen during optimization of the current model. There has, however,
  previously been no attempts to design screening rules that screen further
  along the path.

  In this paper, we present a new screening strategy: \emph{look-ahead}
  screening rules. Our method uses safe screening rules to find a range of
  penalty values for which a given predictor cannot enter the model, thereby
  screening predictors along the remainder of the path. Our screening rules
  lead to reductions in the time required for screening and also applies to
  heuristic rules, for which the time required to conduct checks of the
  optimality conditions to guard against violations of the rules is reduced.
  In experiments we show that these look-ahead screening rules improve the
  performance of existing screening strategies and that the additional cost
  of screening ahead on the path is marginal.
\end{abstract}

\keywords{lasso, sparse regression, screening rules, safe screening rules}

\smallskip

\AMS{62J07}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}

\section{Preliminaries}%
\label{sec:preliminaries}

Starting with the preliminaries of our problem, we take \(X \in \mathbb{R}^{n
  \times p}\) be the design matrix of \(n\) observations and \(p\) predictors
and \(y \in \mathbb{R}^n\) the response vector.

The lasso is represented by the following convex optimization problem:
\begin{equation}
  \label{eq:primal}
  \operatorname*{minimize}_{\beta \in \mathbb{R}^p} P(\beta; \lambda)
\end{equation}
where
\begin{equation}
  P(\beta; \lambda) =
  \frac 1 2 \lVert y - X\beta \rVert_2^2 + \lambda \lVert \beta \rVert_1
\end{equation}
is the \emph{primal} objective. We let \(\hat \beta_\lambda\) be the solution to
\eqref{eq:primal} for a given \(\lambda\). In addition, we also let \(\tilde
\beta_\lambda\) be a numerical approximation to \(\hat\beta_\lambda\)
returned by an algorithm
tasked with solving \eqref{eq:primal}.

The Karush--Kuhn--Tucker (KKT) stationarity condition for \eqref{eq:primal}
holds that
\begin{equation}
  \label{eq:stationarity}
  0 \in X^T(X\beta - y) + \lambda\partial,
\end{equation}
where \(\partial\) is the subdifferential of the \(\ell_1\)-norm, with
its \(j\)th element corresponding to
\begin{equation}
  \label{eq:subdifferential}
  \partial_j \in
  \begin{cases}
    \{\sign(\beta_j)\} & \text{if } \beta_j \neq 0 \\
    [-1,1]             & \text{otherwise.}
  \end{cases}
\end{equation}
Moreover, we define the dual problem of \eqref{eq:primal} as
\begin{equation}
  \label{eq:dual}
  \operatorname*{maximize}_{\theta \in \mathbb{R}^n} D(\theta; \lambda)
\end{equation}
where
\begin{equation}
  D(\theta) = \frac 12 y^T y - \frac{\lambda^2}{2} \left\lVert \theta
  - \frac y \lambda \right\rVert_2^2
\end{equation}
is the \emph{dual} objective.
The relationship between the primal and dual problems is given by
\[
  y = X\hat\beta_\lambda + \lambda \hat\theta_\lambda.
\]
Next, we let \(G\) be the so-called \emph{duality gap}, which we define
as
\begin{equation}
  \begin{aligned}
    G(\beta, \theta; \lambda)
     & = P(\beta; \lambda) - D(\theta; \lambda)                                                 \\
     & = \frac 12 \lVert y - X\beta\rVert_2^2 + \lambda \lVert \beta \rVert_1
    - \frac 12 y^T y + \frac{\lambda^2}{2} \left\lVert \theta - \frac y \theta \right\rVert_2^2 \\
     & =
    \frac 12 \lVert y - X\beta\rVert_2^2 + \lambda \lVert \beta \rVert_1
    - \lambda \theta^T y + \frac{\lambda^2}{2} \theta^T \theta.
  \end{aligned}
\end{equation}
In the case of the lasso, strong duality holds, which means that
\(G(\tilde\beta_\lambda, \tilde\theta_\lambda; \lambda) = 0\) for any
choice of \(\lambda\).

Suppose, now, that we have solved the lasso for \(\lambda\); then
for any given \(\lambda^* \geq \lambda\),
the Gap Safe rule~\citep{ndiaye2017} for the lasso discards the \(j\)th
predictor if
\begin{equation}
  \label{eq:gap-safe-rule}
  |X^T \tilde \theta_\lambda|_j + \lVert x_j\rVert_2
  \sqrt{\frac{1}{\lambda_*^2}
    G(\tilde \beta_\lambda, \tilde \theta_\lambda; \lambda^*)}
  < 1
\end{equation}
where
\[
  \tilde\theta_\lambda = \frac{y - X\tilde\beta_\lambda}{
    \max\big( \max_j|x_j^T(y - X\tilde\beta_\lambda)|, \lambda\big)}
\]
is a dual-feasible point~\cite{ndiaye2017}, which we can always obtain
by dual scaling whenever a candidate is infeasible. Using these facts,
we now arrive at \autoref{thm:look-ahead}, which is the main result of
this paper.

\begin{theorem}
  \label{thm:look-ahead}
  Let
  \((\tilde\beta_\lambda,\tilde\theta_\lambda)\) be
  a feasible primal--dual point for the solution to
  \eqref{eq:primal} and \eqref{eq:dual}. Then
  \(\big(\hat\beta_{\lambda^*}\big)_j = 0\) for any
  \[
    \lambda_* > \frac{-b + \sqrt{b^2 - 4ac}}{2a}
  \]
  where
  \[
    \begin{aligned}
      a & = \big( 1 - | x_j^T \tilde\theta_\lambda|\big)^2 -
      \frac 12 \tilde\theta_\lambda^T \tilde\theta_\lambda \lVert x_j\rVert_2^2      \\
      b & = \big(\tilde\theta_\lambda^T y - \lVert \tilde\beta_\lambda \rVert_1\big)
      \lVert x_j \rVert_2^2                                                          \\
      c & = - \frac 12 \lVert y - X\tilde\beta_\lambda\rVert_2^2
      \lVert x_j\rVert_2^2.                                                          \\
    \end{aligned}
  \]
\end{theorem}
\begin{proof}

\end{proof}

Note that there must be some \(\lambda_*^2\), for which it holds that
\[
  |X^T \tilde \theta_\lambda|_j +
  \lVert x_j\rVert_2 \sqrt{\frac{1}{\lambda_*^2} G(\tilde \beta_\lambda, \tilde \theta_\lambda; \lambda^*)}
  = 1
\]

\acknowledgements{Your acknowledgements.}

\bibliography{LookAheadScreening.bib}

\end{document}

### 2021-05-05 R/RcppExports.R

@@ -1,11 +1,11 @@
 # Generated by using Rcpp::compileAttributes() -> do not edit by hand
 # Generator token: 10BE3573-1514-4C36-9D1C-5A225CD40393
 
-lassoPathDense <- function(X, y, family, standardize, screening_type, path_length, maxit, tol_infeas, tol_gap, gamma, force_kkt_check, line_search, verbosity) {
-    .Call(`_LookAheadScreening_lassoPathDense`, X, y, family, standardize, screening_type, path_length, maxit, tol_infeas, tol_gap, gamma, force_kkt_check, line_search, verbosity)
+lassoPathDense <- function(X, y, standardize, screening_type, path_length, maxit, tol_infeas, tol_gap, force_kkt_check, verbosity) {
+    .Call(`_LookAheadScreening_lassoPathDense`, X, y, standardize, screening_type, path_length, maxit, tol_infeas, tol_gap, force_kkt_check, verbosity)
 }
 
-lassoPathSparse <- function(X, y, family, standardize, screening_type, path_length, maxit, tol_infeas, tol_gap, gamma, force_kkt_check, line_search, verbosity) {
-    .Call(`_LookAheadScreening_lassoPathSparse`, X, y, family, standardize, screening_type, path_length, maxit, tol_infeas, tol_gap, gamma, force_kkt_check, line_search, verbosity)
+lassoPathSparse <- function(X, y, standardize, screening_type, path_length, maxit, tol_infeas, tol_gap, force_kkt_check, verbosity) {
+    .Call(`_LookAheadScreening_lassoPathSparse`, X, y, standardize, screening_type, path_length, maxit, tol_infeas, tol_gap, force_kkt_check, verbosity)
 }
 

### 2021-05-05 R/lassoPath.R

@@ -2,39 +2,31 @@
 #'
 #' @param X The predictor matrix
 #' @param y The reponse vector
-#' @param family The name of the family, "gaussian" or "logistic"
 #' @param standardize Whether to standardize the predictors
 #' @param screening_type Screening rule
 #' @param path_length The (desired) length of the lasso path
 #' @param maxit Maximum number of iterations for Coordinate Descent loop
 #' @param tol_infeas Tolerance threshold for maximum infeasibility
 #' @param tol_gap Tolerance threshold for duality gap
-#' @param gamma Percent of strong approximation to add to Hessian approximation
 #' @param force_kkt_check Whether to force KKT checks even when screening rule
 #'   is safe
-#' @param line_search Use line search when `family = "binomial"`
 #' @param verbosity Controls the level of verbosity. 0 = no output.
 #'
 #' @export
 lassoPath <- function(X,
                       y,
-                      family = c("gaussian", "binomial"),
                       standardize = TRUE,
                       screening_type = c(
-                        "working",
-                        "edpp",
                         "gap_safe",
-                        "strong"
+                        "gap_safe_lookahead"
                       ),
                       path_length = 100L,
                       maxit = 1e5,
-                      tol_infeas = 1e-3,
-                      tol_gap = 1e-4,
-                      gamma = 0.01,
+                      tol_infeas = 1e-4,
+                      tol_gap = 1e-5,
                       force_kkt_check = FALSE,
-                      line_search = TRUE,
                       verbosity = 0) {
-  family <- match.arg(family)
+
   screening_type <- match.arg(screening_type)
 
   sparse <- inherits(X, "sparseMatrix")
@@ -48,32 +40,26 @@ lassoPath <- function(X,
     lassoPathSparse(
       X,
       y,
-      family,
       standardize,
       screening_type,
       path_length,
       maxit,
       tol_infeas,
       tol_gap,
-      gamma,
       force_kkt_check,
-      line_search,
       verbosity
     )
   } else {
     lassoPathDense(
       X,
       y,
-      family,
       standardize,
       screening_type,
       path_length,
       maxit,
       tol_infeas,
       tol_gap,
-      gamma,
       force_kkt_check,
-      line_search,
       verbosity
     )
   }

### 2021-05-05 experiments/arcenegolub_experiment.R

@@ -1,72 +1,0 @@
-#rm(list = ls())
-#graphics.off()
-library(HessianScreening)
-
-
-#d <- readRDS(file.path("data", paste0("leukemia-train", ".rds")))
-#d <- readRDS(file.path("data", paste0("arcene", ".rds")))
-#d <- readRDS(file.path("data", paste0("dorothea", ".rds")))
-#d <- readRDS(file.path("data", paste0("covtype", ".rds")))
-d <- readRDS(file.path("data", paste0("gisette-train", ".rds")))
-
-X <- d$X
-y <- d$y
-family <- "binomial"
-fita <- lassoPath(
-    X,
-    y,
-    family = family,
-    screening_type = "hessian",
-    hessian_warm_starts = TRUE,
-    log_hessian_update_type = "approx",
-    gamma = 0.01,
-    verify_hessian = FALSE,
-    verbosity = 0
-)
-fitf <- lassoPath(
-    X,
-    y,
-    family = family,
-    screening_type = "hessian",
-    hessian_warm_starts = TRUE,
-    log_hessian_update_type = "full",
-    gamma = 0.01,
-    verify_hessian = FALSE,
-    verbosity = 0
-)
-fit.w <- lassoPath(
-    X,
-    y,
-    family = family,
-    screening_type = "working",
-    verbosity = 0
-)
-cat("***************\n")
-cat("hessian:\n")
-cat("full = ", fit$full_time, "\n")
-cat("cd_time = ", sum(fit$cd_time), "\n")
-cat("kkt_time = ", sum(fit$corr_time), "\n")
-cat("hess_time = ", sum(fit$hess_time), "\n")
-cat("gradcorr_time", sum(fit$gradcorr_time), "\n")
-cat("duplicates_time", sum(fit$duplicates_time), "\n")
-cat("***************\n")
-# cat("working:\n")
-cat("full = ", fit.w$full_time, "\n")
-cat("cd_time = ", sum(fit.w$cd_time), "\n")
-cat("kkt_time = ", sum(fit.w$kkt_time), "\n")
-cat("duplicates_time", sum(fit$duplicates_time), "\n")
-
-par(mfrow=c(2,2))
-plot(fit$active, type = "l", lty = 2, ylim = c(0, max(c(fit$active, fit$screened))))
-lines(fit$screened)
-
-plot(fit$cd_time, type = "l")
-lines(fit.w$cd_time, col = "red")
[…]

### 2021-05-05 experiments/logistic-hessian-updates.R

@@ -1,152 +1,0 @@
-library(HessianScreening)
-
-n <- 2000
-p <- 10000
-rho <- 0.4
-dens <- 1
-
-d <-
-  generateDesign(n,
-                 p,
-                 family = "binomial",
-                 rho = rho,
-                 density = dens)
-
-X <- d$X
-y <- d$y
-
-fit_auto <-
-  lassoPath(
-    X,
-    y,
-    family = "binomial",
-    screening_type = "hessian",
-    log_hessian_update_type = "auto",
-    log_hessian_auto_threshold = ceiling(dens*min(n, p)),
-    verbosity = 0
-  )
-fit_full <-
-  lassoPath(
-    X,
-    y,
-    family = "binomial",
-    screening_type = "hessian",
-    log_hessian_update_type = "full"
-  )
-fit_approx <-
-  lassoPath(
-    X,
-    y,
-    family = "binomial",
-    screening_type = "hessian",
-    log_hessian_update_type = "approx"
-  )
-fit_working <-
-  lassoPath(X,
-            y,
-            family = "binomial",
-            screening_type = "working")
-
-fit_auto$full_time
-fit_full$full_time
-fit_approx$full_time
-fit_working$full_time
-
-library(tikzDevice)
-tikz("log-hessian.pdf")
-par(mfrow = c(2, 2))
-
-plot(
-  fit_auto$passes,
-  type = "l",
-  ylab = "passes",
-  ylim = c(
-    0,
-    max(
-      fit_full$passes,
-      fit_approx$passes,
-      fit_auto$passes,
-      fit_working$passes
-    )
-  )
-)
-lines(fit_full$passes, col = "dark orange")
-lines(fit_approx$passes, col = "aquamarine3")
-lines(fit_working$passes, col = "magenta")
-legend(
-  "topleft",
-  legend = c("auto", "full", "approx", "working"),
-  lwd = c(1, 1, 1, 1),
-  col = c("black", "dark orange", "aquamarine3", "magenta")
-)
-
-plot(
-  fit_auto$it_time,
-  type = "l",
-  ylab = "iteration time",
-  ylim = c(0, max(
-    c(fit_auto$it_time, fit_full$it_time, fit_approx$it_time)
-  ))
-)
-lines(fit_full$it_time, col = "dark orange")
-lines(fit_approx$it_time, col = "aquamarine3")
[…]

### 2021-05-05 experiments/realdata.R

@@ -1,4 +1,4 @@
-library(HessianScreening)
+library(LookAheadScreening)
 library(tidyr)
 library(tibble)
 library(Matrix)
@@ -7,31 +7,21 @@ printf <- function(...) invisible(cat(sprintf(...)))
 
 datasets <- c(
   "arcene",
-  "cadata",
-  "dorothea",
-  "gisette-train",
   "colon-cancer",
-  "leukemia-train",
-  "ijcnn1-train",
-  "YearPredictionMSD-train",
-  "madelon-train",
   "e2006-tfidf-train",
-  "e2006-log1p-train",
-  "rcv1-train",
-  "news20"
+  # "e2006-log1p-train",
+  # "rcv1-train",
+  # "news20"
 )
 
 g <- expand_grid(
   dataset = datasets,
-  screening_type = c("working", "hessian", "gap_safe", "edpp"),
-  family = NA,
+  screening_type = c("gap_safe", "gap_safe_lookahead"),
   n = NA,
   p = NA,
   density = NA,
   time = NA,
-  total_violations = NA,
   avg_screened = NA,
-  violations = list(NA),
   screened = list(NA),
   active = list(NA)
 )
@@ -48,18 +38,9 @@ for (i in seq_len(nrow(g))) {
 
   dens <- ifelse(inherits(X, "sparseMatrix"), Matrix::nnzero(X) / length(X), 1)
 
-  family <- if (length(unique(d$y)) == 2) "binomial" else "gaussian"
-
-  if (family == "binomial" && screening_type == "edpp") {
-    next
-  }
-
-  log_hessian_update_type <-
-    ifelse((1 - dens) * min(n, p) / max(n, p) * 10 < 0.1, "full", "approx")
-
   printf("%02d/%i %-10.10s %s\n", i, nrow(g), g$dataset[i], screening_type)
 
-  n_it <- 1
+  n_it <- 5
 
   time <- double(n_it)
 
@@ -67,10 +48,8 @@ for (i in seq_len(nrow(g))) {
     fit <- lassoPath(
       X,
       y,
-      family = family,
       screening_type = screening_type,
-      verbosity = 0,
-      log_hessian_update_type = log_hessian_update_type
+      verbosity = 0
     )
 
     time[k] <- fit$full_time
@@ -78,12 +57,8 @@ for (i in seq_len(nrow(g))) {
 
   g$n[i] <- n
   g$p[i] <- p
-  g$family[i] <- family
[…]

### 2021-05-05 experiments/sandbox.R

@@ -1,73 +1,46 @@
-library(HessianScreening)
+library(LookAheadScreening)
 
-#d <- readRDS(file.path("data", paste0("dorothea", ".rds")))
-d <- generateDesign(100, 10)
+d <- readRDS(file.path("data", paste0("e2006-tfidf-test", ".rds")))
+#d <- generateDesign(100, 10000, s = 10)
 X <- d$X
 y <- d$y
 n <- nrow(X)
 p <- ncol(X)
 family <- "gaussian"
-tol_gap <- 1e-4
-tol_infeas <- 1e-3
+tol_gap <- 1e-5
+tol_infeas <- 1e-4
 
-
-sparsity <- 1 - Matrix::nnzero(X) / length(X)
-sparsity * min(n, p) / max(n, p) * 10
-
-fit_hessian <- lassoPath(
+fit <- lassoPath(
     X,
     y,
-    family = family,
-    screening_type = "edpp",
-    verbosity = 1,
-    tol_gap = tol_gap,
-    tol_infeas = tol_infeas
-)
-
-fit_hessian$lookahead
-
-fit_working <- lassoPath(
-    X,
-    y,
-    family = family,
-    screening_type = "working",
+    screening_type = "gap_safe",
+    standardize = TRUE,
     verbosity = 1,
     tol_gap = tol_gap,
     tol_infeas = tol_infeas,
-    line_search = TRUE
-
-fit_edpp <- lassoPath(
-    X,
-    y,
-    family = family,
-    screening_type = "edpp",
-    verbosity = 1,
-    tol_gap = tol_gap,
-    tol_infeas = tol_infeas
-)
-fit_gapsafe <- lassoPath(
-    X,
-    y,
-    family = family,
-    screening_type = "gap_safe",
-    verbosity = 1,
-    tol_gap = tol_gap,
-    tol_infeas = tol_infeas
+    path_length = 100
 )
 
-# # cat("***************\n")
-# cat("hessian:\n")
-# cat("full = ", fit$full_time, "\n")
-# cat("cd_time = ", sum(fit$cd_time), "\n")
-# cat("kkt_time = ", sum(fit$kkt_time), "\n")
-# cat("hess_time = ", sum(fit$hess_time), "\n")
-# cat("gradcorr_time", sum(fit$gradcorr_time), "\n")
-# cat("***************\n")
-# cat("working:\n")
-# cat("full = ", fit.w$full_time, "\n")
[…]

### 2021-05-05 experiments/simulateddata.R

@@ -1,89 +1,94 @@
-
-library(HessianScreening)
-library(RColorBrewer)
-library(tibble)
-library(dplyr)
+library(LookAheadScreening)
+#library(tibble)
+#library(dplyr)
 library(tidyr)
-library(progress)
+library(readr)
+
+printf <- function(...) invisible(cat(sprintf(...)))
 
 g <- expand_grid(
-  np = list(c(5e4, 1e2), c(1e2, 5e4)),
-  n = NA,
-  p = NA,
-  rho = c(0, 0.3, 0.6),
-  family = c("binomial", "gaussian"),
-  screening_type = c("hessian", "working", "gap_safe", "edpp"),
+  n = 100,
+  p = 20000,
+  snr = 3,
+  s = 10,
+  rho = c(0, 0.4, 0.8),
+  screening_type = c("gap_safe", "gap_safe_lookahead"),
   path_length = 100,
   avg_screened = NA,
-  avg_violations = NA,
   time = list(NA),
   screened = list(NA),
-  active = list(NA)
+  active = list(NA),
+  step = list(NA)
 )
 
-n_it <- 20
-
-pb <- progress_bar$new(
-  format = "  simulating [:bar] :percent eta: :eta",
-  total = nrow(g) * n_it,
-  clear = FALSE,
-  width = 80
-)
+n_it <- 2
 
 for (i in seq_len(nrow(g))) {
-  np <- g$np[i]
-  n <- np[[1]][1]
-  p <- np[[1]][2]
   rho <- g$rho[i]
-  family <- g$family[i]
   screening_type <- g$screening_type[i]
   path_length <- g$path_length[i]
 
-  if (family == "binomial" && screening_type == "edpp") {
-    next
-  }
+  n <- g$n[i]
+  p <- g$p[i]
+  snr <- g$snr[i]
+  s <- g$s[i]
 
   avg_screened <- violations <- time <- double(n_it)
   active <- screened <- matrix(NA, nrow = n_it, ncol = path_length)
 
+  printf(
+    "%02d/%i n: %4d p: %4d rho: %1.1f %-10s\n",
+    i, nrow(g), n, p, rho, screening_type
+  )
+
   for (j in seq_len(n_it)) {
     set.seed(j)
-    pb$tick()
 
-    d <- generateDesign(n, p, family = family, rho = rho)
+    d <- generateDesign(n, p, family = "gaussian", rho = rho, snr = snr)
     X <- d$X
     y <- d$y
 
     fit <- lassoPath(
       X,
       y,
[…]

### 2021-05-05 experiments/test.R

@@ -1,8 +1,0 @@
-# test that
-library(HessianScreening)
-
-d <- generateDesign(100, 10)
-
-fit <- lassoPath(d$X, d$y)
-
-write.csv(fit$beta, "results/test.csv")

### 2021-05-05 figures/real.R

@@ -1,0 +1,66 @@
+library(ggplot2)
+library(dplyr)
+library(tidyr)
+library(lemon)
+library(tikzDevice)
+library(knitr)
+
+source("R/utils.R")
+
+theme_set(theme_minimal(base_size = 9))
+
+d <- readRDS("results/efficiency-realdata.rds")
+
+# https://stackoverflow.com/questions/54438495/shift-legend-into-empty-facets-of-a-faceted-plot-in-ggplot2
+shift_legend2 <- function(p) {
+  gp <- ggplotGrob(p)
+  facet.panels <- grep("^panel", gp[["layout"]][["name"]])
+  empty.facet.panels <- sapply(
+    facet.panels, function(i) "zeroGrob" %in% class(gp[["grobs"]][[i]])
+  )
+  empty.facet.panels <- facet.panels[empty.facet.panels]
+  empty.facet.panels <- gp[["layout"]][empty.facet.panels, ]
+  names <- empty.facet.panels$name
+  reposition_legend(p, "center", panel = names)
+}
+
+d2 <-
+  d %>%
+  mutate(screening_type = recode(screening_type,
+    "edpp" = "EDPP",
+    "gap_safe" = "Gap Safe",
+    "hessian" = "Hessian",
+    "strong" = "Strong"
+  )) %>%
+  drop_na() %>%
+  unnest(c(screened, active)) %>%
+  group_by(dataset, screening_type) %>%
+  mutate(screened = screened / p, active = active / p) %>%
+  mutate(step = seq_along(screened))
+
+cols <- c(
+  "#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442",
+  "#0072B2", "#D55E00", "#CC79A7"
+)
+
+pl <- ggplot(d2, aes(step)) +
+  facet_wrap(~dataset, nrow = 2) +
+  geom_line(aes(y = active), linetype = 2) +
+  geom_line(aes(y = screened, col = screening_type)) +
+  scale_y_continuous(
+    oob = function(x, ...) {
+      x
+    },
+    limits = c(0, 0.06)
+  ) +
+  theme(legend.title = element_blank()) +
+  scale_color_manual(values = cols) +
+  labs(x = "Step", y = "Active Predictors")
+
+file <- "figures/realdata-efficiency.tex"
+
+tikz(file, width = 5.6, height = 2.5, standAlone = TRUE)
+shift_legend2(pl)
+dev.off()
+
+renderPdf(file)

### 2021-05-05 figures/simulated-data-timings.R

@@ -1,107 +1,0 @@
-library(tibble)
-library(tidyr)
-library(dplyr)
-library(forcats)
-library(lattice)
-library(latticeExtra)
-library(tactile)
-library(tikzDevice)
-library(ggplot2)
-
-thm <- tactile.theme(c(12, 8),
-  plot.symbol = list(col = 1),
-  superpose.line = list(lty = 1:3)
-)
-
-d_raw <- readRDS("results/simulateddata.R") %>%
-  mutate(
-    screening_type = recode(
-      screening_type,
-      "hessian" = "Hessian",
-      "working" = "Working",
-      "edpp" = "EDPP",
-      "gap_safe" = "Gap-Safe"
-    ),
-    rho = as.factor(rho),
-    np = paste(n, p, sep = " x ")
-  ) %>%
-  select(np, n, p, rho, family, screening_type, time) %>%
-  unnest(time)
-
-d1 <-
-  d_raw %>%
-  mutate(
-    screening_type = as.factor(screening_type),
-    family = as.factor(family)
-  ) %>%
-  group_by(np, rho, family, screening_type) %>%
-  summarize(
-    meantime = mean(time),
-    se = sd(time / n())
-  ) %>%
-  mutate(
-    hi = meantime + se,
-    lo = meantime - se
-  )
-
-d2_gaussian <-
-  filter(d1, family == "gaussian")
-
-library(qualpalr)
-
-cols <- qualpal(4)
-
-cols <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
-
-tikz("figures/simulateddata-gaussian-timings.tex", width = 5, height = 3)
-xyplot(
-  meantime ~ rho | np,
-  groups = screening_type,
-  data = d2_gaussian,
-  type = "b",
-  auto.key = list(lines = TRUE, points = FALSE),
-  prepanel = prepanel.ci,
-  lower = d2_gaussian$lo,
-  upper = d2_gaussian$hi,
-  panel = function(...) {
-    panel.ci(..., alpha = 0.2, grid = TRUE)
-    panel.xyplot(...)
-  }
-)
-dev.off()
-
-library(ggthemes)
-
-tikz("figures/simulateddata-gaussian-timings.tex", width = 5, height = 3)
-pl <- ggplot(d2_gaussian, aes(rho,
-  meantime,
-  ymin = lo,
-  ymax = hi,
-  group = screening_type,
[…]

### 2021-05-05 figures/simulated.R

@@ -1,0 +1,77 @@
+library(tibble)
+library(tidyr)
+library(dplyr)
+library(forcats)
+library(tikzDevice)
+library(ggplot2)
+
+source("R/utils.R")
+
+theme_set(theme_minimal(base_size = 9))
+
+fw <- 5.6
+
+d_raw <- readRDS("results/simulateddata.rds") %>%
+  filter(screening_type != "strong", scenario != 2) %>%
+  mutate(
+    screening_type = recode(
+      screening_type,
+      "hessian" = "Hessian",
+      "working" = "Working",
+      "gap_safe" = "Gap Safe",
+      "edpp" = "EDPP"
+    ),
+    rho = as.factor(rho),
+    np = paste0("$n=", n, "$, $p=", p, "$"),
+    np = reorder(np, p),
+  ) %>%
+  select(np, n, p, rho, family, screening_type, time) %>%
+  unnest(time)
+
+d1 <-
+  d_raw %>%
+  mutate(
+    screening_type = as.factor(screening_type),
+    family = as.factor(family)
+  ) %>%
+  group_by(np, rho, family, screening_type) %>%
+  summarize(
+    meantime = mean(time),
+    se = sd(time / n())
+  ) %>%
+  mutate(
+    hi = meantime + se,
+    lo = meantime - se,
+    rel_time = meantime / min(meantime)
+  ) %>%
+  drop_na(meantime)
+
+cols <- c(
+  "#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442",
+  "#0072B2", "#D55E00", "#CC79A7"
+)
+
+options(
+  tikzDocumentDeclaration =
+    "\\documentclass[10pt]{article}\n\\usepackage{newtxtext,newtxmath}\n"
+)
+
+file <- "figures/simulateddata-timings.tex"
+tikz(file, width = fw, height = 2.5, standAlone = TRUE)
+ggplot(d1, aes(
+  rho,
+  rel_time,
+  fill = screening_type
+)) +
+  geom_col(position = "dodge", col = 1) +
+  facet_wrap(c("family", "np"), nrow = 1) +
+  scale_fill_manual(values = cols[1:5]) +
+  labs(
+    fill = "Screening",
+    x = "Correlation ($\\rho$)",
+    y = "Time"
+  ) +
+  theme(legend.position = c(0.1, 0.7), legend.title = element_blank())
+dev.off()
+
+renderPdf("figures/simulateddata-timings.tex")

### 2021-05-05 figures/tfidf.R

@@ -1,0 +1,102 @@
+
+library(ggplot2)
+library(dplyr)
+library(tidyr)
+library(tikzDevice)
+
+source("R/utils.R")
+
+d <- readRDS("results/simulateddata.rds")
+
+theme_set(theme_minimal(base_size = 9))
+
+cols <- c(
+  "#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442",
+  "#0072B2", "#D55E00", "#CC79A7"
+)
+
+options(
+  tikzDocumentDeclaration =
+    "\\documentclass[10pt]{article}\n\\usepackage{newtxtext,newtxmath}\n"
+)
+
+d2 <-
+  d %>%
+  mutate(
+    np = paste0("$n=", n, "$, $p=", p, "$"),
+    screening_type = recode(
+      screening_type,
+      "hessian" = "Hessian",
+      "working" = "Working",
+      "gap_safe" = "Gap Safe",
+      "edpp" = "EDPP",
+      "strong" = "Strong"
+    )
+  ) %>%
+  filter(screening_type != "Working") %>%
+  drop_na() %>%
+  unnest(c(screened, active, step)) %>%
+  group_by(family, rho, scenario, screening_type) %>%
+  mutate(screened = screened / p, active = active / p)
+
+rho_labeller <- function(labels, multi_line = TRUE, sep = ":", ...) {
+  value <- label_value(labels, multi_line = multi_line)
+
+  out <- paste0("$\\rho = ", value, "$")
+  #  list(unname(unlist(out)))
+  out
+}
+
+d2_gaussian <- filter(d2, family == "gaussian")
+d2_gaussian_active <-
+  d2_gaussian %>%
+  ungroup() %>%
+  group_by(family, rho, np, step) %>%
+  summarize(avg_active = mean(active, na.rm = TRUE))
+
+f1 <- "figures/simulateddata-efficiency-gaussian.tex"
+tikz(f1, width = 5.6, height = 2.5, standAlone = TRUE)
+ggplot(d2_gaussian, aes(step)) +
+  facet_grid(np ~ rho,
+    labeller = labeller(
+      np = label_value,
+      rho = rho_labeller
+    )
+  ) +
+  geom_line(aes(x = step, y = avg_active),
+    linetype = 2,
+    data = d2_gaussian_active
+  ) +
+  geom_line(aes(y = screened, col = screening_type, group = screening_type)) +
+  theme(legend.title = element_blank()) +
[…]

### 2021-05-05 src/RcppExports.cpp

@@ -7,55 +7,49 @@
 using namespace Rcpp;
 
 // lassoPathDense
-Rcpp::List lassoPathDense(arma::mat X, arma::vec y, const std::string family, const bool standardize, const std::string screening_type, const arma::uword path_length, const arma::uword maxit, const double tol_infeas, const double tol_gap, const double gamma, const bool force_kkt_check, const bool line_search, const arma::uword verbosity);
-RcppExport SEXP _LookAheadScreening_lassoPathDense(SEXP XSEXP, SEXP ySEXP, SEXP familySEXP, SEXP standardizeSEXP, SEXP screening_typeSEXP, SEXP path_lengthSEXP, SEXP maxitSEXP, SEXP tol_infeasSEXP, SEXP tol_gapSEXP, SEXP gammaSEXP, SEXP force_kkt_checkSEXP, SEXP line_searchSEXP, SEXP verbositySEXP) {
+Rcpp::List lassoPathDense(arma::mat X, arma::vec y, const bool standardize, const std::string screening_type, const arma::uword path_length, const arma::uword maxit, const double tol_infeas, const double tol_gap, const bool force_kkt_check, const arma::uword verbosity);
+RcppExport SEXP _LookAheadScreening_lassoPathDense(SEXP XSEXP, SEXP ySEXP, SEXP standardizeSEXP, SEXP screening_typeSEXP, SEXP path_lengthSEXP, SEXP maxitSEXP, SEXP tol_infeasSEXP, SEXP tol_gapSEXP, SEXP force_kkt_checkSEXP, SEXP verbositySEXP) {
 BEGIN_RCPP
     Rcpp::RObject rcpp_result_gen;
     Rcpp::RNGScope rcpp_rngScope_gen;
     Rcpp::traits::input_parameter< arma::mat >::type X(XSEXP);
     Rcpp::traits::input_parameter< arma::vec >::type y(ySEXP);
-    Rcpp::traits::input_parameter< const std::string >::type family(familySEXP);
     Rcpp::traits::input_parameter< const bool >::type standardize(standardizeSEXP);
     Rcpp::traits::input_parameter< const std::string >::type screening_type(screening_typeSEXP);
     Rcpp::traits::input_parameter< const arma::uword >::type path_length(path_lengthSEXP);
     Rcpp::traits::input_parameter< const arma::uword >::type maxit(maxitSEXP);
[…]

### 2021-05-05 src/binomial.h

@@ -1,109 +1,0 @@
-#pragma once
-
-#include <RcppArmadillo.h>
-
-#include "prox.h"
-#include "utils.h"
-
-using namespace arma;
-
-class Binomial : public Model
-{
-public:
-  vec expXbeta;
-  vec pr;
-  vec w;
-
-  const double p_min = 1e-5;
-  const double p_max = 1 - p_min;
-
-  Binomial(const std::string family,
-           vec& y,
-           vec& beta,
-           vec& residual,
-           vec& Xbeta,
-           vec& c,
-           const vec& X_mean_scaled,
-           const vec& X_norms_squared,
-           const uword n,
-           const uword p,
-           const bool standardize)
-    : Model{ family,          y, beta, residual,   Xbeta, c, X_mean_scaled,
-             X_norms_squared, n, p,    standardize }
-    , expXbeta(y.n_elem, fill::zeros)
-    , pr(y.n_elem, fill::zeros)
-    , w(y.n_elem, fill::zeros)
-  {}
-
-  double primal(const double lambda, const uvec& screened_set)
-  {
-    return -sum(y % Xbeta - log1p(expXbeta)) +
-           lambda * norm(beta(screened_set), 1);
-  }
-
-  double dual() { return -sum(pr % log(pr) + (1 - pr) % log(1 - pr)); }
-
-  double scaledDual(const double lambda)
-  {
-    if (dual_scale == 0) {
-      return 0;
-    } else {
-      double alpha = lambda / dual_scale;
-
-      vec prx = clamp(y - alpha * residual, p_min, p_max);
-
-      return -sum(prx % log(prx) + (1 - prx) % log(1 - prx));
-    }
-  }
-
-  double deviance() { return -2 * sum(y % Xbeta - log1p(expXbeta)); }
-
-  double hessianTerm(const mat& X, const uword j)
-  {
-    return std::max(dot(square(X.col(j)), w), std::sqrt(datum::eps));
-  }
-
-  double hessianTerm(const sp_mat& X, const uword j)
-  {
-    double out = dot(square(X.col(j)), w);
-
-    if (standardize) {
-      out += std::pow(X_mean_scaled(j), 2) * sum(w) -
-             2 * dot(X.col(j), w) * X_mean_scaled(j);
-    }
-
-    return std::max(out, std::sqrt(datum::eps));
-  }
-
-  void updateResidual()
-  {
[…]

### 2021-05-05 src/lassoPath.cpp

@@ -3,7 +3,6 @@
 #include "setupModel.h"
 #include "model.h"
 #include "colNormsSquared.h"
-#include "binomial.h"
 #include "gaussian.h"
 #include "checkStoppingConditions.h"
 #include "kktCheck.h"
@@ -18,33 +17,17 @@ template<typename T>
 Rcpp::List
 lassoPath(T& X,
           vec& y,
-          const std::string family,
           const bool standardize,
           const std::string screening_type,
           const uword path_length,
           const uword maxit,
           const double tol_infeas,
           const double tol_gap,
-          const double gamma,
           const bool force_kkt_check,
-          const bool line_search,
           const uword verbosity)
 {
   const uword n = X.n_rows;
   const uword p = X.n_cols;
-
-  if (family == "binomial") {
-    vec y_unique = sort(unique(y));
-
-    if (y_unique.n_elem != 2) {
-      Rcpp::stop("y has more than two unique values");
-    } else if (y_unique(0) != 0 || y_unique(1) != 1) {
-      Rcpp::stop("y is not in {0, 1}");
-    }
-
-    if (screening_type == "edpp")
-      Rcpp::stop("EDPP cannot be used in logistic regression");
-  }
 
   umat lookaheads(X.n_cols, 0);
 
@@ -75,7 +58,7 @@ lassoPath(T& X,
     X_norms_squared.fill(n);
   }
 
-  auto model = setupModel(family,
+  auto model = setupModel("gaussian",
                           y,
                           beta,
                           residual,
@@ -88,7 +71,6 @@ lassoPath(T& X,
                           standardize);
 
   model->standardizeY();
-
   model->updateResidual();
   model->updateCorrelation(X, regspace<uvec>(0, p - 1));
 
@@ -111,7 +93,6 @@ lassoPath(T& X,
   std::vector<uword> n_passes;
   std::vector<uword> n_refits;
   std::vector<double> n_screened;
-  std::vector<uword> n_strong;
   std::vector<uword> n_violations;
 
   uvec active(p, fill::zeros);
@@ -123,8 +104,8 @@ lassoPath(T& X,
   uvec active_prev = active;
   uvec ever_active = active;
   uvec screened = active;
-  uvec strong = active;
-  uvec strong_set = find(strong);
+
+  uvec lookahead(p, fill::zeros);
 
   uvec violations(p, fill::zeros);
 
@@ -178,12 +159,15 @@ lassoPath(T& X,
 
       double t0 = timer.toc();
 
[…]

### 2021-05-05 src/model.h

@@ -166,7 +166,6 @@ public:
     const uword maxit,
     const double tol_gap,
     const double tol_infeas,
-    const bool line_search,
     const uword verbosity)
   {
     const uword p = X.n_cols;
@@ -198,14 +197,14 @@ public:
       updateResidual();
 
       while (it < maxit) {
-        it++;
 
         if (verbosity >= 2) {
-          Rprintf("    iter: %i\n", it);
+          Rprintf("    iter: %i\n", it + 1);
         }
 
-        if (screening_type == "gap_safe" && (it - 1) % screen_interval == 0) {
-          if (it > 1) {
+        if (it % screen_interval == 0 &&
+            !(screening_type == "gap_safe_lookahead" && it == 0)) {
+          if (it > 0) {
             updateLinearPredictor(X, screened_set);
             updateResidual();
           }
@@ -219,10 +218,8 @@ public:
 
           double r_screen{ 0 };
 
-          if (screening_type == "gap_safe") {
-            XTcenter = c / dual_scale;
-            r_screen = safeScreeningRadius(std::max(duality_gap, 0.0), lambda);
-          }
+          XTcenter = c / dual_scale;
+          r_screen = safeScreeningRadius(std::max(duality_gap, 0.0), lambda);
 
           safeScreening(screened, screened_set, X, XTcenter, r_screen);
         }
@@ -238,39 +235,8 @@ public:
             prox(beta_j_old + c(j) / hess_j, lambda / hess_j) - beta(j);
 
           if (v != 0) {
-            if (family == "binomial" && line_search) {
-              // line search (see J. D. Lee, Y. Sun, and M. A. Saunders,
-              // “Proximal Newton-type methods for minimizing composite
-              // functions,” arXiv:1206.1623 [cs, math, stat], Mar. 2014,
-              // Accessed: Jan. 12, 2020. [Online]. Available:
-              // http://arxiv.org/abs/1206.1623)
-
-              double primal_value_old = primal(lambda, screened_set);
-
-              while (true) {
-                double beta_j_prev = beta(j);
-
-                beta(j) = beta_j_old + t(j) * v;
-                adjustResidual(X, j, beta(j) - beta_j_prev);
-
-                primal_value = primal(lambda, screened_set);
-
-                double eta = -c(j) * v + lambda * (std::abs(beta_j_old + v) -
-                                                   std::abs(beta_j_old));
-
-                if (primal_value * (1 - std::sqrt(datum::eps)) <=
[…]

### 2021-05-05 src/screenPredictors.h

@@ -2,16 +2,20 @@
 
 #include <RcppArmadillo.h>
 
+#include "model.h"
+
 using namespace arma;
 
 template<typename T>
-std::tuple<uvec, uvec>
-screenPredictors(const std::string screening_type,
-                 const uvec& strong,
+void
+screenPredictors(uvec& lookahead,
+                 uvec& screened,
+                 const std::unique_ptr<Model>& model,
+                 const std::string screening_type,
                  const uvec& ever_active,
                  const vec& residual,
-                 const vec& c,
-                 const vec& c_grad,
+                 const vec& corr,
+                 const vec& corr_grad,
                  const T& X,
                  const vec& X_norms_squared,
                  const vec& X_mean_scaled,
@@ -19,64 +23,72 @@ screenPredictors(const std::string screening_type,
                  const vec& lambdas,
                  const double lambda,
                  const double lambda_next,
-                 const double gamma,
                  const uword step,
                  const bool standardize)
 {
-  uvec screened(X.n_cols);
-  uvec lookahead(X.n_cols, fill::zeros);
-  lookahead.fill(100);
+  uvec screened_set = find(screened);
+  uword p = X.n_cols;
 
-  if (screening_type == "working") {
-    screened = ever_active;
-  } else if (screening_type == "strong") {
-    screened = strong;
-  } else if (screening_type == "hessian" ||
-             screening_type == "hessian_adaptive") {
-    vec c_pred = c + c_grad * (lambda_next - lambda);
-    screened = (abs(c_pred) + gamma * (lambda - lambda_next) > lambda_next) ||
-               ever_active;
-  } else if (screening_type == "gap_safe") {
-    // we use the active set strategy for the gap safe rules, so we use the
-    // ever-active predictors to get a good warm start
-    screened = ever_active;
-  } else if (screening_type == "edpp") {
-    double dual_scale = std::max(lambda, max(abs(c)));
-    vec v1 = y / lambda - residual / dual_scale;
-    vec v2 = y / lambda_next - residual / dual_scale;
+  if (screening_type == "gap_safe") {
+    screened.fill(true);
[…]

### 2021-05-05 src/setupModel.h

@@ -3,7 +3,6 @@
 #include <RcppArmadillo.h>
 
 #include "model.h"
-#include "binomial.h"
 #include "gaussian.h"
 
 using namespace arma;
@@ -21,19 +20,6 @@ setupModel(const std::string family,
            const uword p,
            const bool standardize)
 {
-  if (family == "binomial")
-    return std::make_unique<Binomial>(family,
-                                      y,
-                                      beta,
-                                      residual,
-                                      Xbeta,
-                                      c,
-                                      X_mean_scaled,
-                                      X_norms_squared,
-                                      n,
-                                      p,
-                                      standardize);
-
   return std::make_unique<Gaussian>(family,
                                     y,
                                     beta,

### 2021-05-05 tables/realdata.R

@@ -1,10 +1,8 @@
-library(lattice)
 library(tibble)
 library(dplyr)
 library(tidyr)
 library(readr)
 library(forcats)
-library(kableExtra)
 library(stringr)
 
 d_raw <- readRDS("results/realdata.rds")

### 2021-05-05 tests/testthat/test-lambda-grid.R

@@ -1,4 +1,4 @@
-library(HessianScreening)
+library(LookAheadScreening)
 
 test_that("lambda grid calculations are correct", {
   for (p in c(10, 100)) {
@@ -13,9 +13,7 @@ test_that("lambda grid calculations are correct", {
     X <- scale(X)
     y <- y - mean(y)
 
-    family <- "gaussian"
-
-    res_work <- lassoPath(X, y, family = family)
+    res_work <- lassoPath(X, y)
     res_glmn <- glmnet::glmnet(X, y, intercept = FALSE)
 
     n_lambda <- min(length(res_work$lambda), length(res_glmn$lambda))

### 2021-05-05 tests/testthat/test-logistic.R

@@ -1,36 +1,0 @@
-test_that("compare against glmnet with real data", {
-  suppressMessages(library(glmnet))
-
-  datalist <- c("heart", "leukemia")
-
-  for (dataset in datalist) {
-    data(list = list(dataset))
-    d <- get(dataset)
-    X <- d$X
-    y <- d$y
-
-    fit_ours <- lassoPath(X,
-      y,
-      "binomial",
-      screening_type = "working",
-      standardize = FALSE
-    )
-
-    lambda <- fit_ours$lambda / nrow(X)
-
-    fit_gnet <- glmnet(X,
-      y,
-      "binomial",
-      lambda = lambda,
-      intercept = FALSE,
-      standardize = FALSE
-    )
-
-    ours_dev <- fit_ours$dev_ratio
-    gnet_dev <- fit_gnet$dev.ratio
-
-    dev_diff <- pmax(gnet_dev - ours_dev, 0)
-
-    expect_equal(dev_diff, rep(0, length(dev_diff)), tolerance = 1e-3)
-  }
-})

### 2021-05-05 tests/testthat/test-screening.R

@@ -5,35 +5,25 @@ test_that("screening methods work", {
   p <- 200
 
   for (density in c(1, 0.5)) {
+    d <- generateDesign(n, p)
 
-    for (family in c("gaussian", "binomial")) {
-      d <- generateDesign(n, p, family = family)
+    X <- d$X
+    y <- d$y
 
-      X <- d$X
-      y <- d$y
+    fit_gap <- lassoPath(X, y, screening_type = "gap_safe")
 
-      fit_work <- lassoPath(X, y, family = family, screening_type = "working")
+    for (screening_type in c("gap_safe_lookahead")) {
+      fit <- lassoPath(X,
+                       y,
+                       screening_type = screening_type,
+                       verbosity = 0,
+                       force_kkt_check = TRUE)
 
-      for (screening_type in c("hessian", "working", "strong", "gap_safe")) {
-        if (family == "gaussian" && screening_type == "edpp") {
-          next
-        }
+      steps <- 1:min(length(fit$lambda), length(fit_gap$lambda))
+      expect_equal(fit_gap$dev[steps], fit$dev[steps],
+                    tolerance = 1e-3)
 
-        fit <- lassoPath(X,
-                         y,
-                         family = family,
-                         screening_type = screening_type,
-                         verbosity = 0,
-                         force_kkt_check = TRUE)
-
-        steps <- 1:min(length(fit$lambda), length(fit_work$lambda))
-        expect_equal(fit_work$dev[steps], fit$dev[steps],
-                     tolerance = 1e-3)
-
-        if (screening_type %in% c("gap_safe")) {
-          expect_equal(sum(fit$violations), 0)
-        }
-      }
+      expect_equal(sum(fit$violations), 0)
     }
   }
 })

### 2021-05-05 tests/testthat/test-simulated.R

@@ -1,12 +1,10 @@
-test_that("gaussian and logistic models for simulated data", {
-  library(HessianScreening)
+test_that("gaussian models for simulated data", {
+  library(LookAheadScreening)
   library(glmnet)
 
   grid <- expand.grid(
     np = list(c(100, 5), c(50, 100)),
     density = c(0.2, 1),
-    screening_type = c("working", "hessian"),
-    family = c("gaussian", "binomial"),
     standardize = c(FALSE),
     stringsAsFactors = FALSE
   )
@@ -19,28 +17,21 @@ test_that("gaussian and logistic models for simulated data", {
     np <- g$np[[1]]
     n <- np[1]
     p <- np[2]
-    family <- g$family
     standardize <- g$standardize
-    screening_type <- g$screening_type
 
     data <- generateDesign(
       n,
       p,
-      family = g$family,
       density = g$density
     )
 
     X <- data$X
     y <- data$y
-
-    if (family == "gaussian") {
-      y <- y - mean(y)
-    }
+    y <- y - mean(y)
 
     fit_glmnet <- glmnet(
       X,
       y,
-      family = family,
       intercept = FALSE,
       standardize = standardize
     )
@@ -48,12 +39,10 @@ test_that("gaussian and logistic models for simulated data", {
     fit_ours <- lassoPath(
       X,
       y,
-      family,
-      screening_type = screening_type,
       standardize = standardize
     )
 
-    n_lambda <- min(length(fit_glmnet$lambda), length(fit_ours$lambda))
+    n_lambda <- min(ncol(fit_glmnet$beta), ncol(fit_ours$beta))
 
     glmnet_lambda <- fit_glmnet$lambda[1:n_lambda] * n
     ours_lambda <- fit_ours$lambda[1:n_lambda]

### 2021-05-05 tests/testthat/test-sparse.R

@@ -2,17 +2,15 @@ test_that("sparse and dense methods are equivalent", {
   n <- 100
   p <- 5
 
-  for (family in c("gaussian", "binomial")) {
-    d <- generateDesign(n, p, family = family, density = 0.5)
-    X <- d$X
-    y <- d$y
-    for (standardize in c(TRUE, FALSE)) {
-      fit_dense <- lassoPath(as.matrix(X), y, family, standardize = standardize)
-      fit_sparse <- lassoPath(X, y, family, standardize = standardize)
+  d <- generateDesign(n, p, density = 0.5)
+  X <- d$X
+  y <- d$y
+  for (standardize in c(TRUE, FALSE)) {
+    fit_dense <- lassoPath(as.matrix(X), y, standardize = standardize)
+    fit_sparse <- lassoPath(X, y, standardize = standardize)
 
-      expect_equal(fit_dense$lambda, fit_sparse$lambda)
-      expect_equal(fit_dense$dev_ratio, fit_sparse$dev_ratio)
-      expect_equal(fit_dense$beta, fit_sparse$beta)
-    }
+    expect_equal(fit_dense$lambda, fit_sparse$lambda)
+    expect_equal(fit_dense$dev_ratio, fit_sparse$dev_ratio)
+    expect_equal(fit_dense$beta, fit_sparse$beta)
   }
 })

### 2021-05-05 src/lassoPath.cpp
Fix some redundancies in screening rule

@@ -106,6 +106,7 @@ lassoPath(T& X,
   uvec screened = active;
 
   uvec lookahead(p, fill::zeros);
+  uvec lookahead_disabled(p, fill::zeros);
 
   uvec violations(p, fill::zeros);
 
@@ -133,14 +134,12 @@ lassoPath(T& X,
   uword i = 0;
 
   while (true) {
-    i++;
-
-    lambda = lambdas(i - 1);
+    lambda = lambdas(i);
 
     double it_time = timer.toc();
 
     if (verbosity >= 1) {
-      Rprintf("step: %i, lambda: %.2f\n", i, lambda);
+      Rprintf("step: %i, lambda: %.2f\n", i + 1, lambda);
     }
 
     vec beta_prev = beta;
@@ -175,7 +174,6 @@ lassoPath(T& X,
                    null_primal,
                    screening_type,
                    first_run,
-                   i,
                    maxit,
                    tol_gap,
                    tol_infeas,
@@ -218,7 +216,7 @@ lassoPath(T& X,
       Rcpp::checkUserInterrupt();
     }
 
-    if (i > 1) {
+    if (i > 0) {
       active = beta != 0;
       active_set = find(active);
       s.zeros();
@@ -240,7 +238,7 @@ lassoPath(T& X,
       Rprintf("  active: %i, new active: %i\n", active_set.n_elem, new_active);
     }
 
-    bool stop_path = checkStoppingConditions(i,
+    bool stop_path = checkStoppingConditions(i + 1,
                                              n,
                                              p,
                                              path_length,
@@ -258,9 +256,10 @@ lassoPath(T& X,
       break;
     }
 
-    double lambda_next = lambdas(i);
+    double lambda_next = lambdas(i + 1);
 
     screenPredictors(lookahead,
+                     lookahead_disabled,
                      screened,
                      model,
                      screening_type,
@@ -286,6 +285,8 @@ lassoPath(T& X,
     it_times.emplace_back(timer.toc() - it_time);
 
     Rcpp::checkUserInterrupt();
+
+    ++i;
   }
 
   rescaleCoefficients(betas, X_mean, X_sd, y_center);

### 2021-05-05 src/model.h

@@ -162,7 +162,6 @@ public:
     const double null_primal,
     const std::string screening_type,
     const bool first_run,
-    const uword step,
     const uword maxit,
     const double tol_gap,
     const double tol_infeas,
@@ -179,13 +178,7 @@ public:
     double dual_value = dual();
     double duality_gap = primal_value - dual_value;
 
-    // line search parameters
-    const double a = 0.1;
-    const double b = 0.5;
-
     vec XTcenter(p);
-
-    vec t(p, fill::ones); // learning rates
 
     const uword screen_interval = 10;
 
@@ -197,7 +190,6 @@ public:
       updateResidual();
 
       while (it < maxit) {
-
         if (verbosity >= 2) {
           Rprintf("    iter: %i\n", it + 1);
         }

### 2021-05-05 src/screenPredictors.h

@@ -9,6 +9,7 @@ using namespace arma;
 template<typename T>
 void
 screenPredictors(uvec& lookahead,
+                 uvec& lookahead_disabled,
                  uvec& screened,
                  const std::unique_ptr<Model>& model,
                  const std::string screening_type,
@@ -42,7 +43,7 @@ screenPredictors(uvec& lookahead,
     double residual_sq_norm2 = std::pow(norm(residual), 2);
 
     for (uword j = 0; j < p; ++j) {
-      if (ever_active(j) || lookahead(j) >= step)
+      if (ever_active(j) || lookahead(j) > step || lookahead_disabled(j))
         continue;
 
       double a = std::pow(1 - std::abs(corr(j) / dual_scale), 2) -
@@ -62,7 +63,9 @@ screenPredictors(uvec& lookahead,
       if (any(tmp)) {
         lookahead(j) = as_scalar(find(tmp, 1, "last"));
       } else {
+        // stop considering predictors that are not captured by the rule
         lookahead(j) = 0;
+        lookahead_disabled(j) = true;
       }
     }
 
@@ -89,6 +92,6 @@ screenPredictors(uvec& lookahead,
     //   }
     // }
 
-    screened = lookahead < (step) || ever_active;
+    screened = lookahead <= step || ever_active;
   }
 }

### 2021-05-06 R/generateDesign.R
Revert file permissions

@@ -16,14 +16,12 @@
 #' @export
 generateDesign <- function(n,
                            p,
-                           family = c("gaussian", "binomial"),
                            density = 1,
                            rho = 0,
                            s = 5,
                            rho_type = c("constant", "auto"),
                            beta_type = 1,
                            snr = 2) {
-  family <- match.arg(family)
   rho_type <- match.arg(rho_type)
 
   s <- min(s, p)
@@ -61,19 +59,15 @@ generateDesign <- function(n,
       sigma <- sqrt((t(beta) %*% Sigma %*% beta) / snr)
     } else if (rho_type == "constant") {
       X <- matrix(rnorm(n), n, p) * sqrt(rho) +
-        sqrt(1 - rho) * matrix(rnorm(n*p), n, p)
+        sqrt(1 - rho) * matrix(rnorm(n * p), n, p)
       sigma <- sqrt((rho * sum(beta)^2 + (1 - rho) * sum(beta^2)) / snr)
     }
   } else {
-    Sigma <- diag(p)
+    Sigma <- Matrix::Diagonal(p)
     sigma <- sqrt((t(beta) %*% Sigma %*% beta) / snr)
   }
 
   y <- as.vector(X %*% beta) + as.vector(sigma) * rnorm(n)
-
-  if (family == "binomial") {
-    y <- (sign(y) + 1) / 2
-  }
 
   list(X = X, y = y)
 }

### 2021-05-06 experiments/realdata.R

@@ -1,17 +1,20 @@
+
 library(LookAheadScreening)
 library(tidyr)
 library(tibble)
 library(Matrix)
+library(readr)
 
 printf <- function(...) invisible(cat(sprintf(...)))
 
 datasets <- c(
+  # region "e2006-tfidf-train",
+  # "e2006-log1p-train",
   "arcene",
   "colon-cancer",
-  "e2006-tfidf-train",
-  # "e2006-log1p-train",
-  # "rcv1-train",
-  # "news20"
+  "duke-breast-cancer"
+  # "gisette-train",
+  # "dorothea"
 )
 
 g <- expand_grid(
@@ -21,7 +24,9 @@ g <- expand_grid(
   p = NA,
   density = NA,
   time = NA,
+  total_violations = NA,
   avg_screened = NA,
+  violations = list(NA),
   screened = list(NA),
   active = list(NA)
 )
@@ -37,10 +42,11 @@ for (i in seq_len(nrow(g))) {
   p <- ncol(X)
 
   dens <- ifelse(inherits(X, "sparseMatrix"), Matrix::nnzero(X) / length(X), 1)
+  sparsity <- 1 - dens
 
   printf("%02d/%i %-10.10s %s\n", i, nrow(g), g$dataset[i], screening_type)
 
-  n_it <- 5
+  n_it <- 100
 
   time <- double(n_it)
 
@@ -53,16 +59,26 @@ for (i in seq_len(nrow(g))) {
     )
 
     time[k] <- fit$full_time
+
+    # stop if standard error is within 2.5% of mean
+    if (k > 1) {
+      time_se <- sd(time[1:k]) / sqrt(k)
+
+      if (time_se / mean(time[1:k]) < 0.025) {
+        break
+      }
+    }
   }
 
   g$n[i] <- n
   g$p[i] <- p
-  g$time[i] <- mean(time)
+  g$time[i] <- mean(time[1:k])
   g$density[i] <- dens
+  g$avg_screened[i] <- mean(fit$active / fit$screened)
   g$screened[i] <- list(fit$screened)
   g$active[i] <- list(fit$active)
 }
 
 cat("DONE!\n")
 
-saveRDS(g, "results/realdata.rds")
+save_rds(g, "results/realdata.rds")

### 2021-05-06 experiments/sandbox.R

@@ -1,12 +1,11 @@
 library(LookAheadScreening)
 
-d <- readRDS(file.path("data", paste0("e2006-tfidf-test", ".rds")))
-#d <- generateDesign(100, 10000, s = 10)
+# d <- readRDS(file.path("data", paste0("e2006-tfidf-test", ".rds")))
+d <- generateDesign(100, 50000, s = 5, density = 1)
 X <- d$X
 y <- d$y
 n <- nrow(X)
 p <- ncol(X)
-family <- "gaussian"
 tol_gap <- 1e-5
 tol_infeas <- 1e-4
 
@@ -15,7 +14,7 @@ fit <- lassoPath(
     y,
     screening_type = "gap_safe",
     standardize = TRUE,
-    verbosity = 1,
+    verbosity = 0,
     tol_gap = tol_gap,
     tol_infeas = tol_infeas,
     path_length = 100
@@ -27,7 +26,7 @@ fit_lookahead <- lassoPath(
     screening_type = "gap_safe_lookahead",
     force_kkt_check = FALSE,
     standardize = TRUE,
-    verbosity = 1,
+    verbosity = 0,
     tol_gap = tol_gap,
     tol_infeas = tol_infeas,
     path_length = 100

### 2021-05-06 experiments/simulateddata.R

@@ -1,6 +1,6 @@
 library(LookAheadScreening)
-#library(tibble)
-#library(dplyr)
+# library(tibble)
+# library(dplyr)
 library(tidyr)
 library(readr)
 
@@ -8,12 +8,11 @@ printf <- function(...) invisible(cat(sprintf(...)))
 
 g <- expand_grid(
   n = 100,
-  p = 20000,
-  snr = 3,
-  s = 10,
-  rho = c(0, 0.4, 0.8),
+  p = 50000,
+  snr = c(0.1, 1, 6),
+  s = c(10),
   screening_type = c("gap_safe", "gap_safe_lookahead"),
-  path_length = 100,
+  path_length = c(100),
   avg_screened = NA,
   time = list(NA),
   screened = list(NA),
@@ -21,10 +20,9 @@ g <- expand_grid(
   step = list(NA)
 )
 
-n_it <- 2
+n_it <- 3
 
 for (i in seq_len(nrow(g))) {
-  rho <- g$rho[i]
   screening_type <- g$screening_type[i]
   path_length <- g$path_length[i]
 
@@ -37,14 +35,14 @@ for (i in seq_len(nrow(g))) {
   active <- screened <- matrix(NA, nrow = n_it, ncol = path_length)
 
   printf(
-    "%02d/%i n: %4d p: %4d rho: %1.1f %-10s\n",
-    i, nrow(g), n, p, rho, screening_type
+    "%02d/%i n: %4d p: %4d snr: %.1f %-10s\n",
+    i, nrow(g), n, p, snr, screening_type
   )
 
   for (j in seq_len(n_it)) {
     set.seed(j)
 
-    d <- generateDesign(n, p, family = "gaussian", rho = rho, snr = snr)
+    d <- generateDesign(n, p, snr = snr)
     X <- d$X
     y <- d$y
 
@@ -90,5 +88,11 @@ for (i in seq_len(nrow(g))) {
   g$active[i] <- list(active)
   g$step[i] <- list(1:path_length)
 }
+
+library(dplyr)
+
+unnest(g, time) %>%
+  group_by(snr, path_length, screening_type) %>%
+  summarize(mean_time = mean(time))
 
 save_rds(g, "results/simulateddata.rds")

### 2021-05-06 src/model.h

@@ -194,8 +194,7 @@ public:
           Rprintf("    iter: %i\n", it + 1);
         }
 
-        if (it % screen_interval == 0 &&
-            !(screening_type == "gap_safe_lookahead" && it == 0)) {
+        if (it % screen_interval == 0) {
           if (it > 0) {
             updateLinearPredictor(X, screened_set);
             updateResidual();

### 2021-05-06 src/screenPredictors.h

@@ -27,7 +27,6 @@ screenPredictors(uvec& lookahead,
                  const uword step,
                  const bool standardize)
 {
-  uvec screened_set = find(screened);
   uword p = X.n_cols;
 
   if (screening_type == "gap_safe") {

### 2021-05-06 sim-test.sh
Drop test script

@@ -1,22 +1,0 @@
-#!/bin/sh
-
-#SBATCH -t 00:15:00
-
-#SBATCH --mail-user=johan.larsson@stat.lu.se
-#SBATCH --mail-type=ALL
-
-#SBATCH -J test
-#SBATCH -o test_%j.out
-#SBATCH -e test_%j.err
-
-#SBATCH -N 1
-#SBATCH --tasks-per-node=20
-
-# modules
-module purge
-
-# bind results folders in Project to host
-export SINGULARITY_BIND="results:/Project/results"
-
-# run the test
-singularity run container.sif test.R

### 2021-05-12 data-raw/arcene.R
Clean out old datasets

@@ -1,29 +1,0 @@
-library(Matrix)
-
-data <- tempfile()
-labels <- tempfile()
-
-download.file(
-  "https://statweb.stanford.edu/~tibs/strong/realdata/arcene_train.data",
-  data
-)
-
-d <- scan(data, sep = " ")
-
-x <- matrix(d, nrow = 100, byrow = TRUE)[, 1:10000]
-x <- Matrix(x, sparse = TRUE)
-
-download.file(
-  "https://statweb.stanford.edu/~tibs/strong/realdata/arcene_train.labels",
-  labels
-)
-
-y <- scan(labels, sep = " ")
-y <- (y + 1) / 2
-
-arcene <- list(X = x, y = y)
-
-saveRDS(arcene, "data/arcene.rds")
-
-unlink(labels)
-unlink(data)

### 2021-05-12 data-raw/dorothea.R

@@ -1,57 +1,0 @@
-library(Matrix)
-
-tmp_data <- tempfile()
-tmp_labels <- tempfile()
-
-download.file(
-  "https://statweb.stanford.edu/~tibs/strong/realdata/dorothea_train.data",
-  tmp_data
-)
-
-download.file(
-  "https://statweb.stanford.edu/~tibs/strong/realdata/dorothea_train.labels",
-  tmp_labels
-)
-
-d <- readLines(tmp_data, n = 800)
-
-makevec <- function(d) {
-  j <- 1
-  j0 <- 1
-  nn <- nchar(d)
-  xx <- NULL
-  while (j < nn) {
-    while (substring(d, j, j) != " ") {
-      j <- j + 1
-    }
-    xx <- c(xx, as.numeric(substring(d, j0, j - 1)))
-    j0 <- j + 1
-    j <- j + 1
-  }
-  xx
-}
-
-y <- makevec(d[1])
-
-x <- matrix(0,
-  nrow = 800,
-  ncol = 100000,
-  byrow = TRUE
-)
-
-for (i in 1:800) {
-  o <- makevec(d[i])
-  x[i, o] <- 1
-}
-
-oo <- colSums(x)
-x <- x[, oo > 0]
-
-dy <- scan(tmp_labels, sep = " ")
-y <- (dy + 1) / 2
-
-X <- Matrix::Matrix(x)
-
-dorothea <- list(X = X, y = y)
-
-saveRDS(dorothea, "data/dorothea.rds")

### 2021-05-12 data-raw/leukemia.R

@@ -1,0 +1,60 @@
+readLIBSVM <- function(file) {
+  dat <- data.table::fread(file,
+    sep = "\n",
+    header = FALSE,
+    showProgress = FALSE
+  )[[1]]
+
+  l <- stringi::stri_split_regex(dat, "[ ]+")
+
+  y <- as.numeric(vapply(l, "[", 1, FUN.VALUE = character(1)))
+
+  vals <- do.call(rbind, lapply(l, function(x) {
+    do.call(rbind, stringi::stri_split_fixed(x[-1], ":"))
+  }))
+
+  row_ind <- rep(seq_len(length(l)), times = lengths(l) - 1)
+  col_ind <- as.integer(vals[, 1])
+
+  X <- Matrix::sparseMatrix(row_ind, col_ind, x = as.numeric(vals[, 2]))
+
+  density <- Matrix::nnzero(X) / length(X)
+
+  if (density > 0.5) {
+    X <- as.matrix(X)
+  }
+
+  if (length(unique(y)) == 2) {
+    y <- as.numeric(as.factor(y)) - 1
+  }
+
+  list(X = X, y = y)
+}
+
+datafiles <- c(
+  "leukemia-train" = "https://www.csie.ntu.edu.tw/~cjlin/libsvmtools/datasets/binary/leu.bz2"
+)
+
+datanames <- names(datafiles)
+
+for (i in seq_along(datanames)) {
+  cat(i, "/", length(datanames), ": ", datanames[i], "..", sep = "")
+
+  file <- file.path("data", paste0(datanames[i], ".rds"))
+
+  if (file.exists(file)) {
+    cat(" already downloaded, skipping!\n")
+  } else {
+    cat(" downloading and parsing .. ")
+    d <- readLIBSVM(datafiles[i])
+    cat(" done!\n")
+
+    density <- Matrix::nnzero(d$X) / length(d$X)
+
+    if (density > 0.25) {
+      d$X <- as.matrix(d$X)
+    }
+
+    saveRDS(d, file)
+  }
+}

### 2021-05-12 data-raw/libsvm-data.R

@@ -1,106 +1,0 @@
-readLIBSVM <- function(file) {
-  dat <- data.table::fread(file,
-    sep = "\n",
-    header = FALSE,
-    showProgress = FALSE
-  )[[1]]
-
-  l <- stringi::stri_split_regex(dat, "[ ]+")
-
-  y <- as.numeric(vapply(l, "[", 1, FUN.VALUE = character(1)))
-
-  vals <- do.call(rbind, lapply(l, function(x) {
-    do.call(rbind, stringi::stri_split_fixed(x[-1], ":"))
-  }))
-
-  row_ind <- rep(seq_len(length(l)), times = lengths(l) - 1)
-  col_ind <- as.integer(vals[, 1])
-
-  X <- Matrix::sparseMatrix(row_ind, col_ind, x = as.numeric(vals[, 2]))
-
-  density <- Matrix::nnzero(X) / length(X)
-
-  if (density > 0.5) {
-    X <- as.matrix(X)
-  }
-
-  if (length(unique(y)) == 2) {
-    y <- as.numeric(as.factor(y)) - 1
-  }
-
-  list(X = X, y = y)
-}
-
-# getLibsvmData <- function(url) {
-#   is_bz2 <- grepl(".bz2$", url)
-
-#   tmp_file <- tempfile(fileext = if (is_bz2) ".bz2" else "")
-
-#   download.file(url, tmp_file, quiet = TRUE)
-
-#   readLIBSVM(tmp_file)
-# }
-
-datafiles <- c(
-  "abalone" = "https://www.csie.ntu.edu.tw/~cjlin/libsvmtools/datasets/regression/abalone",
-  "cadata" = "https://www.csie.ntu.edu.tw/~cjlin/libsvmtools/datasets/regression/cadata",
-  "colon-cancer" = "https://www.csie.ntu.edu.tw/~cjlin/libsvmtools/datasets/binary/colon-cancer.bz2",
-  "covtype" = "https://www.csie.ntu.edu.tw/~cjlin/libsvmtools/datasets/binary/covtype.libsvm.binary.bz2",
-  "diabetes" = "https://www.csie.ntu.edu.tw/~cjlin/libsvmtools/datasets/binary/diabetes",
-  "duke-breast-cancer" = "https://www.csie.ntu.edu.tw/~cjlin/libsvmtools/datasets/binary/duke.bz2",
[…]

### 2021-05-12 README.Rmd
Add instructions for reproducibility to readme

--- 2021-03-31 README.Rmd
@@
 
-# Code for Look-Ahead Screening Rules Paper
+# Code for the Hessian Screening Rule
 
@@
 <!-- badges: end -->
+
+## Results
+
+The results from the simulations, which were run
+on a dedicated HPC cluster, are stored in the [results folder](results/).
+The figures
+in the paper, generated from these results, are stored
+in [`figures/`](figures/).
+
+## Reproducing the Results
+
+The results from our paper were run through a singularity container. Check
+the releases for pre-built singularity containers that you can download and use.
+
+To reproduce the results, **always** use the
+singularity container. To run an experiment from the
+singularity container, call
+
+```shell
+singularity run --bind results:/Project/results container.sif <script>
+```
+
+where `<script>` should be a name of a script in the
+[experiments folder](experiments/), such as `experiments/simulateddata.R`.
+
+### Re-building the Singularity Container
+
+If you want to re-build the singularity container from scratch (or
+simply want to clone the repo to your local drive), you can
+do so via the following steps.
+
+1. Clone the repository to your local hard drive. On linux, using
+   SSH authentication, run
+
+   ```shell
+   git clone git@github.com:jolars/LookAheadScreening.git
+   ```
+
+2. Navigate to the root of the repo and
+   build the singularity container by calling
+
+   ```shell
+   cd LookAheadScreening
+   sudo singularity build container.sif Singularity
+   ```
+
+Then proceed as in [Reproducing the Results](#reproducing-the-results)
+to run the experiments.
+
+### Running Experiments without Singularity (Not Recommended!)
+
+Alternatively, you may also reproduce the results by cloning this repository
+and starting
+R in the root directory of this folder (which will activate the renv
+repository) and then run
+
+```r
+renv::restore()
+```
+
+to restore the project library. Then build the R package (see below) and run the
+simulations directly by running the scripts in the experiments folder. This
+is **not recommended**, however, since it, unlike the Singularity
+container approach, does not exactly
+reproduce the software environment
+used when these simulations where originally run and may result in
+discrepancies due to differences in for instance operating systems,
+compilers, and BLAS/LAPACK implementations.
+
+## R Package
+
+If you want to build
+and experiment with the package, you can do so by calling
+
+```shell
+ R CMD INSTALL  .
+```
+
+provided you have `cd`ed to the root folder of this repository. First
+ensure, however, that you have enabled the renv project library by calling
+`renv::restore()` (see the section above).
+
+## Data
+
+The datasets used in these simulations are stored in the [data folder](data/).
+Scripts to retrieve these datasets from their original
+sources can be found in [`data-raw/`](data-raw/).

### 2021-05-12 experiments/realdata.R
Don't do real data experiments (for lack of space)

@@ -1,84 +1,0 @@
-
-library(LookAheadScreening)
-library(tidyr)
-library(tibble)
-library(Matrix)
-library(readr)
-
-printf <- function(...) invisible(cat(sprintf(...)))
-
-datasets <- c(
-  # "e2006-tfidf-train",
-  # "e2006-log1p-train",
-  "arcene",
-  "colon-cancer",
-  "duke-breast-cancer"
-  # "gisette-train",
-  # "dorothea"
-)
-
-g <- expand_grid(
-  dataset = datasets,
-  screening_type = c("gap_safe", "gap_safe_lookahead"),
-  n = NA,
-  p = NA,
-  density = NA,
-  time = NA,
-  total_violations = NA,
-  avg_screened = NA,
-  violations = list(NA),
-  screened = list(NA),
-  active = list(NA)
-)
-
-for (i in seq_len(nrow(g))) {
-  d <- readRDS(file.path("data", paste0(g$dataset[i], ".rds")))
-  screening_type <- g$screening_type[i]
-
-  X <- d$X
-  y <- d$y
-
-  n <- nrow(X)
-  p <- ncol(X)
-
-  dens <- ifelse(inherits(X, "sparseMatrix"), Matrix::nnzero(X) / length(X), 1)
-  sparsity <- 1 - dens
-
-  printf("%02d/%i %-10.10s %s\n", i, nrow(g), g$dataset[i], screening_type)
-
-  n_it <- 100
-
-  time <- double(n_it)
-
-  for (k in seq_len(n_it)) {
-    fit <- lassoPath(
-      X,
-      y,
-      screening_type = screening_type,
-      verbosity = 0
-    )
-
-    time[k] <- fit$full_time
-
-    # stop if standard error is within 2.5% of mean
-    if (k > 3) {
-      time_se <- sd(time[1:k]) / sqrt(k)
-
-      if (time_se / mean(time[1:k]) < 0.025) {
-        break
-      }
-    }
-  }
-
-  g$n[i] <- n
-  g$p[i] <- p
-  g$time[i] <- mean(time[1:k])
-  g$density[i] <- dens
-  g$avg_screened[i] <- mean(fit$active / fit$screened)
-  g$screened[i] <- list(fit$screened)
-  g$active[i] <- list(fit$active)
-}
-
-cat("DONE!\n")
-
-write_rds(g, "results/realdata.rds")

### 2021-05-12 figures/real.R

@@ -1,66 +1,0 @@
-library(ggplot2)
-library(dplyr)
-library(tidyr)
-library(lemon)
-library(tikzDevice)
-library(knitr)
-
-source("R/utils.R")
-
-theme_set(theme_minimal(base_size = 9))
-
-d <- readRDS("results/efficiency-realdata.rds")
-
-# https://stackoverflow.com/questions/54438495/shift-legend-into-empty-facets-of-a-faceted-plot-in-ggplot2
-shift_legend2 <- function(p) {
-  gp <- ggplotGrob(p)
-  facet.panels <- grep("^panel", gp[["layout"]][["name"]])
-  empty.facet.panels <- sapply(
-    facet.panels, function(i) "zeroGrob" %in% class(gp[["grobs"]][[i]])
-  )
-  empty.facet.panels <- facet.panels[empty.facet.panels]
-  empty.facet.panels <- gp[["layout"]][empty.facet.panels, ]
-  names <- empty.facet.panels$name
-  reposition_legend(p, "center", panel = names)
-}
-
-d2 <-
-  d %>%
-  mutate(screening_type = recode(screening_type,
-    "edpp" = "EDPP",
-    "gap_safe" = "Gap Safe",
-    "hessian" = "Hessian",
-    "strong" = "Strong"
-  )) %>%
-  drop_na() %>%
-  unnest(c(screened, active)) %>%
-  group_by(dataset, screening_type) %>%
-  mutate(screened = screened / p, active = active / p) %>%
-  mutate(step = seq_along(screened))
-
-cols <- c(
-  "#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442",
-  "#0072B2", "#D55E00", "#CC79A7"
-)
-
-pl <- ggplot(d2, aes(step)) +
-  facet_wrap(~dataset, nrow = 2) +
-  geom_line(aes(y = active), linetype = 2) +
-  geom_line(aes(y = screened, col = screening_type)) +
-  scale_y_continuous(
-    oob = function(x, ...) {
-      x
-    },
-    limits = c(0, 0.06)
-  ) +
-  theme(legend.title = element_blank()) +
-  scale_color_manual(values = cols) +
-  labs(x = "Step", y = "Active Predictors")
-
-file <- "figures/realdata-efficiency.tex"
-
-tikz(file, width = 5.6, height = 2.5, standAlone = TRUE)
-shift_legend2(pl)
-dev.off()
-
-renderPdf(file)

### 2021-05-12 sim-real.sh

@@ -1,19 +1,0 @@
-#!/bin/sh
-
-#SBATCH -t 8:00:00
-
-#SBATCH --mail-user=johan.larsson@stat.lu.se
-#SBATCH --mail-type=ALL
-
-#SBATCH -J realdata
-#SBATCH -o realdata_%j.out
-#SBATCH -e realdata_%j.err
-
-#SBATCH -N 1
-#SBATCH --tasks-per-node=20
-
-# modules
-module purge
-
-singularity run --bind results:/Project/results container.sif \
-  experiments/realdata.R

### 2021-05-12 tables/realdata.R

@@ -1,42 +1,0 @@
-library(tibble)
-library(dplyr)
-library(tidyr)
-library(readr)
-library(forcats)
-library(stringr)
-
-d_raw <- readRDS("results/realdata.rds")
-
-d <-
-  d_raw %>%
-  drop_na(time) %>%
-  mutate(
-    screening_type = recode(
-      screening_type,
-      "working" = "Working",
-      "hessian" = "Hessian",
-      "gap_safe" = "GapSafe",
-      "edpp" = "EDPP"
-    ),
-    family = recode(
-      family,
-      "gaussian" = "Gaussian",
-      "binomial" = "Binomial"
-    ),
-    dataset = str_remove(dataset, "(-train|-test)"),
-    dataset = recode(
-      dataset,
-      "YearPredictionMSD" = "YearPredMSD"
-    )
-  ) %>%
-  select(dataset, family, n, p, density, screening = screening_type, time) %>%
-  arrange(family, dataset, screening) %>%
-  pivot_wider(names_from = "screening", values_from = "time")
-
-filter(d, family == "Gaussian") %>%
-  select(-family) %>%
-  write_csv("tables/realdata-timings-gaussian.csv")
-
-filter(d, family == "Binomial") %>%
-  select(-family) %>%
-  write_csv("tables/realdata-timings-binomial.csv")

### 2021-05-12 figures/tfidf.R
Drop unused script

@@ -1,102 +1,0 @@
-
-library(ggplot2)
-library(dplyr)
-library(tidyr)
-library(tikzDevice)
-
-source("R/utils.R")
-
-d <- readRDS("results/simulateddata.rds")
-
-theme_set(theme_minimal(base_size = 9))
-
-cols <- c(
-  "#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442",
-  "#0072B2", "#D55E00", "#CC79A7"
-)
-
-options(
-  tikzDocumentDeclaration =
-    "\\documentclass[10pt]{article}\n\\usepackage{newtxtext,newtxmath}\n"
-)
-
-d2 <-
-  d %>%
-  mutate(
-    np = paste0("$n=", n, "$, $p=", p, "$"),
-    screening_type = recode(
-      screening_type,
-      "hessian" = "Hessian",
-      "working" = "Working",
-      "gap_safe" = "Gap Safe",
-      "edpp" = "EDPP",
-      "strong" = "Strong"
-    )
-  ) %>%
-  filter(screening_type != "Working") %>%
-  drop_na() %>%
-  unnest(c(screened, active, step)) %>%
-  group_by(family, rho, scenario, screening_type) %>%
-  mutate(screened = screened / p, active = active / p)
-
-rho_labeller <- function(labels, multi_line = TRUE, sep = ":", ...) {
-  value <- label_value(labels, multi_line = multi_line)
-
-  out <- paste0("$\\rho = ", value, "$")
-  #  list(unname(unlist(out)))
-  out
-}
-
-d2_gaussian <- filter(d2, family == "gaussian")
-d2_gaussian_active <-
-  d2_gaussian %>%
-  ungroup() %>%
-  group_by(family, rho, np, step) %>%
-  summarize(avg_active = mean(active, na.rm = TRUE))
-
-f1 <- "figures/simulateddata-efficiency-gaussian.tex"
-tikz(f1, width = 5.6, height = 2.5, standAlone = TRUE)
-ggplot(d2_gaussian, aes(step)) +
-  facet_grid(np ~ rho,
-    labeller = labeller(
-      np = label_value,
-      rho = rho_labeller
-    )
-  ) +
-  geom_line(aes(x = step, y = avg_active),
-    linetype = 2,
-    data = d2_gaussian_active
-  ) +
-  geom_line(aes(y = screened, col = screening_type, group = screening_type)) +
-  theme(legend.title = element_blank()) +
[…]

### 2021-05-12 sim-casestudy.sh
Update slurm scripts with project code

@@ -1,3 +1,4 @@
+
 #!/bin/sh
 
 #SBATCH -t 8:00:00
@@ -6,9 +7,9 @@
 #SBATCH --mail-type=ALL
 #SBATCH -A lu2021-2-77
 
-#SBATCH -J simulateddata
-#SBATCH -o simulateddata_%j.out
-#SBATCH -e simulateddata_%j.err
+#SBATCH -J casestudy
+#SBATCH -o casestudy_%j.out
+#SBATCH -e casestudy_%j.err
 
 #SBATCH -N 1
 #SBATCH --tasks-per-node=20
@@ -17,4 +18,4 @@
 module purge
 
 singularity run --bind results:/Project/results container.sif \
-  experiments/simulateddata.R
+  experiments/casestudy.R

### 2021-05-12 experiments/casestudy.R
Add case study experiment

@@ -1,0 +1,55 @@
+
+library(LookAheadScreening)
+library(tidyr)
+library(tibble)
+library(dplyr)
+library(readr)
+
+d <- read_rds("data/leukemia-train.rds")
+
+X <- d$X
+y <- d$y
+
+n <- nrow(X)
+p <- ncol(X)
+
+fit <- lassoPath(
+  X,
+  y,
+  screening_type = "gap_safe_lookahead",
+  verbosity = 0
+)
+
+lookahead <- fit$lookahead
+
+d <- matrix(0, p, ncol(fit$lookahead))
+
+for (j in 1:p) {
+  d[j, 1:(lookahead[j, 1] + 1)] <- TRUE
+}
+
+colnames(d) <- 1:ncol(d)
+
+d1 <- tibble(
+  step = seq_len(ncol(lookahead)),
+  screened = colSums(d) / p
+)
+
+write_rds(d1, "results/casestudy-summary.rds")
+
+q <- 20
+
+set.seed(852)
+
+d2 <-
+  as.data.frame(d) %>%
+  as_tibble() %>%
+  sample_n(q) %>%
+  rowid_to_column() %>%
+  pivot_longer(-rowid) %>%
+  mutate(
+    name = as.integer(name),
+    value = factor(value, labels = c("Included", "Discarded"))
+  )
+
+write_rds(d2, "results/casestudy-full.rds")

### 2021-05-12 experiments/sandbox.R
Tidy up sandbox experiment

@@ -1,20 +1,22 @@
+
 library(LookAheadScreening)
 
-# d <- readRDS(file.path("data", paste0("e2006-tfidf-test", ".rds")))
-d <- generateDesign(100, 50000, s = 5, density = 1)
+# d <- readRDS(file.path("data", paste0("leukemia-train", ".rds")))
+d <- generateDesign(100, 10, s = 1, density = 1)
 X <- d$X
 y <- d$y
 n <- nrow(X)
 p <- ncol(X)
 tol_gap <- 1e-5
 tol_infeas <- 1e-4
+verbosity <- 0
 
 fit <- lassoPath(
     X,
     y,
     screening_type = "gap_safe",
     standardize = TRUE,
-    verbosity = 0,
+    verbosity = 1,
     tol_gap = tol_gap,
     tol_infeas = tol_infeas,
     path_length = 100
@@ -24,13 +26,28 @@ fit_lookahead <- lassoPath(
     X,
     y,
     screening_type = "gap_safe_lookahead",
-    force_kkt_check = FALSE,
     standardize = TRUE,
-    verbosity = 0,
+    verbosity = 1,
     tol_gap = tol_gap,
     tol_infeas = tol_infeas,
     path_length = 100
 )
+
+library(tibble)
+library(ggplot2)
+
+d <- tibble(
+    time = c(fit_lookahead$cd_time, fit$cd_time),
+    passes = c(fit_lookahead$passes, fit$passes),
+    screened = c(fit_lookahead$screened, fit$screened),
+    step = c(seq_along(fit_lookahead$cd_time), seq_along(fit$cd_time)),
+    type = rep(c("lookahead", "standard"),
+        times = c(length(fit_lookahead$cd_time), length(fit$cd_time))
+    )
+)
+
+ggplot(d, aes(step, screened, col = type)) +
+    geom_line()
 
 fit$full_time
 fit_lookahead$full_time
@@ -40,6 +57,5 @@ fit_lookahead$violations
 fit$violations
 
 any(fit_lookahead$violations > 0)
-
 
 fit_lookahead$lookahead[1:30, 1:39]

### 2021-05-12 figures/casestudy.R
Add figure script for case study

@@ -1,0 +1,28 @@
+
+library(readr)
+library(ggplot2)
+library(tikzDevice)
+
+source("R/utils.R")
+
+theme_set(theme_minimal(base_size = 9))
+
+d <- read_rds("results/casestudy-full.rds")
+
+pl <-
+  ggplot(d2, aes(name, rowid, fill = value)) +
+  geom_tile(show.legend = FALSE, col = "white") +
+  scale_fill_manual(values = c("grey", "steelblue4")) +
+  coord_fixed() +
+  scale_y_continuous(breaks = c(1, 5, 10, 15, 20, 25)) +
+  scale_x_continuous(breaks = c(1, 10, 20, 30, 40, 50, 60, 70, 80, 90), expand = expansion(add = 1)) +
+  labs(x = "Step", y = "Predictor")
+
+file <- "paper/figures/casestudy.tex"
+
+tikz(file, width = 4.7, height = 4, standAlone = TRUE)
+pl
+dev.off()
+renderPdf(file)
+
+d2 <- read_rds("results/casestudy-summary.rds")

### 2021-05-12 figures/simulated.R
Fix figure script for simulated data study

@@ -4,74 +4,39 @@ library(dplyr)
 library(forcats)
 library(tikzDevice)
 library(ggplot2)
+library(readr)
 
 source("R/utils.R")
 
 theme_set(theme_minimal(base_size = 9))
 
-fw <- 5.6
-
-d_raw <- readRDS("results/simulateddata.rds") %>%
-  filter(screening_type != "strong", scenario != 2) %>%
+d1 <- read_rds("results/simulateddata.rds") %>%
+  select(-(screened:step)) %>%
+  unnest(time) %>%
   mutate(
     screening_type = recode(
       screening_type,
-      "hessian" = "Hessian",
-      "working" = "Working",
-      "gap_safe" = "Gap Safe",
-      "edpp" = "EDPP"
+      "gap_safe" = "Standard",
+      "gap_safe_lookahead" = "Look-Ahead"
     ),
-    rho = as.factor(rho),
-    np = paste0("$n=", n, "$, $p=", p, "$"),
-    np = reorder(np, p),
-  ) %>%
-  select(np, n, p, rho, family, screening_type, time) %>%
-  unnest(time)
-
-d1 <-
-  d_raw %>%
-  mutate(
-    screening_type = as.factor(screening_type),
-    family = as.factor(family)
-  ) %>%
-  group_by(np, rho, family, screening_type) %>%
-  summarize(
-    meantime = mean(time),
-    se = sd(time / n())
-  ) %>%
-  mutate(
-    hi = meantime + se,
-    lo = meantime - se,
-    rel_time = meantime / min(meantime)
-  ) %>%
-  drop_na(meantime)
+    snr = as.factor(snr)
+  )
 
 cols <- c(
   "#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442",
   "#0072B2", "#D55E00", "#CC79A7"
 )
 
-options(
-  tikzDocumentDeclaration =
-    "\\documentclass[10pt]{article}\n\\usepackage{newtxtext,newtxmath}\n"
-)
-
-file <- "figures/simulateddata-timings.tex"
-tikz(file, width = fw, height = 2.5, standAlone = TRUE)
+file <- "paper/figures/simulateddata-timings.tex"
+tikz(file, width = 4.5, height = 2, standAlone = TRUE)
 ggplot(d1, aes(
-  rho,
-  rel_time,
+  snr,
+  time,
   fill = screening_type
 )) +
[…]

### 2021-05-12 R/RcppExports.R
Change name of argument to kkt_check

@@ -1,11 +1,11 @@
 # Generated by using Rcpp::compileAttributes() -> do not edit by hand
 # Generator token: 10BE3573-1514-4C36-9D1C-5A225CD40393
 
-lassoPathDense <- function(X, y, standardize, screening_type, path_length, maxit, tol_infeas, tol_gap, force_kkt_check, verbosity) {
-    .Call(`_LookAheadScreening_lassoPathDense`, X, y, standardize, screening_type, path_length, maxit, tol_infeas, tol_gap, force_kkt_check, verbosity)
+lassoPathDense <- function(X, y, standardize, screening_type, path_length, maxit, tol_infeas, tol_gap, check_kkt, verbosity) {
+    .Call(`_LookAheadScreening_lassoPathDense`, X, y, standardize, screening_type, path_length, maxit, tol_infeas, tol_gap, check_kkt, verbosity)
 }
 
-lassoPathSparse <- function(X, y, standardize, screening_type, path_length, maxit, tol_infeas, tol_gap, force_kkt_check, verbosity) {
-    .Call(`_LookAheadScreening_lassoPathSparse`, X, y, standardize, screening_type, path_length, maxit, tol_infeas, tol_gap, force_kkt_check, verbosity)
+lassoPathSparse <- function(X, y, standardize, screening_type, path_length, maxit, tol_infeas, tol_gap, check_kkt, verbosity) {
+    .Call(`_LookAheadScreening_lassoPathSparse`, X, y, standardize, screening_type, path_length, maxit, tol_infeas, tol_gap, check_kkt, verbosity)
 }
 

### 2021-05-12 R/lassoPath.R

@@ -8,8 +8,7 @@
 #' @param maxit Maximum number of iterations for Coordinate Descent loop
 #' @param tol_infeas Tolerance threshold for maximum infeasibility
 #' @param tol_gap Tolerance threshold for duality gap
-#' @param force_kkt_check Whether to force KKT checks even when screening rule
-#'   is safe
+#' @param check_kkt Whether to force KKT checks
 #' @param verbosity Controls the level of verbosity. 0 = no output.
 #'
 #' @export
@@ -24,9 +23,8 @@ lassoPath <- function(X,
                       maxit = 1e5,
                       tol_infeas = 1e-4,
                       tol_gap = 1e-5,
-                      force_kkt_check = FALSE,
+                      check_kkt = FALSE,
                       verbosity = 0) {
-
   screening_type <- match.arg(screening_type)
 
   sparse <- inherits(X, "sparseMatrix")
@@ -46,7 +44,7 @@ lassoPath <- function(X,
       maxit,
       tol_infeas,
       tol_gap,
-      force_kkt_check,
+      check_kkt,
       verbosity
     )
   } else {
@@ -59,7 +57,7 @@ lassoPath <- function(X,
       maxit,
       tol_infeas,
       tol_gap,
-      force_kkt_check,
+      check_kkt,
       verbosity
     )
   }

### 2021-05-12 src/lassoPath.cpp

@@ -316,7 +316,7 @@ lassoPathDense(arma::mat X,
                const arma::uword maxit,
                const double tol_infeas,
                const double tol_gap,
-               const bool force_kkt_check,
+               const bool check_kkt,
                const arma::uword verbosity)
 {
   return lassoPath(X,
@@ -327,7 +327,7 @@ lassoPathDense(arma::mat X,
                    maxit,
                    tol_infeas,
                    tol_gap,
-                   force_kkt_check,
+                   check_kkt,
                    verbosity);
 }
 
@@ -341,7 +341,7 @@ lassoPathSparse(arma::sp_mat X,
                 const arma::uword maxit,
                 const double tol_infeas,
                 const double tol_gap,
-                const bool force_kkt_check,
+                const bool check_kkt,
                 const arma::uword verbosity)
 {
   return lassoPath(X,
@@ -352,6 +352,6 @@ lassoPathSparse(arma::sp_mat X,
                    maxit,
                    tol_infeas,
                    tol_gap,
-                   force_kkt_check,
+                   check_kkt,
                    verbosity);
 }

### 2021-05-12 src/screenPredictors.h

@@ -42,7 +42,8 @@ screenPredictors(uvec& lookahead,
     double residual_sq_norm2 = std::pow(norm(residual), 2);
 
     for (uword j = 0; j < p; ++j) {
-      if (ever_active(j) || step < lookahead(j) || screened(j))
+      if (ever_active(j) || step < lookahead(j) || lookahead_disabled(j) ||
+          screened(j))
         continue;
 
       double a = std::pow(1 - std::abs(corr(j) / dual_scale), 2) -

### 2021-05-12 paper/main.tex
Update paper after feedback

@@
 \renewcommand{\shortauthor}{J. Larsson}
-\renewcommand{\shorttitle}{Look-Ahead Screening Rules for the Lasso}
+%\renewcommand{\shorttitle}{Look-Ahead Screening Rules for the Lasso}
 
@@
 \begin{abstract}
-  The lasso is a popular method for inducing shrinkage and sparsity in the
-  solution vector (coefficients) of regression problems, particularly when
-  the number of predictors far outnumber the number of observations. Solving
-  the lasso for high-dimensional data can, however, be computationally
-  demanding. Fortunately, this computational load can be alleviated via the
-  use of \emph{screening rules}, which screen and discard predictors prior to
-  fitting the model, leading a reduced problem to be solved. Screening rules
-  are particularly effective when fitting a full regularization path: a
-  sequence of models with decreasing penalization. Screening rules can be
-  safe or heuristic. Safe rules certify that discarded predictors are not in
-  the solution; heuristic ones do not. Existing screening rules typically
-  work sequentially or dynamically. Sequential rules screen predictors for
-  the next model along the regularization path, whereas dynamical rules
-  screen during optimization of the current model. There has, however,
-  previously been no attempts to design screening rules that screen further
-  along the path.
-
-  In this paper, we present a new screening strategy: \emph{look-ahead}
-  screening rules. Our method uses safe screening rules to find a range of
-  penalty values for which a given predictor cannot enter the model, thereby
-  screening predictors along the remainder of the path. Our screening rules
-  lead to reductions in the time required for screening and also applies to
-  heuristic rules, for which the time required to conduct checks of the
-  optimality conditions to guard against violations of the rules is reduced.
+  The lasso is a popular method to induce shrinkage and sparsity in the
+  solution vector (coefficients) of regression problems, particularly
+  when there are many predictors relative to the number of observations. Solving
+  the lasso in this high-dimensional setting can, however, be computationally
+  demanding. Fortunately, this demand can be alleviated via the
+  use of \emph{screening rules} that discard predictors prior to
+  fitting the model, leading to a reduced problem to be solved.
+  In this paper, we present a new screening strategy: \emph{look-ahead
+    screening}. Our method uses safe screening rules to find a range of
+  penalty values for which a given predictor cannot enter the model,
+  thereby screening predictors along the remainder of the path.
   In experiments we show that these look-ahead screening rules improve the
-  performance of existing screening strategies and that the additional cost
-  of screening ahead on the path is marginal.
+  performance of existing screening strategies.
 \end{abstract}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \section{Introduction}
 
-\section{Preliminaries}%
-\label{sec:preliminaries}
+The lasso~\cite{tibshirani1996} is a staple among regression models for
+high-dimensional data. It induces shrinkage and sparsity in the solution
+vector (regression coefficients) through penalization by the
+\(\ell_1\)-norm. The optimal level of penalization is, however, usually
+unknown, which means we typically need to estimate it through model tuning
+across a grid of candidate values: the regularization path. This leads to a
+heavy computational load.
 
-Starting with the preliminaries of our problem, we take \(X \in \mathbb{R}^{n
-  \times p}\) be the design matrix of \(n\) observations and \(p\) predictors
+Thankfully, the advent of so-called \emph{screening rules} have lead to
+remarkable advances in tackling this problem. Screening rules discard a
+subset of the predictors \emph{before} fitting the model, leading to, often
+considerable, reductions in problem size. There are two types of screening
+rules: heuristic and safe rules.
+The latter kind provides a certificate that discarded predictors cannot be
+active at the optimum---that is, have a non-zero corresponding
+coefficients---whereas heuristic rules do not. In this paper, we will
+focus entirely on safe rules.
+
+A prominent type of safe rules are the Gap Safe
+rules~\citep{ndiaye2017,fercoq2015}, which use the duality gap in a problem
+to provide effective screening rules. There currently exists
+sequential versions of
+the Gap Safe rules, that discard predictors for the next step on the
+regularization path, as well as dynamic rules, which discard predictors
+during optimization at the current penalization value.
+
+The objective of this paper is to introduce a new screening strategy based
+on Gap Safe screening: \emph{look-ahead screening}, which
+screens predictors for a range of penalization parameters. We
+show that this method can be used to screen predictors for the entire
+stretch of the regularization path, leading to substantial improvements in
+the time to fit the entire lasso path.
+
+\section{Look-Ahead Screening}%
+\label{sec:look-ahead-screening}
+
+Let \(X \in \mathbb{R}^{n \times p}\) be the design matrix with \(n\)
+observations and \(p\) predictors
 and \(y \in \mathbb{R}^n\) the response vector.
-
 The lasso is represented by the following convex optimization problem:
@@
   \operatorname*{minimize}_{\beta \in \mathbb{R}^p} P(\beta; \lambda)
+  = \frac 1 2 \lVert y - X\beta \rVert_2^2 + \lambda \lVert \beta \rVert_1
 \end{equation}
-where
-\begin{equation}
-  P(\beta; \lambda) =
-  \frac 1 2 \lVert y - X\beta \rVert_2^2 + \lambda \lVert \beta \rVert_1
-\end{equation}
+where \(P(\beta;\lambda)\)
 is the \emph{primal} objective. We let \(\hat \beta_\lambda\) be the solution to
-\eqref{eq:primal} for a given \(\lambda\). In addition, we also let \(\tilde
-\beta_\lambda\) be a numerical approximation to \(\hat\beta_\lambda\)
-returned by an algorithm
-tasked with solving \eqref{eq:primal}.
+\eqref{eq:primal} for a given \(\lambda\) and \(\tilde
+\beta_\lambda\) an estimate of \(\hat\beta_\lambda\).\footnote{Such as
+  the current estimate in an iterative solver tasked with solving
+  \eqref{eq:primal}.}
 
-The Karush--Kuhn--Tucker (KKT) stationarity condition for \eqref{eq:primal}
-holds that
-\begin{equation}
-  \label{eq:stationarity}
-  0 \in X^T(X\beta - y) + \lambda\partial,
-\end{equation}
-where \(\partial\) is the subdifferential of the \(\ell_1\)-norm, with
-its \(j\)th element corresponding to
-\begin{equation}
-  \label{eq:subdifferential}
-  \partial_j \in
-  \begin{cases}
-    \{\sign(\beta_j)\} & \text{if } \beta_j \neq 0 \\
-    [-1,1]             & \text{otherwise.}
-  \end{cases}
-\end{equation}
-Moreover, we define the dual problem of \eqref{eq:primal} as
+% The Karush--Kuhn--Tucker (KKT) stationarity condition for \eqref{eq:primal}
+% holds that
+% \begin{equation}
+%   \label{eq:stationarity}
+%   0 \in X^T(X\beta - y) + \lambda\partial,
+% \end{equation}
+% where \(\partial\) is the subdifferential of the \(\ell_1\)-norm, with
+% its \(j\)th element corresponding to
+% \begin{equation}
+%   \label{eq:subdifferential}
+%   \partial_j \in
+%   \begin{cases}
+%     \{\sign(\beta_j)\} & \text{if } \beta_j \neq 0 \\
+%     [-1,1]             & \text{otherwise.}
+%   \end{cases}
+% \end{equation}
+Moreover, the dual problem of \eqref{eq:primal} is
 \begin{equation}
   \label{eq:dual}
-  \operatorname*{maximize}_{\theta \in \mathbb{R}^n} D(\theta; \lambda)
-\end{equation}
-where
-\begin{equation}
-  D(\theta) = \frac 12 y^T y - \frac{\lambda^2}{2} \left\lVert \theta
+  \operatorname*{maximize}_{\theta \in \mathbb{R}^n} D(\theta; \lambda) =
+  \frac 12 y^T y - \frac{\lambda^2}{2} \left\lVert \theta
   - \frac y \lambda \right\rVert_2^2
 \end{equation}
-is the \emph{dual} objective.
+where \(D(\theta; \lambda)\) is the \emph{dual} objective.
 The relationship between the primal and dual problems is given by
-\[
-  y = X\hat\beta_\lambda + \lambda \hat\theta_\lambda.
-\]
-Next, we let \(G\) be the so-called \emph{duality gap}, which we define
-as
+\(y = X\hat\beta_\lambda + \lambda \hat\theta_\lambda.\)
+
+Next, we let \(G\) be the so-called \emph{duality gap}, defined as
 \begin{equation}
-  \begin{aligned}
   G(\beta, \theta; \lambda)
-     & = P(\beta; \lambda) - D(\theta; \lambda)                                                 \\
-     & = \frac 12 \lVert y - X\beta\rVert_2^2 + \lambda \lVert \beta \rVert_1
-    - \frac 12 y^T y + \frac{\lambda^2}{2} \left\lVert \theta - \frac y \theta \right\rVert_2^2 \\
-     & =
+  = P(\beta; \lambda) - D(\theta; \lambda)
+  =
   \frac 12 \lVert y - X\beta\rVert_2^2 + \lambda \lVert \beta \rVert_1
   - \lambda \theta^T y + \frac{\lambda^2}{2} \theta^T \theta.
-  \end{aligned}
 \end{equation}
@@
 Suppose, now, that we have solved the lasso for \(\lambda\); then
-for any given \(\lambda^* \geq \lambda\),
-the Gap Safe rule~\citep{ndiaye2017} for the lasso discards the \(j\)th
+for any given \(\lambda^* \leq \lambda\);
+the Gap Safe rule~\citep{ndiaye2017} discards the \(j\)th
 predictor if
@@
   \tilde\theta_\lambda = \frac{y - X\tilde\beta_\lambda}{
-    \max\big( \max_j|x_j^T(y - X\tilde\beta_\lambda)|, \lambda\big)}
+    \max\big( |X^T(y - X\tilde\beta_\lambda)|, \lambda\big)}
 \]
-is a dual-feasible point~\cite{ndiaye2017}, which we can always obtain
-by dual scaling whenever a candidate is infeasible. Using these facts,
-we now arrive at \autoref{thm:look-ahead}, which is the main result of
-this paper.
+is a dual-feasible point~\cite{ndiaye2017} obtained through dual scaling.
 
-\begin{theorem}
-  \label{thm:look-ahead}
-  Let
-  \((\tilde\beta_\lambda,\tilde\theta_\lambda)\) be
-  a feasible primal--dual point for the solution to
-  \eqref{eq:primal} and \eqref{eq:dual}. Then
-  \(\big(\hat\beta_{\lambda^*}\big)_j = 0\) for any
+Next, observe that \eqref{eq:gap-safe-rule} is a quadratic inequality with
+respect to \(\lambda_*\), which
+means that it is trivial to discover the boundary points via the
+quadratic formula:
 \[
-    \lambda_* > \frac{-b + \sqrt{b^2 - 4ac}}{2a}
+  \lambda_* = \frac{-b \pm \sqrt{b^2 - 4ac}}{2a}
 \]
@@
 \]
-\end{theorem}
-\begin{proof}
+By restricting ourselves to an index \(j\) corresponding to a predictor that is
+inactive at \(\lambda\) and recalling that we have \(\lambda_* \leq \lambda\) by
+construction, we can inspect the signs of \(a\), \(b\), and \(c\) and find a
+range \(\lambda\) values for which predictor \(j\) must be inactive. Using this
+idea for the lasso path---a grid of \(\lambda\) values starting from the null
+(intercept-only) model, which corresponds to \(\lambda_\text{max} =
+\max_i|x_i^Ty|\), and finishing at fraction of this (see
+\autoref{seq:simulations} for specifics)---we can screen predictor \(j\) for all
+upcoming \(\lambda\)s, possibly discarding it for multiple steps on the path
+rather than just the next step. We call this idea \emph{look-ahead screening}.
 
-\end{proof}
+To illustrate the effectiveness of this screening method,
+we consider an instance of employing look-ahead screening for fitting
+a full lasso path to the \emph{leukemia} dataset~\citep{golub1999}.
+At the first step of
+the path, the screening method discards 99.6\% of the
+predictors for the steps up to and including
+step 5. The respective figures for steps 10 and 15 are 99.3\% and 57\%.
+At step 20, however, the
+rule does the rule not discard a single predictor.
 
-Note that there must be some \(\lambda_*^2\), for which it holds that
-\[
-  |X^T \tilde \theta_\lambda|_j +
-  \lVert x_j\rVert_2 \sqrt{\frac{1}{\lambda_*^2} G(\tilde \beta_\lambda, \tilde \theta_\lambda; \lambda^*)}
-  = 1
-\]
+In \autoref{fig:case-study}, we have visualized the screening performance
+of look-ahead screening for a random sample of 25 predictors from this
+dataset.
 
-\acknowledgements{Your acknowledgements.}
+\begin{figure}[hbtp]
+  \centering
+  \includegraphics{figures/casestudy.pdf}
+  \caption{This figure shows the predictors screened at the first step of the
+    lasso path via look-ahead screening for a random sample of
+    20 predictors from the \emph{leukemia}
+    dataset. A blue square indicates that the corresponding predictor can
+    be discarded at the respective step.\label{fig:case-study}}
+\end{figure}
 
+As is typical for all screening methods,
+the effectiveness of look-ahead screening is strongest at the
+start of the path and diminishes as the strength of
+penalization decreases further up on the
+path. Note, however, that all of the quantities involved in the rule are
+available as a by-product of solving the problem at the previous step, which
+means that the costs of the look-ahead screening method are negligible.
+
+\section{Simulations}\label{seq:simulations}
+
+In this section, we study the effectiveness of the look-ahead screening rules by
+comparing them against the active warm start version of the Gap Safe
+rules~\citep{fercoq2015,ndiaye2017}.  We follow the recommendations in
+\citet{ndiaye2017} and run the screening procedure every tenth pass of the
+solver.
+
+Throughout the experiments, we center the response vector by its mean. In
+addition, we center and scale the predictors by their means and uncorrected
+sample standard deviations respectively.
+
+To construct
+the regularization path, we employ the standard settings from \textsf{glmnet},
+using a log-spaced path of 100 \(\lambda\) values from \(\lambda_\text{max}\)
+to \(\varepsilon \lambda_\text{max}\), where \(\varepsilon = 10^{-2}\) if
+\(p > n\) and \(10^{-4}\) otherwise. We also use the default
+path stopping criteria from \textsf{glmnet}, that is, stop the path whenever
+the deviance ratio, \(1 - \text{dev}/\text{dev}_\text{null}\),
+is greater than or equal to 0.999,
+the fractional increase in deviance explained is lower than
+\(10^{-5}\), or, if \(p \geq n\),
+when the number of active predictors exceeds or is equal to
+\(n\).
+
+To fit the lasso, we
+use cyclical coordinate descent~\cite{friedman2010}.
+We consider the solver to have converged whenever
+the duality gap as a fraction of the primal value
+for the null model is less than or equal to \(10^{-6}\) and the amount of
+\emph{infeasibility}, which we define as \(\max_i\big( |c_i| -
+\lambda\big)\), as a fraction of \(\lambda_\text{max}\) is lower than or
+equal to \(10^{-5}\).
+
+The code used in these experiments is programmed in \textsf{C++}.
+We use a combination of the \textsf{renv} R
+package and Singularity to set up a
+reproducible environment for the experiments. All
+source code
+can be found at \url{https://github.com/jolars/LookAheadScreening/}. An HPC
+cluster node with two Intel Xeon E5-2650 v3 processors (Haswell, 20 compute
+cores per node) and 64 GB of RAM was used to run the experiments.
+
+We
+run experiments on a design with \(n = 100\) and \(p = 50\,000\),
+drawing the rows of \(X\) i.i.d.
+from \(\mathcal{N}(0, \Sigma)\) and \(y\)
+from \(\mathcal{N}(X\beta, \sigma^2I)\) with \(\sigma^2 =
+\beta^T\Sigma\beta/\text{SNR}\), where SNR is the signal-to-noise ratio.  We set
+\(5\) coefficients, equally spaced throughout the coefficient vector, to 1 and
+the rest to zero. Taking inspriation from \citet{hastie2020}, we
+consider SNR values of 0.1, 1, and 6.
+
+Judging by the results~(\autoref{fig:simulated-data}), the addition of
+look-ahead screening results in sizable reductions in the solving time of
+the lasso path, particularly in the high signal-to-noise context.
+
+\begin{figure}[hbtp]
+  \centering
+  \includegraphics{figures/simulateddata-timings.pdf}
+  \caption{Standard box plots of timings to fit a full lasso path to
+    a simulated dataset with \(n = 100\), \(p = 50\,000\), and five true
+    signals.}
+  \label{fig:simulated-data}
+\end{figure}
+
+\section{Discussion}
+
+In this paper, we have presented \emph{look-ahead screening}, which is a
+novel method to screen predictors for a range of penalization values along
+the lasso regularization path using Gap Safe screening. Our results show that
+this type of screening can yield considerable improvements in performance.
+
+The idea is general and can therefore be extended to any type of safe screening
+rule and also used in tandem with heuristic screening rules in order to avoid
+expensive KKT computations.
+
+\acknowledgements{
+  I would like to thank my supervisor, Jonas Wallin, for valuable feedback
+  on this work.
+
+  The computations were enabled by resources provided by the Swedish
+  National Infrastructure for Computing (SNIC) at LUNARC partially funded
+  by the Swedish Research Council through grant agreement no. 2017-05973.
+}
 \bibliography{LookAheadScreening.bib}

### 2021-05-12 paper/figures/casestudy.tex
Update results

% Created by tikzDevice version 0.12.3.1 on 2021-05-11 11:26:34
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

\usepackage[active,tightpage,psfixbb]{preview}

\PreviewEnvironment{pgfpicture}

\setlength\PreviewBorder{0pt}
\begin{document}

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (339.67,289.08);
\begin{scope}
\path[clip] ( 25.95,117.46) rectangle (335.17,192.22);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 25.95,129.36) --
	(335.17,129.36);

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 25.95,144.65) --
	(335.17,144.65);

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 25.95,161.64) --
	(335.17,161.64);

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 25.95,178.63) --
	(335.17,178.63);

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 46.33,117.46) --
	( 46.33,192.22);

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 78.62,117.46) --
	( 78.62,192.22);

\path[draw=drawColor,line width= 0.2pt,line join=round] (112.60,117.46) --
	(112.60,192.22);

\path[draw=drawColor,line width= 0.2pt,line join=round] (146.58,117.46) --
	(146.58,192.22);

\path[draw=drawColor,line width= 0.2pt,line join=round] (180.56,117.46) --
	(180.56,192.22);

\path[draw=drawColor,line width= 0.2pt,line join=round] (214.54,117.46) --
	(214.54,192.22);

\path[draw=drawColor,line width= 0.2pt,line join=round] (248.52,117.46) --
	(248.52,192.22);

\path[draw=drawColor,line width= 0.2pt,line join=round] (282.50,117.46) --
	(282.50,192.22);

\path[draw=drawColor,line width= 0.2pt,line join=round] (316.48,117.46) --
	(316.48,192.22);

\path[draw=drawColor,line width= 0.5pt,line join=round] ( 25.95,122.56) --
	(335.17,122.56);

\path[draw=drawColor,line width= 0.5pt,line join=round] ( 25.95,136.15) --
	(335.17,136.15);

\path[draw=drawColor,line width= 0.5pt,line join=round] ( 25.95,153.14) --
	(335.17,153.14);

\path[draw=drawColor,line width= 0.5pt,line join=round] ( 25.95,170.13) --
	(335.17,170.13);

\path[draw=drawColor,line width= 0.5pt,line join=round] ( 25.95,187.12) --
	(335.17,187.12);

\path[draw=drawColor,line width= 0.5pt,line join=round] ( 31.04,117.46) --
	( 31.04,192.22);

\path[draw=drawColor,line width= 0.5pt,line join=round] ( 61.63,117.46) --
	( 61.63,192.22);

\path[draw=drawColor,line width= 0.5pt,line join=round] ( 95.61,117.46) --
	( 95.61,192.22);

\path[draw=drawColor,line width= 0.5pt,line join=round] (129.59,117.46) --
	(129.59,192.22);

\path[draw=drawColor,line width= 0.5pt,line join=round] (163.57,117.46) --
	(163.57,192.22);

\path[draw=drawColor,line width= 0.5pt,line join=round] (197.55,117.46) --
	(197.55,192.22);

\path[draw=drawColor,line width= 0.5pt,line join=round] (231.53,117.46) --
	(231.53,192.22);

\path[draw=drawColor,line width= 0.5pt,line join=round] (265.51,117.46) --
	(265.51,192.22);

\path[draw=drawColor,line width= 0.5pt,line join=round] (299.49,117.46) --
	(299.49,192.22);

\path[draw=drawColor,line width= 0.5pt,line join=round] (333.47,117.46) --
	(333.47,192.22);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{54,100,139}

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 29.34,120.86) rectangle ( 32.74,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 32.74,120.86) rectangle ( 36.14,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 36.14,120.86) rectangle ( 39.54,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 39.54,120.86) rectangle ( 42.94,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 42.94,120.86) rectangle ( 46.33,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 46.33,120.86) rectangle ( 49.73,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 49.73,120.86) rectangle ( 53.13,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 53.13,120.86) rectangle ( 56.53,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 56.53,120.86) rectangle ( 59.93,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 59.93,120.86) rectangle ( 63.32,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 63.32,120.86) rectangle ( 66.72,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 66.72,120.86) rectangle ( 70.12,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 70.12,120.86) rectangle ( 73.52,124.26);
\definecolor{fillColor}{RGB}{190,190,190}

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 73.52,120.86) rectangle ( 76.92,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 76.92,120.86) rectangle ( 80.32,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 80.32,120.86) rectangle ( 83.71,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 83.71,120.86) rectangle ( 87.11,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 87.11,120.86) rectangle ( 90.51,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 90.51,120.86) rectangle ( 93.91,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 93.91,120.86) rectangle ( 97.31,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 97.31,120.86) rectangle (100.70,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (100.70,120.86) rectangle (104.10,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (104.10,120.86) rectangle (107.50,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (107.50,120.86) rectangle (110.90,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (110.90,120.86) rectangle (114.30,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (114.30,120.86) rectangle (117.69,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (117.69,120.86) rectangle (121.09,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (121.09,120.86) rectangle (124.49,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (124.49,120.86) rectangle (127.89,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (127.89,120.86) rectangle (131.29,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (131.29,120.86) rectangle (134.68,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (134.68,120.86) rectangle (138.08,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (138.08,120.86) rectangle (141.48,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (141.48,120.86) rectangle (144.88,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (144.88,120.86) rectangle (148.28,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (148.28,120.86) rectangle (151.67,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (151.67,120.86) rectangle (155.07,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (155.07,120.86) rectangle (158.47,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (158.47,120.86) rectangle (161.87,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (161.87,120.86) rectangle (165.27,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (165.27,120.86) rectangle (168.66,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (168.66,120.86) rectangle (172.06,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (172.06,120.86) rectangle (175.46,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (175.46,120.86) rectangle (178.86,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (178.86,120.86) rectangle (182.26,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (182.26,120.86) rectangle (185.65,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (185.65,120.86) rectangle (189.05,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (189.05,120.86) rectangle (192.45,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (192.45,120.86) rectangle (195.85,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (195.85,120.86) rectangle (199.25,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (199.25,120.86) rectangle (202.64,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (202.64,120.86) rectangle (206.04,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (206.04,120.86) rectangle (209.44,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (209.44,120.86) rectangle (212.84,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (212.84,120.86) rectangle (216.24,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (216.24,120.86) rectangle (219.64,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (219.64,120.86) rectangle (223.03,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (223.03,120.86) rectangle (226.43,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (226.43,120.86) rectangle (229.83,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (229.83,120.86) rectangle (233.23,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (233.23,120.86) rectangle (236.63,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (236.63,120.86) rectangle (240.02,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (240.02,120.86) rectangle (243.42,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (243.42,120.86) rectangle (246.82,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (246.82,120.86) rectangle (250.22,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (250.22,120.86) rectangle (253.62,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (253.62,120.86) rectangle (257.01,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (257.01,120.86) rectangle (260.41,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (260.41,120.86) rectangle (263.81,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (263.81,120.86) rectangle (267.21,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (267.21,120.86) rectangle (270.61,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (270.61,120.86) rectangle (274.00,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (274.00,120.86) rectangle (277.40,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (277.40,120.86) rectangle (280.80,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (280.80,120.86) rectangle (284.20,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (284.20,120.86) rectangle (287.60,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (287.60,120.86) rectangle (290.99,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (290.99,120.86) rectangle (294.39,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (294.39,120.86) rectangle (297.79,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (297.79,120.86) rectangle (301.19,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (301.19,120.86) rectangle (304.59,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (304.59,120.86) rectangle (307.98,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (307.98,120.86) rectangle (311.38,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (311.38,120.86) rectangle (314.78,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (314.78,120.86) rectangle (318.18,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (318.18,120.86) rectangle (321.58,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (321.58,120.86) rectangle (324.97,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (324.97,120.86) rectangle (328.37,124.26);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (328.37,120.86) rectangle (331.77,124.26);
\definecolor{fillColor}{RGB}{54,100,139}

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 29.34,124.26) rectangle ( 32.74,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 32.74,124.26) rectangle ( 36.14,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 36.14,124.26) rectangle ( 39.54,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 39.54,124.26) rectangle ( 42.94,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 42.94,124.26) rectangle ( 46.33,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 46.33,124.26) rectangle ( 49.73,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 49.73,124.26) rectangle ( 53.13,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 53.13,124.26) rectangle ( 56.53,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 56.53,124.26) rectangle ( 59.93,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 59.93,124.26) rectangle ( 63.32,127.66);
\definecolor{fillColor}{RGB}{190,190,190}

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 63.32,124.26) rectangle ( 66.72,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 66.72,124.26) rectangle ( 70.12,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 70.12,124.26) rectangle ( 73.52,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 73.52,124.26) rectangle ( 76.92,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 76.92,124.26) rectangle ( 80.32,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 80.32,124.26) rectangle ( 83.71,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 83.71,124.26) rectangle ( 87.11,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 87.11,124.26) rectangle ( 90.51,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 90.51,124.26) rectangle ( 93.91,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 93.91,124.26) rectangle ( 97.31,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 97.31,124.26) rectangle (100.70,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (100.70,124.26) rectangle (104.10,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (104.10,124.26) rectangle (107.50,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (107.50,124.26) rectangle (110.90,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (110.90,124.26) rectangle (114.30,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (114.30,124.26) rectangle (117.69,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (117.69,124.26) rectangle (121.09,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (121.09,124.26) rectangle (124.49,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (124.49,124.26) rectangle (127.89,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (127.89,124.26) rectangle (131.29,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (131.29,124.26) rectangle (134.68,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (134.68,124.26) rectangle (138.08,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (138.08,124.26) rectangle (141.48,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (141.48,124.26) rectangle (144.88,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (144.88,124.26) rectangle (148.28,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (148.28,124.26) rectangle (151.67,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (151.67,124.26) rectangle (155.07,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (155.07,124.26) rectangle (158.47,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (158.47,124.26) rectangle (161.87,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (161.87,124.26) rectangle (165.27,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (165.27,124.26) rectangle (168.66,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (168.66,124.26) rectangle (172.06,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (172.06,124.26) rectangle (175.46,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (175.46,124.26) rectangle (178.86,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (178.86,124.26) rectangle (182.26,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (182.26,124.26) rectangle (185.65,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (185.65,124.26) rectangle (189.05,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (189.05,124.26) rectangle (192.45,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (192.45,124.26) rectangle (195.85,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (195.85,124.26) rectangle (199.25,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (199.25,124.26) rectangle (202.64,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (202.64,124.26) rectangle (206.04,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (206.04,124.26) rectangle (209.44,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (209.44,124.26) rectangle (212.84,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (212.84,124.26) rectangle (216.24,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (216.24,124.26) rectangle (219.64,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (219.64,124.26) rectangle (223.03,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (223.03,124.26) rectangle (226.43,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (226.43,124.26) rectangle (229.83,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (229.83,124.26) rectangle (233.23,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (233.23,124.26) rectangle (236.63,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (236.63,124.26) rectangle (240.02,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (240.02,124.26) rectangle (243.42,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (243.42,124.26) rectangle (246.82,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (246.82,124.26) rectangle (250.22,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (250.22,124.26) rectangle (253.62,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (253.62,124.26) rectangle (257.01,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (257.01,124.26) rectangle (260.41,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (260.41,124.26) rectangle (263.81,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (263.81,124.26) rectangle (267.21,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (267.21,124.26) rectangle (270.61,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (270.61,124.26) rectangle (274.00,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (274.00,124.26) rectangle (277.40,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (277.40,124.26) rectangle (280.80,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (280.80,124.26) rectangle (284.20,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (284.20,124.26) rectangle (287.60,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (287.60,124.26) rectangle (290.99,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (290.99,124.26) rectangle (294.39,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (294.39,124.26) rectangle (297.79,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (297.79,124.26) rectangle (301.19,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (301.19,124.26) rectangle (304.59,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (304.59,124.26) rectangle (307.98,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (307.98,124.26) rectangle (311.38,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (311.38,124.26) rectangle (314.78,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (314.78,124.26) rectangle (318.18,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (318.18,124.26) rectangle (321.58,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (321.58,124.26) rectangle (324.97,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (324.97,124.26) rectangle (328.37,127.66);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (328.37,124.26) rectangle (331.77,127.66);
\definecolor{fillColor}{RGB}{54,100,139}

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 29.34,127.66) rectangle ( 32.74,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 32.74,127.66) rectangle ( 36.14,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 36.14,127.66) rectangle ( 39.54,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 39.54,127.66) rectangle ( 42.94,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 42.94,127.66) rectangle ( 46.33,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 46.33,127.66) rectangle ( 49.73,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 49.73,127.66) rectangle ( 53.13,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 53.13,127.66) rectangle ( 56.53,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 56.53,127.66) rectangle ( 59.93,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 59.93,127.66) rectangle ( 63.32,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 63.32,127.66) rectangle ( 66.72,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 66.72,127.66) rectangle ( 70.12,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 70.12,127.66) rectangle ( 73.52,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 73.52,127.66) rectangle ( 76.92,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 76.92,127.66) rectangle ( 80.32,131.06);
\definecolor{fillColor}{RGB}{190,190,190}

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 80.32,127.66) rectangle ( 83.71,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 83.71,127.66) rectangle ( 87.11,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 87.11,127.66) rectangle ( 90.51,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 90.51,127.66) rectangle ( 93.91,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 93.91,127.66) rectangle ( 97.31,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 97.31,127.66) rectangle (100.70,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (100.70,127.66) rectangle (104.10,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (104.10,127.66) rectangle (107.50,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (107.50,127.66) rectangle (110.90,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (110.90,127.66) rectangle (114.30,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (114.30,127.66) rectangle (117.69,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (117.69,127.66) rectangle (121.09,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (121.09,127.66) rectangle (124.49,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (124.49,127.66) rectangle (127.89,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (127.89,127.66) rectangle (131.29,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (131.29,127.66) rectangle (134.68,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (134.68,127.66) rectangle (138.08,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (138.08,127.66) rectangle (141.48,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (141.48,127.66) rectangle (144.88,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (144.88,127.66) rectangle (148.28,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (148.28,127.66) rectangle (151.67,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (151.67,127.66) rectangle (155.07,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (155.07,127.66) rectangle (158.47,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (158.47,127.66) rectangle (161.87,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (161.87,127.66) rectangle (165.27,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (165.27,127.66) rectangle (168.66,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (168.66,127.66) rectangle (172.06,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (172.06,127.66) rectangle (175.46,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (175.46,127.66) rectangle (178.86,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (178.86,127.66) rectangle (182.26,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (182.26,127.66) rectangle (185.65,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (185.65,127.66) rectangle (189.05,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (189.05,127.66) rectangle (192.45,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (192.45,127.66) rectangle (195.85,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (195.85,127.66) rectangle (199.25,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (199.25,127.66) rectangle (202.64,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (202.64,127.66) rectangle (206.04,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (206.04,127.66) rectangle (209.44,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (209.44,127.66) rectangle (212.84,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (212.84,127.66) rectangle (216.24,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (216.24,127.66) rectangle (219.64,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (219.64,127.66) rectangle (223.03,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (223.03,127.66) rectangle (226.43,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (226.43,127.66) rectangle (229.83,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (229.83,127.66) rectangle (233.23,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (233.23,127.66) rectangle (236.63,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (236.63,127.66) rectangle (240.02,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (240.02,127.66) rectangle (243.42,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (243.42,127.66) rectangle (246.82,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (246.82,127.66) rectangle (250.22,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (250.22,127.66) rectangle (253.62,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (253.62,127.66) rectangle (257.01,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (257.01,127.66) rectangle (260.41,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (260.41,127.66) rectangle (263.81,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (263.81,127.66) rectangle (267.21,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (267.21,127.66) rectangle (270.61,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (270.61,127.66) rectangle (274.00,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (274.00,127.66) rectangle (277.40,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (277.40,127.66) rectangle (280.80,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (280.80,127.66) rectangle (284.20,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (284.20,127.66) rectangle (287.60,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (287.60,127.66) rectangle (290.99,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (290.99,127.66) rectangle (294.39,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (294.39,127.66) rectangle (297.79,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (297.79,127.66) rectangle (301.19,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (301.19,127.66) rectangle (304.59,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (304.59,127.66) rectangle (307.98,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (307.98,127.66) rectangle (311.38,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (311.38,127.66) rectangle (314.78,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (314.78,127.66) rectangle (318.18,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (318.18,127.66) rectangle (321.58,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (321.58,127.66) rectangle (324.97,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (324.97,127.66) rectangle (328.37,131.06);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (328.37,127.66) rectangle (331.77,131.06);
\definecolor{fillColor}{RGB}{54,100,139}

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 29.34,131.06) rectangle ( 32.74,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 32.74,131.06) rectangle ( 36.14,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 36.14,131.06) rectangle ( 39.54,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 39.54,131.06) rectangle ( 42.94,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 42.94,131.06) rectangle ( 46.33,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 46.33,131.06) rectangle ( 49.73,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 49.73,131.06) rectangle ( 53.13,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 53.13,131.06) rectangle ( 56.53,134.45);
\definecolor{fillColor}{RGB}{190,190,190}

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 56.53,131.06) rectangle ( 59.93,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 59.93,131.06) rectangle ( 63.32,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 63.32,131.06) rectangle ( 66.72,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 66.72,131.06) rectangle ( 70.12,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 70.12,131.06) rectangle ( 73.52,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 73.52,131.06) rectangle ( 76.92,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 76.92,131.06) rectangle ( 80.32,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 80.32,131.06) rectangle ( 83.71,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 83.71,131.06) rectangle ( 87.11,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 87.11,131.06) rectangle ( 90.51,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 90.51,131.06) rectangle ( 93.91,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 93.91,131.06) rectangle ( 97.31,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 97.31,131.06) rectangle (100.70,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (100.70,131.06) rectangle (104.10,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (104.10,131.06) rectangle (107.50,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (107.50,131.06) rectangle (110.90,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (110.90,131.06) rectangle (114.30,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (114.30,131.06) rectangle (117.69,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (117.69,131.06) rectangle (121.09,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (121.09,131.06) rectangle (124.49,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (124.49,131.06) rectangle (127.89,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (127.89,131.06) rectangle (131.29,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (131.29,131.06) rectangle (134.68,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (134.68,131.06) rectangle (138.08,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (138.08,131.06) rectangle (141.48,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (141.48,131.06) rectangle (144.88,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (144.88,131.06) rectangle (148.28,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (148.28,131.06) rectangle (151.67,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (151.67,131.06) rectangle (155.07,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (155.07,131.06) rectangle (158.47,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (158.47,131.06) rectangle (161.87,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (161.87,131.06) rectangle (165.27,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (165.27,131.06) rectangle (168.66,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (168.66,131.06) rectangle (172.06,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (172.06,131.06) rectangle (175.46,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (175.46,131.06) rectangle (178.86,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (178.86,131.06) rectangle (182.26,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (182.26,131.06) rectangle (185.65,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (185.65,131.06) rectangle (189.05,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (189.05,131.06) rectangle (192.45,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (192.45,131.06) rectangle (195.85,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (195.85,131.06) rectangle (199.25,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (199.25,131.06) rectangle (202.64,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (202.64,131.06) rectangle (206.04,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (206.04,131.06) rectangle (209.44,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (209.44,131.06) rectangle (212.84,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (212.84,131.06) rectangle (216.24,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (216.24,131.06) rectangle (219.64,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (219.64,131.06) rectangle (223.03,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (223.03,131.06) rectangle (226.43,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (226.43,131.06) rectangle (229.83,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (229.83,131.06) rectangle (233.23,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (233.23,131.06) rectangle (236.63,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (236.63,131.06) rectangle (240.02,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (240.02,131.06) rectangle (243.42,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (243.42,131.06) rectangle (246.82,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (246.82,131.06) rectangle (250.22,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (250.22,131.06) rectangle (253.62,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (253.62,131.06) rectangle (257.01,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (257.01,131.06) rectangle (260.41,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (260.41,131.06) rectangle (263.81,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (263.81,131.06) rectangle (267.21,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (267.21,131.06) rectangle (270.61,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (270.61,131.06) rectangle (274.00,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (274.00,131.06) rectangle (277.40,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (277.40,131.06) rectangle (280.80,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (280.80,131.06) rectangle (284.20,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (284.20,131.06) rectangle (287.60,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (287.60,131.06) rectangle (290.99,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (290.99,131.06) rectangle (294.39,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (294.39,131.06) rectangle (297.79,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (297.79,131.06) rectangle (301.19,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (301.19,131.06) rectangle (304.59,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (304.59,131.06) rectangle (307.98,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (307.98,131.06) rectangle (311.38,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (311.38,131.06) rectangle (314.78,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (314.78,131.06) rectangle (318.18,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (318.18,131.06) rectangle (321.58,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (321.58,131.06) rectangle (324.97,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (324.97,131.06) rectangle (328.37,134.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (328.37,131.06) rectangle (331.77,134.45);
\definecolor{fillColor}{RGB}{54,100,139}

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 29.34,134.45) rectangle ( 32.74,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 32.74,134.45) rectangle ( 36.14,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 36.14,134.45) rectangle ( 39.54,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 39.54,134.45) rectangle ( 42.94,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 42.94,134.45) rectangle ( 46.33,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 46.33,134.45) rectangle ( 49.73,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 49.73,134.45) rectangle ( 53.13,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 53.13,134.45) rectangle ( 56.53,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 56.53,134.45) rectangle ( 59.93,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 59.93,134.45) rectangle ( 63.32,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 63.32,134.45) rectangle ( 66.72,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 66.72,134.45) rectangle ( 70.12,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 70.12,134.45) rectangle ( 73.52,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 73.52,134.45) rectangle ( 76.92,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 76.92,134.45) rectangle ( 80.32,137.85);
\definecolor{fillColor}{RGB}{190,190,190}

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 80.32,134.45) rectangle ( 83.71,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 83.71,134.45) rectangle ( 87.11,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 87.11,134.45) rectangle ( 90.51,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 90.51,134.45) rectangle ( 93.91,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 93.91,134.45) rectangle ( 97.31,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 97.31,134.45) rectangle (100.70,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (100.70,134.45) rectangle (104.10,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (104.10,134.45) rectangle (107.50,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (107.50,134.45) rectangle (110.90,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (110.90,134.45) rectangle (114.30,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (114.30,134.45) rectangle (117.69,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (117.69,134.45) rectangle (121.09,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (121.09,134.45) rectangle (124.49,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (124.49,134.45) rectangle (127.89,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (127.89,134.45) rectangle (131.29,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (131.29,134.45) rectangle (134.68,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (134.68,134.45) rectangle (138.08,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (138.08,134.45) rectangle (141.48,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (141.48,134.45) rectangle (144.88,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (144.88,134.45) rectangle (148.28,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (148.28,134.45) rectangle (151.67,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (151.67,134.45) rectangle (155.07,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (155.07,134.45) rectangle (158.47,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (158.47,134.45) rectangle (161.87,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (161.87,134.45) rectangle (165.27,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (165.27,134.45) rectangle (168.66,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (168.66,134.45) rectangle (172.06,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (172.06,134.45) rectangle (175.46,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (175.46,134.45) rectangle (178.86,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (178.86,134.45) rectangle (182.26,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (182.26,134.45) rectangle (185.65,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (185.65,134.45) rectangle (189.05,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (189.05,134.45) rectangle (192.45,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (192.45,134.45) rectangle (195.85,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (195.85,134.45) rectangle (199.25,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (199.25,134.45) rectangle (202.64,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (202.64,134.45) rectangle (206.04,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (206.04,134.45) rectangle (209.44,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (209.44,134.45) rectangle (212.84,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (212.84,134.45) rectangle (216.24,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (216.24,134.45) rectangle (219.64,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (219.64,134.45) rectangle (223.03,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (223.03,134.45) rectangle (226.43,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (226.43,134.45) rectangle (229.83,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (229.83,134.45) rectangle (233.23,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (233.23,134.45) rectangle (236.63,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (236.63,134.45) rectangle (240.02,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (240.02,134.45) rectangle (243.42,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (243.42,134.45) rectangle (246.82,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (246.82,134.45) rectangle (250.22,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (250.22,134.45) rectangle (253.62,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (253.62,134.45) rectangle (257.01,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (257.01,134.45) rectangle (260.41,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (260.41,134.45) rectangle (263.81,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (263.81,134.45) rectangle (267.21,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (267.21,134.45) rectangle (270.61,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (270.61,134.45) rectangle (274.00,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (274.00,134.45) rectangle (277.40,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (277.40,134.45) rectangle (280.80,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (280.80,134.45) rectangle (284.20,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (284.20,134.45) rectangle (287.60,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (287.60,134.45) rectangle (290.99,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (290.99,134.45) rectangle (294.39,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (294.39,134.45) rectangle (297.79,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (297.79,134.45) rectangle (301.19,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (301.19,134.45) rectangle (304.59,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (304.59,134.45) rectangle (307.98,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (307.98,134.45) rectangle (311.38,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (311.38,134.45) rectangle (314.78,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (314.78,134.45) rectangle (318.18,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (318.18,134.45) rectangle (321.58,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (321.58,134.45) rectangle (324.97,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (324.97,134.45) rectangle (328.37,137.85);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (328.37,134.45) rectangle (331.77,137.85);
\definecolor{fillColor}{RGB}{54,100,139}

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 29.34,137.85) rectangle ( 32.74,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 32.74,137.85) rectangle ( 36.14,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 36.14,137.85) rectangle ( 39.54,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 39.54,137.85) rectangle ( 42.94,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 42.94,137.85) rectangle ( 46.33,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 46.33,137.85) rectangle ( 49.73,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 49.73,137.85) rectangle ( 53.13,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 53.13,137.85) rectangle ( 56.53,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 56.53,137.85) rectangle ( 59.93,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 59.93,137.85) rectangle ( 63.32,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 63.32,137.85) rectangle ( 66.72,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 66.72,137.85) rectangle ( 70.12,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 70.12,137.85) rectangle ( 73.52,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 73.52,137.85) rectangle ( 76.92,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 76.92,137.85) rectangle ( 80.32,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 80.32,137.85) rectangle ( 83.71,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 83.71,137.85) rectangle ( 87.11,141.25);
\definecolor{fillColor}{RGB}{190,190,190}

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 87.11,137.85) rectangle ( 90.51,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 90.51,137.85) rectangle ( 93.91,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 93.91,137.85) rectangle ( 97.31,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 97.31,137.85) rectangle (100.70,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (100.70,137.85) rectangle (104.10,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (104.10,137.85) rectangle (107.50,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (107.50,137.85) rectangle (110.90,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (110.90,137.85) rectangle (114.30,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (114.30,137.85) rectangle (117.69,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (117.69,137.85) rectangle (121.09,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (121.09,137.85) rectangle (124.49,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (124.49,137.85) rectangle (127.89,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (127.89,137.85) rectangle (131.29,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (131.29,137.85) rectangle (134.68,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (134.68,137.85) rectangle (138.08,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (138.08,137.85) rectangle (141.48,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (141.48,137.85) rectangle (144.88,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (144.88,137.85) rectangle (148.28,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (148.28,137.85) rectangle (151.67,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (151.67,137.85) rectangle (155.07,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (155.07,137.85) rectangle (158.47,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (158.47,137.85) rectangle (161.87,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (161.87,137.85) rectangle (165.27,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (165.27,137.85) rectangle (168.66,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (168.66,137.85) rectangle (172.06,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (172.06,137.85) rectangle (175.46,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (175.46,137.85) rectangle (178.86,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (178.86,137.85) rectangle (182.26,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (182.26,137.85) rectangle (185.65,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (185.65,137.85) rectangle (189.05,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (189.05,137.85) rectangle (192.45,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (192.45,137.85) rectangle (195.85,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (195.85,137.85) rectangle (199.25,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (199.25,137.85) rectangle (202.64,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (202.64,137.85) rectangle (206.04,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (206.04,137.85) rectangle (209.44,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (209.44,137.85) rectangle (212.84,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (212.84,137.85) rectangle (216.24,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (216.24,137.85) rectangle (219.64,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (219.64,137.85) rectangle (223.03,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (223.03,137.85) rectangle (226.43,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (226.43,137.85) rectangle (229.83,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (229.83,137.85) rectangle (233.23,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (233.23,137.85) rectangle (236.63,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (236.63,137.85) rectangle (240.02,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (240.02,137.85) rectangle (243.42,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (243.42,137.85) rectangle (246.82,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (246.82,137.85) rectangle (250.22,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (250.22,137.85) rectangle (253.62,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (253.62,137.85) rectangle (257.01,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (257.01,137.85) rectangle (260.41,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (260.41,137.85) rectangle (263.81,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (263.81,137.85) rectangle (267.21,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (267.21,137.85) rectangle (270.61,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (270.61,137.85) rectangle (274.00,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (274.00,137.85) rectangle (277.40,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (277.40,137.85) rectangle (280.80,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (280.80,137.85) rectangle (284.20,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (284.20,137.85) rectangle (287.60,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (287.60,137.85) rectangle (290.99,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (290.99,137.85) rectangle (294.39,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (294.39,137.85) rectangle (297.79,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (297.79,137.85) rectangle (301.19,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (301.19,137.85) rectangle (304.59,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (304.59,137.85) rectangle (307.98,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (307.98,137.85) rectangle (311.38,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (311.38,137.85) rectangle (314.78,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (314.78,137.85) rectangle (318.18,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (318.18,137.85) rectangle (321.58,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (321.58,137.85) rectangle (324.97,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (324.97,137.85) rectangle (328.37,141.25);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (328.37,137.85) rectangle (331.77,141.25);
\definecolor{fillColor}{RGB}{54,100,139}

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 29.34,141.25) rectangle ( 32.74,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 32.74,141.25) rectangle ( 36.14,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 36.14,141.25) rectangle ( 39.54,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 39.54,141.25) rectangle ( 42.94,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 42.94,141.25) rectangle ( 46.33,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 46.33,141.25) rectangle ( 49.73,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 49.73,141.25) rectangle ( 53.13,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 53.13,141.25) rectangle ( 56.53,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 56.53,141.25) rectangle ( 59.93,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 59.93,141.25) rectangle ( 63.32,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 63.32,141.25) rectangle ( 66.72,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 66.72,141.25) rectangle ( 70.12,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 70.12,141.25) rectangle ( 73.52,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 73.52,141.25) rectangle ( 76.92,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 76.92,141.25) rectangle ( 80.32,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 80.32,141.25) rectangle ( 83.71,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 83.71,141.25) rectangle ( 87.11,144.65);
\definecolor{fillColor}{RGB}{190,190,190}

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 87.11,141.25) rectangle ( 90.51,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 90.51,141.25) rectangle ( 93.91,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 93.91,141.25) rectangle ( 97.31,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 97.31,141.25) rectangle (100.70,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (100.70,141.25) rectangle (104.10,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (104.10,141.25) rectangle (107.50,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (107.50,141.25) rectangle (110.90,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (110.90,141.25) rectangle (114.30,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (114.30,141.25) rectangle (117.69,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (117.69,141.25) rectangle (121.09,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (121.09,141.25) rectangle (124.49,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (124.49,141.25) rectangle (127.89,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (127.89,141.25) rectangle (131.29,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (131.29,141.25) rectangle (134.68,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (134.68,141.25) rectangle (138.08,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (138.08,141.25) rectangle (141.48,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (141.48,141.25) rectangle (144.88,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (144.88,141.25) rectangle (148.28,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (148.28,141.25) rectangle (151.67,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (151.67,141.25) rectangle (155.07,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (155.07,141.25) rectangle (158.47,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (158.47,141.25) rectangle (161.87,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (161.87,141.25) rectangle (165.27,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (165.27,141.25) rectangle (168.66,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (168.66,141.25) rectangle (172.06,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (172.06,141.25) rectangle (175.46,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (175.46,141.25) rectangle (178.86,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (178.86,141.25) rectangle (182.26,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (182.26,141.25) rectangle (185.65,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (185.65,141.25) rectangle (189.05,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (189.05,141.25) rectangle (192.45,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (192.45,141.25) rectangle (195.85,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (195.85,141.25) rectangle (199.25,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (199.25,141.25) rectangle (202.64,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (202.64,141.25) rectangle (206.04,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (206.04,141.25) rectangle (209.44,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (209.44,141.25) rectangle (212.84,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (212.84,141.25) rectangle (216.24,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (216.24,141.25) rectangle (219.64,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (219.64,141.25) rectangle (223.03,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (223.03,141.25) rectangle (226.43,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (226.43,141.25) rectangle (229.83,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (229.83,141.25) rectangle (233.23,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (233.23,141.25) rectangle (236.63,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (236.63,141.25) rectangle (240.02,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (240.02,141.25) rectangle (243.42,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (243.42,141.25) rectangle (246.82,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (246.82,141.25) rectangle (250.22,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (250.22,141.25) rectangle (253.62,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (253.62,141.25) rectangle (257.01,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (257.01,141.25) rectangle (260.41,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (260.41,141.25) rectangle (263.81,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (263.81,141.25) rectangle (267.21,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (267.21,141.25) rectangle (270.61,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (270.61,141.25) rectangle (274.00,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (274.00,141.25) rectangle (277.40,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (277.40,141.25) rectangle (280.80,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (280.80,141.25) rectangle (284.20,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (284.20,141.25) rectangle (287.60,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (287.60,141.25) rectangle (290.99,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (290.99,141.25) rectangle (294.39,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (294.39,141.25) rectangle (297.79,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (297.79,141.25) rectangle (301.19,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (301.19,141.25) rectangle (304.59,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (304.59,141.25) rectangle (307.98,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (307.98,141.25) rectangle (311.38,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (311.38,141.25) rectangle (314.78,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (314.78,141.25) rectangle (318.18,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (318.18,141.25) rectangle (321.58,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (321.58,141.25) rectangle (324.97,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (324.97,141.25) rectangle (328.37,144.65);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (328.37,141.25) rectangle (331.77,144.65);
\definecolor{fillColor}{RGB}{54,100,139}

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 29.34,144.65) rectangle ( 32.74,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 32.74,144.65) rectangle ( 36.14,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 36.14,144.65) rectangle ( 39.54,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 39.54,144.65) rectangle ( 42.94,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 42.94,144.65) rectangle ( 46.33,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 46.33,144.65) rectangle ( 49.73,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 49.73,144.65) rectangle ( 53.13,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 53.13,144.65) rectangle ( 56.53,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 56.53,144.65) rectangle ( 59.93,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 59.93,144.65) rectangle ( 63.32,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 63.32,144.65) rectangle ( 66.72,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 66.72,144.65) rectangle ( 70.12,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 70.12,144.65) rectangle ( 73.52,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 73.52,144.65) rectangle ( 76.92,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 76.92,144.65) rectangle ( 80.32,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 80.32,144.65) rectangle ( 83.71,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 83.71,144.65) rectangle ( 87.11,148.05);
\definecolor{fillColor}{RGB}{190,190,190}

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 87.11,144.65) rectangle ( 90.51,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 90.51,144.65) rectangle ( 93.91,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 93.91,144.65) rectangle ( 97.31,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 97.31,144.65) rectangle (100.70,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (100.70,144.65) rectangle (104.10,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (104.10,144.65) rectangle (107.50,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (107.50,144.65) rectangle (110.90,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (110.90,144.65) rectangle (114.30,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (114.30,144.65) rectangle (117.69,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (117.69,144.65) rectangle (121.09,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (121.09,144.65) rectangle (124.49,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (124.49,144.65) rectangle (127.89,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (127.89,144.65) rectangle (131.29,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (131.29,144.65) rectangle (134.68,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (134.68,144.65) rectangle (138.08,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (138.08,144.65) rectangle (141.48,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (141.48,144.65) rectangle (144.88,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (144.88,144.65) rectangle (148.28,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (148.28,144.65) rectangle (151.67,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (151.67,144.65) rectangle (155.07,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (155.07,144.65) rectangle (158.47,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (158.47,144.65) rectangle (161.87,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (161.87,144.65) rectangle (165.27,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (165.27,144.65) rectangle (168.66,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (168.66,144.65) rectangle (172.06,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (172.06,144.65) rectangle (175.46,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (175.46,144.65) rectangle (178.86,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (178.86,144.65) rectangle (182.26,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (182.26,144.65) rectangle (185.65,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (185.65,144.65) rectangle (189.05,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (189.05,144.65) rectangle (192.45,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (192.45,144.65) rectangle (195.85,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (195.85,144.65) rectangle (199.25,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (199.25,144.65) rectangle (202.64,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (202.64,144.65) rectangle (206.04,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (206.04,144.65) rectangle (209.44,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (209.44,144.65) rectangle (212.84,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (212.84,144.65) rectangle (216.24,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (216.24,144.65) rectangle (219.64,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (219.64,144.65) rectangle (223.03,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (223.03,144.65) rectangle (226.43,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (226.43,144.65) rectangle (229.83,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (229.83,144.65) rectangle (233.23,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (233.23,144.65) rectangle (236.63,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (236.63,144.65) rectangle (240.02,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (240.02,144.65) rectangle (243.42,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (243.42,144.65) rectangle (246.82,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (246.82,144.65) rectangle (250.22,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (250.22,144.65) rectangle (253.62,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (253.62,144.65) rectangle (257.01,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (257.01,144.65) rectangle (260.41,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (260.41,144.65) rectangle (263.81,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (263.81,144.65) rectangle (267.21,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (267.21,144.65) rectangle (270.61,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (270.61,144.65) rectangle (274.00,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (274.00,144.65) rectangle (277.40,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (277.40,144.65) rectangle (280.80,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (280.80,144.65) rectangle (284.20,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (284.20,144.65) rectangle (287.60,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (287.60,144.65) rectangle (290.99,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (290.99,144.65) rectangle (294.39,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (294.39,144.65) rectangle (297.79,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (297.79,144.65) rectangle (301.19,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (301.19,144.65) rectangle (304.59,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (304.59,144.65) rectangle (307.98,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (307.98,144.65) rectangle (311.38,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (311.38,144.65) rectangle (314.78,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (314.78,144.65) rectangle (318.18,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (318.18,144.65) rectangle (321.58,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (321.58,144.65) rectangle (324.97,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (324.97,144.65) rectangle (328.37,148.05);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (328.37,144.65) rectangle (331.77,148.05);
\definecolor{fillColor}{RGB}{54,100,139}

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 29.34,148.05) rectangle ( 32.74,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 32.74,148.05) rectangle ( 36.14,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 36.14,148.05) rectangle ( 39.54,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 39.54,148.05) rectangle ( 42.94,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 42.94,148.05) rectangle ( 46.33,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 46.33,148.05) rectangle ( 49.73,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 49.73,148.05) rectangle ( 53.13,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 53.13,148.05) rectangle ( 56.53,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 56.53,148.05) rectangle ( 59.93,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 59.93,148.05) rectangle ( 63.32,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 63.32,148.05) rectangle ( 66.72,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 66.72,148.05) rectangle ( 70.12,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 70.12,148.05) rectangle ( 73.52,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 73.52,148.05) rectangle ( 76.92,151.45);
\definecolor{fillColor}{RGB}{190,190,190}

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 76.92,148.05) rectangle ( 80.32,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 80.32,148.05) rectangle ( 83.71,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 83.71,148.05) rectangle ( 87.11,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 87.11,148.05) rectangle ( 90.51,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 90.51,148.05) rectangle ( 93.91,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 93.91,148.05) rectangle ( 97.31,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 97.31,148.05) rectangle (100.70,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (100.70,148.05) rectangle (104.10,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (104.10,148.05) rectangle (107.50,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (107.50,148.05) rectangle (110.90,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (110.90,148.05) rectangle (114.30,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (114.30,148.05) rectangle (117.69,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (117.69,148.05) rectangle (121.09,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (121.09,148.05) rectangle (124.49,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (124.49,148.05) rectangle (127.89,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (127.89,148.05) rectangle (131.29,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (131.29,148.05) rectangle (134.68,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (134.68,148.05) rectangle (138.08,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (138.08,148.05) rectangle (141.48,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (141.48,148.05) rectangle (144.88,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (144.88,148.05) rectangle (148.28,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (148.28,148.05) rectangle (151.67,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (151.67,148.05) rectangle (155.07,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (155.07,148.05) rectangle (158.47,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (158.47,148.05) rectangle (161.87,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (161.87,148.05) rectangle (165.27,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (165.27,148.05) rectangle (168.66,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (168.66,148.05) rectangle (172.06,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (172.06,148.05) rectangle (175.46,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (175.46,148.05) rectangle (178.86,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (178.86,148.05) rectangle (182.26,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (182.26,148.05) rectangle (185.65,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (185.65,148.05) rectangle (189.05,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (189.05,148.05) rectangle (192.45,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (192.45,148.05) rectangle (195.85,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (195.85,148.05) rectangle (199.25,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (199.25,148.05) rectangle (202.64,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (202.64,148.05) rectangle (206.04,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (206.04,148.05) rectangle (209.44,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (209.44,148.05) rectangle (212.84,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (212.84,148.05) rectangle (216.24,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (216.24,148.05) rectangle (219.64,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (219.64,148.05) rectangle (223.03,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (223.03,148.05) rectangle (226.43,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (226.43,148.05) rectangle (229.83,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (229.83,148.05) rectangle (233.23,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (233.23,148.05) rectangle (236.63,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (236.63,148.05) rectangle (240.02,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (240.02,148.05) rectangle (243.42,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (243.42,148.05) rectangle (246.82,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (246.82,148.05) rectangle (250.22,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (250.22,148.05) rectangle (253.62,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (253.62,148.05) rectangle (257.01,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (257.01,148.05) rectangle (260.41,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (260.41,148.05) rectangle (263.81,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (263.81,148.05) rectangle (267.21,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (267.21,148.05) rectangle (270.61,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (270.61,148.05) rectangle (274.00,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (274.00,148.05) rectangle (277.40,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (277.40,148.05) rectangle (280.80,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (280.80,148.05) rectangle (284.20,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (284.20,148.05) rectangle (287.60,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (287.60,148.05) rectangle (290.99,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (290.99,148.05) rectangle (294.39,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (294.39,148.05) rectangle (297.79,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (297.79,148.05) rectangle (301.19,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (301.19,148.05) rectangle (304.59,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (304.59,148.05) rectangle (307.98,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (307.98,148.05) rectangle (311.38,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (311.38,148.05) rectangle (314.78,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (314.78,148.05) rectangle (318.18,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (318.18,148.05) rectangle (321.58,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (321.58,148.05) rectangle (324.97,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (324.97,148.05) rectangle (328.37,151.45);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (328.37,148.05) rectangle (331.77,151.45);
\definecolor{fillColor}{RGB}{54,100,139}

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 29.34,151.45) rectangle ( 32.74,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 32.74,151.45) rectangle ( 36.14,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 36.14,151.45) rectangle ( 39.54,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 39.54,151.45) rectangle ( 42.94,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 42.94,151.45) rectangle ( 46.33,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 46.33,151.45) rectangle ( 49.73,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 49.73,151.45) rectangle ( 53.13,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 53.13,151.45) rectangle ( 56.53,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 56.53,151.45) rectangle ( 59.93,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 59.93,151.45) rectangle ( 63.32,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 63.32,151.45) rectangle ( 66.72,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 66.72,151.45) rectangle ( 70.12,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 70.12,151.45) rectangle ( 73.52,154.84);
\definecolor{fillColor}{RGB}{190,190,190}

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 73.52,151.45) rectangle ( 76.92,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 76.92,151.45) rectangle ( 80.32,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 80.32,151.45) rectangle ( 83.71,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 83.71,151.45) rectangle ( 87.11,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 87.11,151.45) rectangle ( 90.51,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 90.51,151.45) rectangle ( 93.91,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 93.91,151.45) rectangle ( 97.31,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 97.31,151.45) rectangle (100.70,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (100.70,151.45) rectangle (104.10,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (104.10,151.45) rectangle (107.50,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (107.50,151.45) rectangle (110.90,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (110.90,151.45) rectangle (114.30,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (114.30,151.45) rectangle (117.69,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (117.69,151.45) rectangle (121.09,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (121.09,151.45) rectangle (124.49,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (124.49,151.45) rectangle (127.89,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (127.89,151.45) rectangle (131.29,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (131.29,151.45) rectangle (134.68,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (134.68,151.45) rectangle (138.08,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (138.08,151.45) rectangle (141.48,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (141.48,151.45) rectangle (144.88,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (144.88,151.45) rectangle (148.28,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (148.28,151.45) rectangle (151.67,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (151.67,151.45) rectangle (155.07,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (155.07,151.45) rectangle (158.47,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (158.47,151.45) rectangle (161.87,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (161.87,151.45) rectangle (165.27,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (165.27,151.45) rectangle (168.66,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (168.66,151.45) rectangle (172.06,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (172.06,151.45) rectangle (175.46,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (175.46,151.45) rectangle (178.86,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (178.86,151.45) rectangle (182.26,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (182.26,151.45) rectangle (185.65,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (185.65,151.45) rectangle (189.05,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (189.05,151.45) rectangle (192.45,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (192.45,151.45) rectangle (195.85,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (195.85,151.45) rectangle (199.25,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (199.25,151.45) rectangle (202.64,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (202.64,151.45) rectangle (206.04,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (206.04,151.45) rectangle (209.44,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (209.44,151.45) rectangle (212.84,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (212.84,151.45) rectangle (216.24,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (216.24,151.45) rectangle (219.64,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (219.64,151.45) rectangle (223.03,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (223.03,151.45) rectangle (226.43,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (226.43,151.45) rectangle (229.83,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (229.83,151.45) rectangle (233.23,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (233.23,151.45) rectangle (236.63,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (236.63,151.45) rectangle (240.02,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (240.02,151.45) rectangle (243.42,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (243.42,151.45) rectangle (246.82,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (246.82,151.45) rectangle (250.22,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (250.22,151.45) rectangle (253.62,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (253.62,151.45) rectangle (257.01,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (257.01,151.45) rectangle (260.41,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (260.41,151.45) rectangle (263.81,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (263.81,151.45) rectangle (267.21,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (267.21,151.45) rectangle (270.61,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (270.61,151.45) rectangle (274.00,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (274.00,151.45) rectangle (277.40,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (277.40,151.45) rectangle (280.80,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (280.80,151.45) rectangle (284.20,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (284.20,151.45) rectangle (287.60,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (287.60,151.45) rectangle (290.99,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (290.99,151.45) rectangle (294.39,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (294.39,151.45) rectangle (297.79,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (297.79,151.45) rectangle (301.19,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (301.19,151.45) rectangle (304.59,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (304.59,151.45) rectangle (307.98,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (307.98,151.45) rectangle (311.38,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (311.38,151.45) rectangle (314.78,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (314.78,151.45) rectangle (318.18,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (318.18,151.45) rectangle (321.58,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (321.58,151.45) rectangle (324.97,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (324.97,151.45) rectangle (328.37,154.84);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (328.37,151.45) rectangle (331.77,154.84);
\definecolor{fillColor}{RGB}{54,100,139}

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 29.34,154.84) rectangle ( 32.74,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 32.74,154.84) rectangle ( 36.14,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 36.14,154.84) rectangle ( 39.54,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 39.54,154.84) rectangle ( 42.94,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 42.94,154.84) rectangle ( 46.33,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 46.33,154.84) rectangle ( 49.73,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 49.73,154.84) rectangle ( 53.13,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 53.13,154.84) rectangle ( 56.53,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 56.53,154.84) rectangle ( 59.93,158.24);
\definecolor{fillColor}{RGB}{190,190,190}

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 59.93,154.84) rectangle ( 63.32,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 63.32,154.84) rectangle ( 66.72,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 66.72,154.84) rectangle ( 70.12,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 70.12,154.84) rectangle ( 73.52,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 73.52,154.84) rectangle ( 76.92,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 76.92,154.84) rectangle ( 80.32,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 80.32,154.84) rectangle ( 83.71,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 83.71,154.84) rectangle ( 87.11,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 87.11,154.84) rectangle ( 90.51,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 90.51,154.84) rectangle ( 93.91,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 93.91,154.84) rectangle ( 97.31,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 97.31,154.84) rectangle (100.70,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (100.70,154.84) rectangle (104.10,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (104.10,154.84) rectangle (107.50,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (107.50,154.84) rectangle (110.90,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (110.90,154.84) rectangle (114.30,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (114.30,154.84) rectangle (117.69,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (117.69,154.84) rectangle (121.09,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (121.09,154.84) rectangle (124.49,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (124.49,154.84) rectangle (127.89,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (127.89,154.84) rectangle (131.29,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (131.29,154.84) rectangle (134.68,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (134.68,154.84) rectangle (138.08,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (138.08,154.84) rectangle (141.48,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (141.48,154.84) rectangle (144.88,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (144.88,154.84) rectangle (148.28,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (148.28,154.84) rectangle (151.67,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (151.67,154.84) rectangle (155.07,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (155.07,154.84) rectangle (158.47,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (158.47,154.84) rectangle (161.87,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (161.87,154.84) rectangle (165.27,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (165.27,154.84) rectangle (168.66,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (168.66,154.84) rectangle (172.06,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (172.06,154.84) rectangle (175.46,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (175.46,154.84) rectangle (178.86,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (178.86,154.84) rectangle (182.26,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (182.26,154.84) rectangle (185.65,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (185.65,154.84) rectangle (189.05,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (189.05,154.84) rectangle (192.45,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (192.45,154.84) rectangle (195.85,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (195.85,154.84) rectangle (199.25,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (199.25,154.84) rectangle (202.64,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (202.64,154.84) rectangle (206.04,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (206.04,154.84) rectangle (209.44,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (209.44,154.84) rectangle (212.84,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (212.84,154.84) rectangle (216.24,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (216.24,154.84) rectangle (219.64,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (219.64,154.84) rectangle (223.03,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (223.03,154.84) rectangle (226.43,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (226.43,154.84) rectangle (229.83,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (229.83,154.84) rectangle (233.23,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (233.23,154.84) rectangle (236.63,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (236.63,154.84) rectangle (240.02,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (240.02,154.84) rectangle (243.42,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (243.42,154.84) rectangle (246.82,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (246.82,154.84) rectangle (250.22,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (250.22,154.84) rectangle (253.62,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (253.62,154.84) rectangle (257.01,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (257.01,154.84) rectangle (260.41,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (260.41,154.84) rectangle (263.81,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (263.81,154.84) rectangle (267.21,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (267.21,154.84) rectangle (270.61,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (270.61,154.84) rectangle (274.00,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (274.00,154.84) rectangle (277.40,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (277.40,154.84) rectangle (280.80,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (280.80,154.84) rectangle (284.20,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (284.20,154.84) rectangle (287.60,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (287.60,154.84) rectangle (290.99,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (290.99,154.84) rectangle (294.39,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (294.39,154.84) rectangle (297.79,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (297.79,154.84) rectangle (301.19,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (301.19,154.84) rectangle (304.59,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (304.59,154.84) rectangle (307.98,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (307.98,154.84) rectangle (311.38,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (311.38,154.84) rectangle (314.78,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (314.78,154.84) rectangle (318.18,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (318.18,154.84) rectangle (321.58,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (321.58,154.84) rectangle (324.97,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (324.97,154.84) rectangle (328.37,158.24);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (328.37,154.84) rectangle (331.77,158.24);
\definecolor{fillColor}{RGB}{54,100,139}

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 29.34,158.24) rectangle ( 32.74,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 32.74,158.24) rectangle ( 36.14,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 36.14,158.24) rectangle ( 39.54,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 39.54,158.24) rectangle ( 42.94,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 42.94,158.24) rectangle ( 46.33,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 46.33,158.24) rectangle ( 49.73,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 49.73,158.24) rectangle ( 53.13,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 53.13,158.24) rectangle ( 56.53,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 56.53,158.24) rectangle ( 59.93,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 59.93,158.24) rectangle ( 63.32,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 63.32,158.24) rectangle ( 66.72,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 66.72,158.24) rectangle ( 70.12,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 70.12,158.24) rectangle ( 73.52,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 73.52,158.24) rectangle ( 76.92,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 76.92,158.24) rectangle ( 80.32,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 80.32,158.24) rectangle ( 83.71,161.64);
\definecolor{fillColor}{RGB}{190,190,190}

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 83.71,158.24) rectangle ( 87.11,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 87.11,158.24) rectangle ( 90.51,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 90.51,158.24) rectangle ( 93.91,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 93.91,158.24) rectangle ( 97.31,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 97.31,158.24) rectangle (100.70,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (100.70,158.24) rectangle (104.10,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (104.10,158.24) rectangle (107.50,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (107.50,158.24) rectangle (110.90,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (110.90,158.24) rectangle (114.30,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (114.30,158.24) rectangle (117.69,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (117.69,158.24) rectangle (121.09,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (121.09,158.24) rectangle (124.49,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (124.49,158.24) rectangle (127.89,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (127.89,158.24) rectangle (131.29,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (131.29,158.24) rectangle (134.68,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (134.68,158.24) rectangle (138.08,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (138.08,158.24) rectangle (141.48,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (141.48,158.24) rectangle (144.88,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (144.88,158.24) rectangle (148.28,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (148.28,158.24) rectangle (151.67,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (151.67,158.24) rectangle (155.07,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (155.07,158.24) rectangle (158.47,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (158.47,158.24) rectangle (161.87,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (161.87,158.24) rectangle (165.27,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (165.27,158.24) rectangle (168.66,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (168.66,158.24) rectangle (172.06,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (172.06,158.24) rectangle (175.46,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (175.46,158.24) rectangle (178.86,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (178.86,158.24) rectangle (182.26,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (182.26,158.24) rectangle (185.65,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (185.65,158.24) rectangle (189.05,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (189.05,158.24) rectangle (192.45,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (192.45,158.24) rectangle (195.85,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (195.85,158.24) rectangle (199.25,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (199.25,158.24) rectangle (202.64,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (202.64,158.24) rectangle (206.04,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (206.04,158.24) rectangle (209.44,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (209.44,158.24) rectangle (212.84,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (212.84,158.24) rectangle (216.24,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (216.24,158.24) rectangle (219.64,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (219.64,158.24) rectangle (223.03,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (223.03,158.24) rectangle (226.43,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (226.43,158.24) rectangle (229.83,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (229.83,158.24) rectangle (233.23,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (233.23,158.24) rectangle (236.63,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (236.63,158.24) rectangle (240.02,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (240.02,158.24) rectangle (243.42,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (243.42,158.24) rectangle (246.82,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (246.82,158.24) rectangle (250.22,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (250.22,158.24) rectangle (253.62,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (253.62,158.24) rectangle (257.01,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (257.01,158.24) rectangle (260.41,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (260.41,158.24) rectangle (263.81,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (263.81,158.24) rectangle (267.21,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (267.21,158.24) rectangle (270.61,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (270.61,158.24) rectangle (274.00,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (274.00,158.24) rectangle (277.40,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (277.40,158.24) rectangle (280.80,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (280.80,158.24) rectangle (284.20,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (284.20,158.24) rectangle (287.60,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (287.60,158.24) rectangle (290.99,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (290.99,158.24) rectangle (294.39,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (294.39,158.24) rectangle (297.79,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (297.79,158.24) rectangle (301.19,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (301.19,158.24) rectangle (304.59,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (304.59,158.24) rectangle (307.98,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (307.98,158.24) rectangle (311.38,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (311.38,158.24) rectangle (314.78,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (314.78,158.24) rectangle (318.18,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (318.18,158.24) rectangle (321.58,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (321.58,158.24) rectangle (324.97,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (324.97,158.24) rectangle (328.37,161.64);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (328.37,158.24) rectangle (331.77,161.64);
\definecolor{fillColor}{RGB}{54,100,139}

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 29.34,161.64) rectangle ( 32.74,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 32.74,161.64) rectangle ( 36.14,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 36.14,161.64) rectangle ( 39.54,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 39.54,161.64) rectangle ( 42.94,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 42.94,161.64) rectangle ( 46.33,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 46.33,161.64) rectangle ( 49.73,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 49.73,161.64) rectangle ( 53.13,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 53.13,161.64) rectangle ( 56.53,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 56.53,161.64) rectangle ( 59.93,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 59.93,161.64) rectangle ( 63.32,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 63.32,161.64) rectangle ( 66.72,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 66.72,161.64) rectangle ( 70.12,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 70.12,161.64) rectangle ( 73.52,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 73.52,161.64) rectangle ( 76.92,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 76.92,161.64) rectangle ( 80.32,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 80.32,161.64) rectangle ( 83.71,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 83.71,161.64) rectangle ( 87.11,165.04);
\definecolor{fillColor}{RGB}{190,190,190}

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 87.11,161.64) rectangle ( 90.51,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 90.51,161.64) rectangle ( 93.91,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 93.91,161.64) rectangle ( 97.31,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 97.31,161.64) rectangle (100.70,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (100.70,161.64) rectangle (104.10,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (104.10,161.64) rectangle (107.50,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (107.50,161.64) rectangle (110.90,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (110.90,161.64) rectangle (114.30,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (114.30,161.64) rectangle (117.69,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (117.69,161.64) rectangle (121.09,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (121.09,161.64) rectangle (124.49,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (124.49,161.64) rectangle (127.89,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (127.89,161.64) rectangle (131.29,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (131.29,161.64) rectangle (134.68,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (134.68,161.64) rectangle (138.08,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (138.08,161.64) rectangle (141.48,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (141.48,161.64) rectangle (144.88,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (144.88,161.64) rectangle (148.28,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (148.28,161.64) rectangle (151.67,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (151.67,161.64) rectangle (155.07,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (155.07,161.64) rectangle (158.47,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (158.47,161.64) rectangle (161.87,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (161.87,161.64) rectangle (165.27,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (165.27,161.64) rectangle (168.66,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (168.66,161.64) rectangle (172.06,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (172.06,161.64) rectangle (175.46,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (175.46,161.64) rectangle (178.86,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (178.86,161.64) rectangle (182.26,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (182.26,161.64) rectangle (185.65,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (185.65,161.64) rectangle (189.05,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (189.05,161.64) rectangle (192.45,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (192.45,161.64) rectangle (195.85,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (195.85,161.64) rectangle (199.25,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (199.25,161.64) rectangle (202.64,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (202.64,161.64) rectangle (206.04,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (206.04,161.64) rectangle (209.44,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (209.44,161.64) rectangle (212.84,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (212.84,161.64) rectangle (216.24,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (216.24,161.64) rectangle (219.64,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (219.64,161.64) rectangle (223.03,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (223.03,161.64) rectangle (226.43,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (226.43,161.64) rectangle (229.83,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (229.83,161.64) rectangle (233.23,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (233.23,161.64) rectangle (236.63,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (236.63,161.64) rectangle (240.02,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (240.02,161.64) rectangle (243.42,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (243.42,161.64) rectangle (246.82,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (246.82,161.64) rectangle (250.22,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (250.22,161.64) rectangle (253.62,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (253.62,161.64) rectangle (257.01,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (257.01,161.64) rectangle (260.41,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (260.41,161.64) rectangle (263.81,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (263.81,161.64) rectangle (267.21,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (267.21,161.64) rectangle (270.61,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (270.61,161.64) rectangle (274.00,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (274.00,161.64) rectangle (277.40,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (277.40,161.64) rectangle (280.80,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (280.80,161.64) rectangle (284.20,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (284.20,161.64) rectangle (287.60,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (287.60,161.64) rectangle (290.99,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (290.99,161.64) rectangle (294.39,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (294.39,161.64) rectangle (297.79,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (297.79,161.64) rectangle (301.19,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (301.19,161.64) rectangle (304.59,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (304.59,161.64) rectangle (307.98,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (307.98,161.64) rectangle (311.38,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (311.38,161.64) rectangle (314.78,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (314.78,161.64) rectangle (318.18,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (318.18,161.64) rectangle (321.58,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (321.58,161.64) rectangle (324.97,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (324.97,161.64) rectangle (328.37,165.04);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (328.37,161.64) rectangle (331.77,165.04);
\definecolor{fillColor}{RGB}{54,100,139}

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 29.34,165.04) rectangle ( 32.74,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 32.74,165.04) rectangle ( 36.14,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 36.14,165.04) rectangle ( 39.54,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 39.54,165.04) rectangle ( 42.94,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 42.94,165.04) rectangle ( 46.33,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 46.33,165.04) rectangle ( 49.73,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 49.73,165.04) rectangle ( 53.13,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 53.13,165.04) rectangle ( 56.53,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 56.53,165.04) rectangle ( 59.93,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 59.93,165.04) rectangle ( 63.32,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 63.32,165.04) rectangle ( 66.72,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 66.72,165.04) rectangle ( 70.12,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 70.12,165.04) rectangle ( 73.52,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 73.52,165.04) rectangle ( 76.92,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 76.92,165.04) rectangle ( 80.32,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 80.32,165.04) rectangle ( 83.71,168.44);
\definecolor{fillColor}{RGB}{190,190,190}

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 83.71,165.04) rectangle ( 87.11,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 87.11,165.04) rectangle ( 90.51,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 90.51,165.04) rectangle ( 93.91,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 93.91,165.04) rectangle ( 97.31,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 97.31,165.04) rectangle (100.70,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (100.70,165.04) rectangle (104.10,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (104.10,165.04) rectangle (107.50,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (107.50,165.04) rectangle (110.90,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (110.90,165.04) rectangle (114.30,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (114.30,165.04) rectangle (117.69,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (117.69,165.04) rectangle (121.09,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (121.09,165.04) rectangle (124.49,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (124.49,165.04) rectangle (127.89,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (127.89,165.04) rectangle (131.29,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (131.29,165.04) rectangle (134.68,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (134.68,165.04) rectangle (138.08,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (138.08,165.04) rectangle (141.48,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (141.48,165.04) rectangle (144.88,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (144.88,165.04) rectangle (148.28,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (148.28,165.04) rectangle (151.67,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (151.67,165.04) rectangle (155.07,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (155.07,165.04) rectangle (158.47,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (158.47,165.04) rectangle (161.87,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (161.87,165.04) rectangle (165.27,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (165.27,165.04) rectangle (168.66,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (168.66,165.04) rectangle (172.06,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (172.06,165.04) rectangle (175.46,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (175.46,165.04) rectangle (178.86,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (178.86,165.04) rectangle (182.26,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (182.26,165.04) rectangle (185.65,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (185.65,165.04) rectangle (189.05,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (189.05,165.04) rectangle (192.45,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (192.45,165.04) rectangle (195.85,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (195.85,165.04) rectangle (199.25,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (199.25,165.04) rectangle (202.64,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (202.64,165.04) rectangle (206.04,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (206.04,165.04) rectangle (209.44,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (209.44,165.04) rectangle (212.84,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (212.84,165.04) rectangle (216.24,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (216.24,165.04) rectangle (219.64,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (219.64,165.04) rectangle (223.03,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (223.03,165.04) rectangle (226.43,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (226.43,165.04) rectangle (229.83,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (229.83,165.04) rectangle (233.23,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (233.23,165.04) rectangle (236.63,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (236.63,165.04) rectangle (240.02,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (240.02,165.04) rectangle (243.42,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (243.42,165.04) rectangle (246.82,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (246.82,165.04) rectangle (250.22,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (250.22,165.04) rectangle (253.62,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (253.62,165.04) rectangle (257.01,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (257.01,165.04) rectangle (260.41,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (260.41,165.04) rectangle (263.81,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (263.81,165.04) rectangle (267.21,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (267.21,165.04) rectangle (270.61,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (270.61,165.04) rectangle (274.00,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (274.00,165.04) rectangle (277.40,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (277.40,165.04) rectangle (280.80,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (280.80,165.04) rectangle (284.20,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (284.20,165.04) rectangle (287.60,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (287.60,165.04) rectangle (290.99,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (290.99,165.04) rectangle (294.39,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (294.39,165.04) rectangle (297.79,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (297.79,165.04) rectangle (301.19,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (301.19,165.04) rectangle (304.59,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (304.59,165.04) rectangle (307.98,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (307.98,165.04) rectangle (311.38,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (311.38,165.04) rectangle (314.78,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (314.78,165.04) rectangle (318.18,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (318.18,165.04) rectangle (321.58,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (321.58,165.04) rectangle (324.97,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (324.97,165.04) rectangle (328.37,168.44);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (328.37,165.04) rectangle (331.77,168.44);
\definecolor{fillColor}{RGB}{54,100,139}

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 29.34,168.44) rectangle ( 32.74,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 32.74,168.44) rectangle ( 36.14,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 36.14,168.44) rectangle ( 39.54,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 39.54,168.44) rectangle ( 42.94,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 42.94,168.44) rectangle ( 46.33,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 46.33,168.44) rectangle ( 49.73,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 49.73,168.44) rectangle ( 53.13,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 53.13,168.44) rectangle ( 56.53,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 56.53,168.44) rectangle ( 59.93,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 59.93,168.44) rectangle ( 63.32,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 63.32,168.44) rectangle ( 66.72,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 66.72,168.44) rectangle ( 70.12,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 70.12,168.44) rectangle ( 73.52,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 73.52,168.44) rectangle ( 76.92,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 76.92,168.44) rectangle ( 80.32,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 80.32,168.44) rectangle ( 83.71,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 83.71,168.44) rectangle ( 87.11,171.83);
\definecolor{fillColor}{RGB}{190,190,190}

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 87.11,168.44) rectangle ( 90.51,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 90.51,168.44) rectangle ( 93.91,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 93.91,168.44) rectangle ( 97.31,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 97.31,168.44) rectangle (100.70,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (100.70,168.44) rectangle (104.10,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (104.10,168.44) rectangle (107.50,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (107.50,168.44) rectangle (110.90,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (110.90,168.44) rectangle (114.30,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (114.30,168.44) rectangle (117.69,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (117.69,168.44) rectangle (121.09,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (121.09,168.44) rectangle (124.49,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (124.49,168.44) rectangle (127.89,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (127.89,168.44) rectangle (131.29,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (131.29,168.44) rectangle (134.68,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (134.68,168.44) rectangle (138.08,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (138.08,168.44) rectangle (141.48,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (141.48,168.44) rectangle (144.88,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (144.88,168.44) rectangle (148.28,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (148.28,168.44) rectangle (151.67,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (151.67,168.44) rectangle (155.07,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (155.07,168.44) rectangle (158.47,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (158.47,168.44) rectangle (161.87,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (161.87,168.44) rectangle (165.27,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (165.27,168.44) rectangle (168.66,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (168.66,168.44) rectangle (172.06,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (172.06,168.44) rectangle (175.46,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (175.46,168.44) rectangle (178.86,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (178.86,168.44) rectangle (182.26,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (182.26,168.44) rectangle (185.65,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (185.65,168.44) rectangle (189.05,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (189.05,168.44) rectangle (192.45,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (192.45,168.44) rectangle (195.85,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (195.85,168.44) rectangle (199.25,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (199.25,168.44) rectangle (202.64,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (202.64,168.44) rectangle (206.04,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (206.04,168.44) rectangle (209.44,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (209.44,168.44) rectangle (212.84,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (212.84,168.44) rectangle (216.24,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (216.24,168.44) rectangle (219.64,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (219.64,168.44) rectangle (223.03,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (223.03,168.44) rectangle (226.43,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (226.43,168.44) rectangle (229.83,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (229.83,168.44) rectangle (233.23,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (233.23,168.44) rectangle (236.63,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (236.63,168.44) rectangle (240.02,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (240.02,168.44) rectangle (243.42,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (243.42,168.44) rectangle (246.82,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (246.82,168.44) rectangle (250.22,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (250.22,168.44) rectangle (253.62,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (253.62,168.44) rectangle (257.01,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (257.01,168.44) rectangle (260.41,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (260.41,168.44) rectangle (263.81,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (263.81,168.44) rectangle (267.21,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (267.21,168.44) rectangle (270.61,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (270.61,168.44) rectangle (274.00,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (274.00,168.44) rectangle (277.40,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (277.40,168.44) rectangle (280.80,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (280.80,168.44) rectangle (284.20,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (284.20,168.44) rectangle (287.60,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (287.60,168.44) rectangle (290.99,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (290.99,168.44) rectangle (294.39,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (294.39,168.44) rectangle (297.79,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (297.79,168.44) rectangle (301.19,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (301.19,168.44) rectangle (304.59,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (304.59,168.44) rectangle (307.98,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (307.98,168.44) rectangle (311.38,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (311.38,168.44) rectangle (314.78,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (314.78,168.44) rectangle (318.18,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (318.18,168.44) rectangle (321.58,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (321.58,168.44) rectangle (324.97,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (324.97,168.44) rectangle (328.37,171.83);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (328.37,168.44) rectangle (331.77,171.83);
\definecolor{fillColor}{RGB}{54,100,139}

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 29.34,171.83) rectangle ( 32.74,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 32.74,171.83) rectangle ( 36.14,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 36.14,171.83) rectangle ( 39.54,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 39.54,171.83) rectangle ( 42.94,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 42.94,171.83) rectangle ( 46.33,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 46.33,171.83) rectangle ( 49.73,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 49.73,171.83) rectangle ( 53.13,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 53.13,171.83) rectangle ( 56.53,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 56.53,171.83) rectangle ( 59.93,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 59.93,171.83) rectangle ( 63.32,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 63.32,171.83) rectangle ( 66.72,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 66.72,171.83) rectangle ( 70.12,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 70.12,171.83) rectangle ( 73.52,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 73.52,171.83) rectangle ( 76.92,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 76.92,171.83) rectangle ( 80.32,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 80.32,171.83) rectangle ( 83.71,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 83.71,171.83) rectangle ( 87.11,175.23);
\definecolor{fillColor}{RGB}{190,190,190}

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 87.11,171.83) rectangle ( 90.51,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 90.51,171.83) rectangle ( 93.91,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 93.91,171.83) rectangle ( 97.31,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 97.31,171.83) rectangle (100.70,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (100.70,171.83) rectangle (104.10,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (104.10,171.83) rectangle (107.50,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (107.50,171.83) rectangle (110.90,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (110.90,171.83) rectangle (114.30,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (114.30,171.83) rectangle (117.69,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (117.69,171.83) rectangle (121.09,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (121.09,171.83) rectangle (124.49,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (124.49,171.83) rectangle (127.89,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (127.89,171.83) rectangle (131.29,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (131.29,171.83) rectangle (134.68,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (134.68,171.83) rectangle (138.08,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (138.08,171.83) rectangle (141.48,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (141.48,171.83) rectangle (144.88,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (144.88,171.83) rectangle (148.28,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (148.28,171.83) rectangle (151.67,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (151.67,171.83) rectangle (155.07,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (155.07,171.83) rectangle (158.47,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (158.47,171.83) rectangle (161.87,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (161.87,171.83) rectangle (165.27,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (165.27,171.83) rectangle (168.66,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (168.66,171.83) rectangle (172.06,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (172.06,171.83) rectangle (175.46,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (175.46,171.83) rectangle (178.86,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (178.86,171.83) rectangle (182.26,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (182.26,171.83) rectangle (185.65,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (185.65,171.83) rectangle (189.05,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (189.05,171.83) rectangle (192.45,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (192.45,171.83) rectangle (195.85,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (195.85,171.83) rectangle (199.25,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (199.25,171.83) rectangle (202.64,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (202.64,171.83) rectangle (206.04,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (206.04,171.83) rectangle (209.44,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (209.44,171.83) rectangle (212.84,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (212.84,171.83) rectangle (216.24,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (216.24,171.83) rectangle (219.64,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (219.64,171.83) rectangle (223.03,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (223.03,171.83) rectangle (226.43,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (226.43,171.83) rectangle (229.83,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (229.83,171.83) rectangle (233.23,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (233.23,171.83) rectangle (236.63,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (236.63,171.83) rectangle (240.02,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (240.02,171.83) rectangle (243.42,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (243.42,171.83) rectangle (246.82,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (246.82,171.83) rectangle (250.22,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (250.22,171.83) rectangle (253.62,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (253.62,171.83) rectangle (257.01,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (257.01,171.83) rectangle (260.41,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (260.41,171.83) rectangle (263.81,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (263.81,171.83) rectangle (267.21,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (267.21,171.83) rectangle (270.61,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (270.61,171.83) rectangle (274.00,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (274.00,171.83) rectangle (277.40,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (277.40,171.83) rectangle (280.80,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (280.80,171.83) rectangle (284.20,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (284.20,171.83) rectangle (287.60,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (287.60,171.83) rectangle (290.99,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (290.99,171.83) rectangle (294.39,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (294.39,171.83) rectangle (297.79,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (297.79,171.83) rectangle (301.19,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (301.19,171.83) rectangle (304.59,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (304.59,171.83) rectangle (307.98,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (307.98,171.83) rectangle (311.38,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (311.38,171.83) rectangle (314.78,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (314.78,171.83) rectangle (318.18,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (318.18,171.83) rectangle (321.58,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (321.58,171.83) rectangle (324.97,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (324.97,171.83) rectangle (328.37,175.23);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (328.37,171.83) rectangle (331.77,175.23);
\definecolor{fillColor}{RGB}{54,100,139}

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 29.34,175.23) rectangle ( 32.74,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 32.74,175.23) rectangle ( 36.14,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 36.14,175.23) rectangle ( 39.54,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 39.54,175.23) rectangle ( 42.94,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 42.94,175.23) rectangle ( 46.33,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 46.33,175.23) rectangle ( 49.73,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 49.73,175.23) rectangle ( 53.13,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 53.13,175.23) rectangle ( 56.53,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 56.53,175.23) rectangle ( 59.93,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 59.93,175.23) rectangle ( 63.32,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 63.32,175.23) rectangle ( 66.72,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 66.72,175.23) rectangle ( 70.12,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 70.12,175.23) rectangle ( 73.52,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 73.52,175.23) rectangle ( 76.92,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 76.92,175.23) rectangle ( 80.32,178.63);
\definecolor{fillColor}{RGB}{190,190,190}

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 80.32,175.23) rectangle ( 83.71,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 83.71,175.23) rectangle ( 87.11,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 87.11,175.23) rectangle ( 90.51,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 90.51,175.23) rectangle ( 93.91,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 93.91,175.23) rectangle ( 97.31,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 97.31,175.23) rectangle (100.70,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (100.70,175.23) rectangle (104.10,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (104.10,175.23) rectangle (107.50,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (107.50,175.23) rectangle (110.90,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (110.90,175.23) rectangle (114.30,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (114.30,175.23) rectangle (117.69,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (117.69,175.23) rectangle (121.09,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (121.09,175.23) rectangle (124.49,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (124.49,175.23) rectangle (127.89,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (127.89,175.23) rectangle (131.29,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (131.29,175.23) rectangle (134.68,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (134.68,175.23) rectangle (138.08,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (138.08,175.23) rectangle (141.48,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (141.48,175.23) rectangle (144.88,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (144.88,175.23) rectangle (148.28,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (148.28,175.23) rectangle (151.67,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (151.67,175.23) rectangle (155.07,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (155.07,175.23) rectangle (158.47,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (158.47,175.23) rectangle (161.87,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (161.87,175.23) rectangle (165.27,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (165.27,175.23) rectangle (168.66,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (168.66,175.23) rectangle (172.06,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (172.06,175.23) rectangle (175.46,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (175.46,175.23) rectangle (178.86,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (178.86,175.23) rectangle (182.26,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (182.26,175.23) rectangle (185.65,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (185.65,175.23) rectangle (189.05,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (189.05,175.23) rectangle (192.45,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (192.45,175.23) rectangle (195.85,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (195.85,175.23) rectangle (199.25,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (199.25,175.23) rectangle (202.64,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (202.64,175.23) rectangle (206.04,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (206.04,175.23) rectangle (209.44,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (209.44,175.23) rectangle (212.84,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (212.84,175.23) rectangle (216.24,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (216.24,175.23) rectangle (219.64,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (219.64,175.23) rectangle (223.03,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (223.03,175.23) rectangle (226.43,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (226.43,175.23) rectangle (229.83,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (229.83,175.23) rectangle (233.23,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (233.23,175.23) rectangle (236.63,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (236.63,175.23) rectangle (240.02,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (240.02,175.23) rectangle (243.42,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (243.42,175.23) rectangle (246.82,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (246.82,175.23) rectangle (250.22,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (250.22,175.23) rectangle (253.62,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (253.62,175.23) rectangle (257.01,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (257.01,175.23) rectangle (260.41,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (260.41,175.23) rectangle (263.81,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (263.81,175.23) rectangle (267.21,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (267.21,175.23) rectangle (270.61,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (270.61,175.23) rectangle (274.00,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (274.00,175.23) rectangle (277.40,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (277.40,175.23) rectangle (280.80,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (280.80,175.23) rectangle (284.20,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (284.20,175.23) rectangle (287.60,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (287.60,175.23) rectangle (290.99,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (290.99,175.23) rectangle (294.39,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (294.39,175.23) rectangle (297.79,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (297.79,175.23) rectangle (301.19,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (301.19,175.23) rectangle (304.59,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (304.59,175.23) rectangle (307.98,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (307.98,175.23) rectangle (311.38,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (311.38,175.23) rectangle (314.78,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (314.78,175.23) rectangle (318.18,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (318.18,175.23) rectangle (321.58,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (321.58,175.23) rectangle (324.97,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (324.97,175.23) rectangle (328.37,178.63);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (328.37,175.23) rectangle (331.77,178.63);
\definecolor{fillColor}{RGB}{54,100,139}

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 29.34,178.63) rectangle ( 32.74,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 32.74,178.63) rectangle ( 36.14,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 36.14,178.63) rectangle ( 39.54,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 39.54,178.63) rectangle ( 42.94,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 42.94,178.63) rectangle ( 46.33,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 46.33,178.63) rectangle ( 49.73,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 49.73,178.63) rectangle ( 53.13,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 53.13,178.63) rectangle ( 56.53,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 56.53,178.63) rectangle ( 59.93,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 59.93,178.63) rectangle ( 63.32,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 63.32,178.63) rectangle ( 66.72,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 66.72,178.63) rectangle ( 70.12,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 70.12,178.63) rectangle ( 73.52,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 73.52,178.63) rectangle ( 76.92,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 76.92,178.63) rectangle ( 80.32,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 80.32,178.63) rectangle ( 83.71,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 83.71,178.63) rectangle ( 87.11,182.03);
\definecolor{fillColor}{RGB}{190,190,190}

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 87.11,178.63) rectangle ( 90.51,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 90.51,178.63) rectangle ( 93.91,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 93.91,178.63) rectangle ( 97.31,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 97.31,178.63) rectangle (100.70,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (100.70,178.63) rectangle (104.10,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (104.10,178.63) rectangle (107.50,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (107.50,178.63) rectangle (110.90,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (110.90,178.63) rectangle (114.30,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (114.30,178.63) rectangle (117.69,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (117.69,178.63) rectangle (121.09,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (121.09,178.63) rectangle (124.49,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (124.49,178.63) rectangle (127.89,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (127.89,178.63) rectangle (131.29,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (131.29,178.63) rectangle (134.68,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (134.68,178.63) rectangle (138.08,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (138.08,178.63) rectangle (141.48,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (141.48,178.63) rectangle (144.88,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (144.88,178.63) rectangle (148.28,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (148.28,178.63) rectangle (151.67,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (151.67,178.63) rectangle (155.07,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (155.07,178.63) rectangle (158.47,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (158.47,178.63) rectangle (161.87,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (161.87,178.63) rectangle (165.27,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (165.27,178.63) rectangle (168.66,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (168.66,178.63) rectangle (172.06,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (172.06,178.63) rectangle (175.46,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (175.46,178.63) rectangle (178.86,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (178.86,178.63) rectangle (182.26,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (182.26,178.63) rectangle (185.65,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (185.65,178.63) rectangle (189.05,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (189.05,178.63) rectangle (192.45,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (192.45,178.63) rectangle (195.85,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (195.85,178.63) rectangle (199.25,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (199.25,178.63) rectangle (202.64,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (202.64,178.63) rectangle (206.04,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (206.04,178.63) rectangle (209.44,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (209.44,178.63) rectangle (212.84,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (212.84,178.63) rectangle (216.24,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (216.24,178.63) rectangle (219.64,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (219.64,178.63) rectangle (223.03,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (223.03,178.63) rectangle (226.43,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (226.43,178.63) rectangle (229.83,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (229.83,178.63) rectangle (233.23,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (233.23,178.63) rectangle (236.63,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (236.63,178.63) rectangle (240.02,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (240.02,178.63) rectangle (243.42,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (243.42,178.63) rectangle (246.82,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (246.82,178.63) rectangle (250.22,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (250.22,178.63) rectangle (253.62,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (253.62,178.63) rectangle (257.01,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (257.01,178.63) rectangle (260.41,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (260.41,178.63) rectangle (263.81,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (263.81,178.63) rectangle (267.21,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (267.21,178.63) rectangle (270.61,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (270.61,178.63) rectangle (274.00,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (274.00,178.63) rectangle (277.40,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (277.40,178.63) rectangle (280.80,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (280.80,178.63) rectangle (284.20,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (284.20,178.63) rectangle (287.60,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (287.60,178.63) rectangle (290.99,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (290.99,178.63) rectangle (294.39,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (294.39,178.63) rectangle (297.79,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (297.79,178.63) rectangle (301.19,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (301.19,178.63) rectangle (304.59,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (304.59,178.63) rectangle (307.98,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (307.98,178.63) rectangle (311.38,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (311.38,178.63) rectangle (314.78,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (314.78,178.63) rectangle (318.18,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (318.18,178.63) rectangle (321.58,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (321.58,178.63) rectangle (324.97,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (324.97,178.63) rectangle (328.37,182.03);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (328.37,178.63) rectangle (331.77,182.03);
\definecolor{fillColor}{RGB}{54,100,139}

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 29.34,182.03) rectangle ( 32.74,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 32.74,182.03) rectangle ( 36.14,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 36.14,182.03) rectangle ( 39.54,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 39.54,182.03) rectangle ( 42.94,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 42.94,182.03) rectangle ( 46.33,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 46.33,182.03) rectangle ( 49.73,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 49.73,182.03) rectangle ( 53.13,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 53.13,182.03) rectangle ( 56.53,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 56.53,182.03) rectangle ( 59.93,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 59.93,182.03) rectangle ( 63.32,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 63.32,182.03) rectangle ( 66.72,185.43);
\definecolor{fillColor}{RGB}{190,190,190}

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 66.72,182.03) rectangle ( 70.12,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 70.12,182.03) rectangle ( 73.52,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 73.52,182.03) rectangle ( 76.92,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 76.92,182.03) rectangle ( 80.32,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 80.32,182.03) rectangle ( 83.71,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 83.71,182.03) rectangle ( 87.11,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 87.11,182.03) rectangle ( 90.51,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 90.51,182.03) rectangle ( 93.91,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 93.91,182.03) rectangle ( 97.31,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 97.31,182.03) rectangle (100.70,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (100.70,182.03) rectangle (104.10,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (104.10,182.03) rectangle (107.50,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (107.50,182.03) rectangle (110.90,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (110.90,182.03) rectangle (114.30,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (114.30,182.03) rectangle (117.69,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (117.69,182.03) rectangle (121.09,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (121.09,182.03) rectangle (124.49,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (124.49,182.03) rectangle (127.89,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (127.89,182.03) rectangle (131.29,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (131.29,182.03) rectangle (134.68,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (134.68,182.03) rectangle (138.08,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (138.08,182.03) rectangle (141.48,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (141.48,182.03) rectangle (144.88,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (144.88,182.03) rectangle (148.28,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (148.28,182.03) rectangle (151.67,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (151.67,182.03) rectangle (155.07,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (155.07,182.03) rectangle (158.47,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (158.47,182.03) rectangle (161.87,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (161.87,182.03) rectangle (165.27,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (165.27,182.03) rectangle (168.66,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (168.66,182.03) rectangle (172.06,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (172.06,182.03) rectangle (175.46,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (175.46,182.03) rectangle (178.86,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (178.86,182.03) rectangle (182.26,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (182.26,182.03) rectangle (185.65,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (185.65,182.03) rectangle (189.05,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (189.05,182.03) rectangle (192.45,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (192.45,182.03) rectangle (195.85,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (195.85,182.03) rectangle (199.25,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (199.25,182.03) rectangle (202.64,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (202.64,182.03) rectangle (206.04,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (206.04,182.03) rectangle (209.44,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (209.44,182.03) rectangle (212.84,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (212.84,182.03) rectangle (216.24,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (216.24,182.03) rectangle (219.64,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (219.64,182.03) rectangle (223.03,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (223.03,182.03) rectangle (226.43,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (226.43,182.03) rectangle (229.83,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (229.83,182.03) rectangle (233.23,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (233.23,182.03) rectangle (236.63,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (236.63,182.03) rectangle (240.02,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (240.02,182.03) rectangle (243.42,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (243.42,182.03) rectangle (246.82,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (246.82,182.03) rectangle (250.22,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (250.22,182.03) rectangle (253.62,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (253.62,182.03) rectangle (257.01,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (257.01,182.03) rectangle (260.41,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (260.41,182.03) rectangle (263.81,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (263.81,182.03) rectangle (267.21,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (267.21,182.03) rectangle (270.61,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (270.61,182.03) rectangle (274.00,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (274.00,182.03) rectangle (277.40,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (277.40,182.03) rectangle (280.80,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (280.80,182.03) rectangle (284.20,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (284.20,182.03) rectangle (287.60,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (287.60,182.03) rectangle (290.99,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (290.99,182.03) rectangle (294.39,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (294.39,182.03) rectangle (297.79,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (297.79,182.03) rectangle (301.19,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (301.19,182.03) rectangle (304.59,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (304.59,182.03) rectangle (307.98,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (307.98,182.03) rectangle (311.38,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (311.38,182.03) rectangle (314.78,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (314.78,182.03) rectangle (318.18,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (318.18,182.03) rectangle (321.58,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (321.58,182.03) rectangle (324.97,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (324.97,182.03) rectangle (328.37,185.43);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (328.37,182.03) rectangle (331.77,185.43);
\definecolor{fillColor}{RGB}{54,100,139}

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 29.34,185.43) rectangle ( 32.74,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 32.74,185.43) rectangle ( 36.14,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 36.14,185.43) rectangle ( 39.54,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 39.54,185.43) rectangle ( 42.94,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 42.94,185.43) rectangle ( 46.33,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 46.33,185.43) rectangle ( 49.73,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 49.73,185.43) rectangle ( 53.13,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 53.13,185.43) rectangle ( 56.53,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 56.53,185.43) rectangle ( 59.93,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 59.93,185.43) rectangle ( 63.32,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 63.32,185.43) rectangle ( 66.72,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 66.72,185.43) rectangle ( 70.12,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 70.12,185.43) rectangle ( 73.52,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 73.52,185.43) rectangle ( 76.92,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 76.92,185.43) rectangle ( 80.32,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 80.32,185.43) rectangle ( 83.71,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 83.71,185.43) rectangle ( 87.11,188.82);
\definecolor{fillColor}{RGB}{190,190,190}

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 87.11,185.43) rectangle ( 90.51,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 90.51,185.43) rectangle ( 93.91,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 93.91,185.43) rectangle ( 97.31,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] ( 97.31,185.43) rectangle (100.70,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (100.70,185.43) rectangle (104.10,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (104.10,185.43) rectangle (107.50,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (107.50,185.43) rectangle (110.90,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (110.90,185.43) rectangle (114.30,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (114.30,185.43) rectangle (117.69,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (117.69,185.43) rectangle (121.09,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (121.09,185.43) rectangle (124.49,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (124.49,185.43) rectangle (127.89,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (127.89,185.43) rectangle (131.29,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (131.29,185.43) rectangle (134.68,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (134.68,185.43) rectangle (138.08,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (138.08,185.43) rectangle (141.48,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (141.48,185.43) rectangle (144.88,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (144.88,185.43) rectangle (148.28,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (148.28,185.43) rectangle (151.67,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (151.67,185.43) rectangle (155.07,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (155.07,185.43) rectangle (158.47,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (158.47,185.43) rectangle (161.87,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (161.87,185.43) rectangle (165.27,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (165.27,185.43) rectangle (168.66,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (168.66,185.43) rectangle (172.06,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (172.06,185.43) rectangle (175.46,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (175.46,185.43) rectangle (178.86,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (178.86,185.43) rectangle (182.26,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (182.26,185.43) rectangle (185.65,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (185.65,185.43) rectangle (189.05,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (189.05,185.43) rectangle (192.45,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (192.45,185.43) rectangle (195.85,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (195.85,185.43) rectangle (199.25,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (199.25,185.43) rectangle (202.64,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (202.64,185.43) rectangle (206.04,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (206.04,185.43) rectangle (209.44,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (209.44,185.43) rectangle (212.84,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (212.84,185.43) rectangle (216.24,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (216.24,185.43) rectangle (219.64,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (219.64,185.43) rectangle (223.03,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (223.03,185.43) rectangle (226.43,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (226.43,185.43) rectangle (229.83,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (229.83,185.43) rectangle (233.23,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (233.23,185.43) rectangle (236.63,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (236.63,185.43) rectangle (240.02,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (240.02,185.43) rectangle (243.42,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (243.42,185.43) rectangle (246.82,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (246.82,185.43) rectangle (250.22,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (250.22,185.43) rectangle (253.62,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (253.62,185.43) rectangle (257.01,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (257.01,185.43) rectangle (260.41,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (260.41,185.43) rectangle (263.81,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (263.81,185.43) rectangle (267.21,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (267.21,185.43) rectangle (270.61,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (270.61,185.43) rectangle (274.00,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (274.00,185.43) rectangle (277.40,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (277.40,185.43) rectangle (280.80,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (280.80,185.43) rectangle (284.20,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (284.20,185.43) rectangle (287.60,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (287.60,185.43) rectangle (290.99,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (290.99,185.43) rectangle (294.39,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (294.39,185.43) rectangle (297.79,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (297.79,185.43) rectangle (301.19,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (301.19,185.43) rectangle (304.59,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (304.59,185.43) rectangle (307.98,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (307.98,185.43) rectangle (311.38,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (311.38,185.43) rectangle (314.78,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (314.78,185.43) rectangle (318.18,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (318.18,185.43) rectangle (321.58,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (321.58,185.43) rectangle (324.97,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (324.97,185.43) rectangle (328.37,188.82);

\path[draw=drawColor,line width= 0.1pt,line cap=rect,fill=fillColor] (328.37,185.43) rectangle (331.77,188.82);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (339.67,289.08);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 21.90,120.08) {1};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 21.90,133.67) {5};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 21.90,150.66) {10};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 21.90,167.66) {15};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 21.90,184.65) {20};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (339.67,289.08);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 31.04,108.46) {1};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 61.63,108.46) {10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 95.61,108.46) {20};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (129.59,108.46) {30};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (163.57,108.46) {40};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (197.55,108.46) {50};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (231.53,108.46) {60};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (265.51,108.46) {70};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (299.49,108.46) {80};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (333.47,108.46) {90};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (339.67,289.08);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (180.56, 98.61) {Step};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (339.67,289.08);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 10.70,154.84) {Predictor};
\end{scope}
\end{tikzpicture}

\end{document}

### 2021-05-12 paper/figures/simulateddata-timings.tex
Update results

% Created by tikzDevice version 0.12.3.1 on 2021-05-11 11:28:06
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

\usepackage[active,tightpage,psfixbb]{preview}

\PreviewEnvironment{pgfpicture}

\setlength\PreviewBorder{0pt}
\begin{document}

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (325.21,144.54);
\begin{scope}
\path[clip] ( 27.95, 25.11) rectangle (245.47,140.04);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 27.95, 25.15) --
	(245.47, 25.15);

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 27.95, 53.21) --
	(245.47, 53.21);

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 27.95, 81.27) --
	(245.47, 81.27);

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 27.95,109.33) --
	(245.47,109.33);

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 27.95,137.39) --
	(245.47,137.39);

\path[draw=drawColor,line width= 0.5pt,line join=round] ( 27.95, 39.18) --
	(245.47, 39.18);

\path[draw=drawColor,line width= 0.5pt,line join=round] ( 27.95, 67.24) --
	(245.47, 67.24);

\path[draw=drawColor,line width= 0.5pt,line join=round] ( 27.95, 95.30) --
	(245.47, 95.30);

\path[draw=drawColor,line width= 0.5pt,line join=round] ( 27.95,123.36) --
	(245.47,123.36);

\path[draw=drawColor,line width= 0.5pt,line join=round] ( 68.73, 25.11) --
	( 68.73,140.04);

\path[draw=drawColor,line width= 0.5pt,line join=round] (136.71, 25.11) --
	(136.71,140.04);

\path[draw=drawColor,line width= 0.5pt,line join=round] (204.68, 25.11) --
	(204.68,140.04);
\definecolor{drawColor}{RGB}{51,51,51}
\definecolor{fillColor}{RGB}{51,51,51}

\path[draw=drawColor,draw opacity=0.70,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.70] ( 55.99, 35.59) circle (  1.96);

\path[draw=drawColor,draw opacity=0.70,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.70] ( 55.99, 30.33) circle (  1.96);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 55.99, 69.35) -- ( 55.99, 81.87);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 55.99, 56.03) -- ( 55.99, 36.07);
\definecolor{fillColor}{gray}{0.60}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 44.52, 69.35) --
	( 44.52, 56.03) --
	( 67.46, 56.03) --
	( 67.46, 69.35) --
	( 44.52, 69.35) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 44.52, 64.82) -- ( 67.46, 64.82);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 81.48,100.56) -- ( 81.48,134.82);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 81.48, 75.58) -- ( 81.48, 47.67);
\definecolor{fillColor}{RGB}{230,159,0}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 70.01,100.56) --
	( 70.01, 75.58) --
	( 92.95, 75.58) --
	( 92.95,100.56) --
	( 70.01,100.56) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 70.01, 87.94) -- ( 92.95, 87.94);
\definecolor{drawColor}{RGB}{51,51,51}
\definecolor{fillColor}{RGB}{51,51,51}

\path[draw=drawColor,draw opacity=0.70,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.70] (123.96, 40.25) circle (  1.96);

\path[draw=drawColor,draw opacity=0.70,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.70] (123.96, 48.90) circle (  1.96);

\path[draw=drawColor,draw opacity=0.70,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.70] (123.96, 46.58) circle (  1.96);

\path[draw=drawColor,draw opacity=0.70,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.70] (123.96, 43.27) circle (  1.96);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] (123.96, 73.30) -- (123.96, 85.57);

\path[draw=drawColor,line width= 0.6pt,line join=round] (123.96, 63.82) -- (123.96, 55.13);
\definecolor{fillColor}{gray}{0.60}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (112.49, 73.30) --
	(112.49, 63.82) --
	(135.43, 63.82) --
	(135.43, 73.30) --
	(112.49, 73.30) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (112.49, 68.49) -- (135.43, 68.49);

\path[draw=drawColor,line width= 0.6pt,line join=round] (149.45,106.12) -- (149.45,122.35);

\path[draw=drawColor,line width= 0.6pt,line join=round] (149.45, 87.88) -- (149.45, 62.14);
\definecolor{fillColor}{RGB}{230,159,0}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (137.98,106.12) --
	(137.98, 87.88) --
	(160.92, 87.88) --
	(160.92,106.12) --
	(137.98,106.12) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (137.98, 99.28) -- (160.92, 99.28);
\definecolor{drawColor}{RGB}{51,51,51}
\definecolor{fillColor}{RGB}{51,51,51}

\path[draw=drawColor,draw opacity=0.70,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.70] (191.94, 89.45) circle (  1.96);

\path[draw=drawColor,draw opacity=0.70,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.70] (191.94, 90.50) circle (  1.96);

\path[draw=drawColor,draw opacity=0.70,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.70] (191.94, 53.69) circle (  1.96);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] (191.94, 73.09) -- (191.94, 80.70);

\path[draw=drawColor,line width= 0.6pt,line join=round] (191.94, 67.49) -- (191.94, 60.23);
\definecolor{fillColor}{gray}{0.60}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (180.47, 73.09) --
	(180.47, 67.49) --
	(203.41, 67.49) --
	(203.41, 73.09) --
	(180.47, 73.09) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (180.47, 71.06) -- (203.41, 71.06);
\definecolor{drawColor}{RGB}{51,51,51}
\definecolor{fillColor}{RGB}{51,51,51}

\path[draw=drawColor,draw opacity=0.70,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.70] (217.43,132.84) circle (  1.96);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] (217.43,114.32) -- (217.43,122.03);

\path[draw=drawColor,line width= 0.6pt,line join=round] (217.43,103.13) -- (217.43, 86.49);
\definecolor{fillColor}{RGB}{230,159,0}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (205.96,114.32) --
	(205.96,103.13) --
	(228.90,103.13) --
	(228.90,114.32) --
	(205.96,114.32) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (205.96,109.09) -- (228.90,109.09);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,144.54);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 23.90, 36.70) {1.5};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 23.90, 64.76) {2.0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 23.90, 92.82) {2.5};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 23.90,120.88) {3.0};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,144.54);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 68.73, 16.10) {0.1};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (136.71, 16.10) {1};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (204.68, 16.10) {6};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,144.54);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (136.71,  6.25) {Signal-to-Noise Ratio};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,144.54);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 10.70, 82.57) {Time (s)};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,144.54);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (266.20, 81.77) --
	(266.20, 83.94);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (266.20, 91.16) --
	(266.20, 93.33);
\definecolor{fillColor}{gray}{0.60}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (260.78, 83.94) rectangle (271.62, 91.16);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (260.78, 87.55) --
	(271.62, 87.55);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,144.54);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (266.20, 67.31) --
	(266.20, 69.48);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (266.20, 76.71) --
	(266.20, 78.88);
\definecolor{fillColor}{RGB}{230,159,0}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (260.78, 69.48) rectangle (271.62, 76.71);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (260.78, 73.10) --
	(271.62, 73.10);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,144.54);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at (277.92, 85.07) {Look-Ahead};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,144.54);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at (277.92, 70.62) {Standard};
\end{scope}
\end{tikzpicture}

\end{document}

### 2021-05-12 src/RcppExports.cpp
Update c++ exports

@@ -7,8 +7,8 @@
 using namespace Rcpp;
 
 // lassoPathDense
-Rcpp::List lassoPathDense(arma::mat X, arma::vec y, const bool standardize, const std::string screening_type, const arma::uword path_length, const arma::uword maxit, const double tol_infeas, const double tol_gap, const bool force_kkt_check, const arma::uword verbosity);
-RcppExport SEXP _LookAheadScreening_lassoPathDense(SEXP XSEXP, SEXP ySEXP, SEXP standardizeSEXP, SEXP screening_typeSEXP, SEXP path_lengthSEXP, SEXP maxitSEXP, SEXP tol_infeasSEXP, SEXP tol_gapSEXP, SEXP force_kkt_checkSEXP, SEXP verbositySEXP) {
+Rcpp::List lassoPathDense(arma::mat X, arma::vec y, const bool standardize, const std::string screening_type, const arma::uword path_length, const arma::uword maxit, const double tol_infeas, const double tol_gap, const bool check_kkt, const arma::uword verbosity);
+RcppExport SEXP _LookAheadScreening_lassoPathDense(SEXP XSEXP, SEXP ySEXP, SEXP standardizeSEXP, SEXP screening_typeSEXP, SEXP path_lengthSEXP, SEXP maxitSEXP, SEXP tol_infeasSEXP, SEXP tol_gapSEXP, SEXP check_kktSEXP, SEXP verbositySEXP) {
 BEGIN_RCPP
     Rcpp::RObject rcpp_result_gen;
     Rcpp::RNGScope rcpp_rngScope_gen;
@@ -20,15 +20,15 @@ BEGIN_RCPP
     Rcpp::traits::input_parameter< const arma::uword >::type maxit(maxitSEXP);
     Rcpp::traits::input_parameter< const double >::type tol_infeas(tol_infeasSEXP);
     Rcpp::traits::input_parameter< const double >::type tol_gap(tol_gapSEXP);
-    Rcpp::traits::input_parameter< const bool >::type force_kkt_check(force_kkt_checkSEXP);
+    Rcpp::traits::input_parameter< const bool >::type check_kkt(check_kktSEXP);
     Rcpp::traits::input_parameter< const arma::uword >::type verbosity(verbositySEXP);
[…]

### 2021-05-12 sim-casestudy.sh
Fix bash script for case study

@@ -1,4 +1,3 @@
-
 #!/bin/sh
 
 #SBATCH -t 8:00:00

### 2021-05-12 tests/testthat/test-screening.R
Fix failing test

@@ -17,7 +17,7 @@ test_that("screening methods work", {
                        y,
                        screening_type = screening_type,
                        verbosity = 0,
-                       force_kkt_check = TRUE)
+                       check_kkt = TRUE)
 
       steps <- 1:min(length(fit$lambda), length(fit_gap$lambda))
       expect_equal(fit_gap$dev[steps], fit$dev[steps],

### 2021-05-12 R/generateDesign.R
Dro unused arugment in documentation

@@ -2,7 +2,6 @@
 #'
 #' @param n Number of observations
 #' @param p Number of predictors
-#' @param family Response type
 #' @param density Density of design matrix
 #' @param rho Correlation between predictors (corresponding to choice in `rho_type`)
 #' @param s Number of signals (nonzero coefficients)
@@ -44,7 +43,7 @@ generateDesign <- function(n,
   }
 
   if (density == 1) {
-    X <- matrix(rnorm(n * p), n)
+    X <- matrix(stats::rnorm(n * p), n)
   } else {
     X <- Matrix::rsparsematrix(n, p, density)
   }

### 2021-05-12 R/lassoPath.R
Use methods namespace

@@ -33,7 +33,7 @@ lassoPath <- function(X,
   p <- ncol(X)
 
   if (sparse) {
-    X <- as(X, "dgCMatrix")
+    X <- methods::as(X, "dgCMatrix")
 
     lassoPathSparse(
       X,

### 2021-05-12 figures/casestudy.R
Fix figure script

@@ -10,7 +10,7 @@ theme_set(theme_minimal(base_size = 9))
 d <- read_rds("results/casestudy-full.rds")
 
 pl <-
-  ggplot(d2, aes(name, rowid, fill = value)) +
+  ggplot(d, aes(name, rowid, fill = value)) +
   geom_tile(show.legend = FALSE, col = "white") +
   scale_fill_manual(values = c("grey", "steelblue4")) +
   coord_fixed() +
@@ -25,4 +25,5 @@ pl
 dev.off()
 renderPdf(file)
 
-d2 <- read_rds("results/casestudy-summary.rds")
+# d2 <- read_rds("results/casestudy-summary.rds")
+# print(d2, n = Inf)

### 2021-05-12 paper/figures/simulateddata-timings.tex
Update results and figures

@@
-% Created by tikzDevice version 0.12.3.1 on 2021-05-11 11:28:06
+% Created by tikzDevice version 0.12.3.1 on 2021-05-12 11:19:34
 % !TEX encoding = UTF-8 Unicode
@@
 
-\path[draw=drawColor,line width= 0.2pt,line join=round] ( 27.95, 25.15) --
-	(245.47, 25.15);
+\path[draw=drawColor,line width= 0.2pt,line join=round] ( 27.95, 25.98) --
+	(245.47, 25.98);
 
-\path[draw=drawColor,line width= 0.2pt,line join=round] ( 27.95, 53.21) --
-	(245.47, 53.21);
+\path[draw=drawColor,line width= 0.2pt,line join=round] ( 27.95, 57.72) --
+	(245.47, 57.72);
 
-\path[draw=drawColor,line width= 0.2pt,line join=round] ( 27.95, 81.27) --
-	(245.47, 81.27);
+\path[draw=drawColor,line width= 0.2pt,line join=round] ( 27.95, 89.47) --
+	(245.47, 89.47);
 
-\path[draw=drawColor,line width= 0.2pt,line join=round] ( 27.95,109.33) --
-	(245.47,109.33);
+\path[draw=drawColor,line width= 0.2pt,line join=round] ( 27.95,121.21) --
+	(245.47,121.21);
 
-\path[draw=drawColor,line width= 0.2pt,line join=round] ( 27.95,137.39) --
-	(245.47,137.39);
+\path[draw=drawColor,line width= 0.5pt,line join=round] ( 27.95, 41.85) --
+	(245.47, 41.85);
 
-\path[draw=drawColor,line width= 0.5pt,line join=round] ( 27.95, 39.18) --
-	(245.47, 39.18);
+\path[draw=drawColor,line width= 0.5pt,line join=round] ( 27.95, 73.59) --
+	(245.47, 73.59);
 
-\path[draw=drawColor,line width= 0.5pt,line join=round] ( 27.95, 67.24) --
-	(245.47, 67.24);
+\path[draw=drawColor,line width= 0.5pt,line join=round] ( 27.95,105.34) --
+	(245.47,105.34);
 
-\path[draw=drawColor,line width= 0.5pt,line join=round] ( 27.95, 95.30) --
-	(245.47, 95.30);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] ( 27.95,123.36) --
-	(245.47,123.36);
+\path[draw=drawColor,line width= 0.5pt,line join=round] ( 27.95,137.08) --
+	(245.47,137.08);
 
@@
 
-\path[draw=drawColor,draw opacity=0.70,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.70] ( 55.99, 35.59) circle (  1.96);
+\path[draw=drawColor,draw opacity=0.70,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.70] ( 55.99, 30.73) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.70,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.70] ( 55.99, 37.51) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.70,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.70] ( 55.99, 31.21) circle (  1.96);
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 55.99, 69.35) -- ( 55.99, 81.87);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 55.99, 67.44) -- ( 55.99, 76.82);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 55.99, 56.03) -- ( 55.99, 36.07);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 55.99, 55.70) -- ( 55.99, 42.49);
 \definecolor{fillColor}{gray}{0.60}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 44.52, 69.35) --
-	( 44.52, 56.03) --
-	( 67.46, 56.03) --
-	( 67.46, 69.35) --
-	( 44.52, 69.35) --
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 44.52, 67.44) --
+	( 44.52, 55.70) --
+	( 67.46, 55.70) --
+	( 67.46, 67.44) --
+	( 44.52, 67.44) --
 	cycle;
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] ( 44.52, 64.82) -- ( 67.46, 64.82);
+\path[draw=drawColor,line width= 1.1pt,line join=round] ( 44.52, 63.76) -- ( 67.46, 63.76);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 81.48,100.56) -- ( 81.48,134.82);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 81.48, 96.61) -- ( 81.48,133.30);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 81.48, 75.58) -- ( 81.48, 47.67);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 81.48, 71.28) -- ( 81.48, 52.00);
 \definecolor{fillColor}{RGB}{230,159,0}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 70.01,100.56) --
-	( 70.01, 75.58) --
-	( 92.95, 75.58) --
-	( 92.95,100.56) --
-	( 70.01,100.56) --
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 70.01, 96.61) --
+	( 70.01, 71.28) --
+	( 92.95, 71.28) --
+	( 92.95, 96.61) --
+	( 70.01, 96.61) --
 	cycle;
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] ( 70.01, 87.94) -- ( 92.95, 87.94);
+\path[draw=drawColor,line width= 1.1pt,line join=round] ( 70.01, 82.83) -- ( 92.95, 82.83);
 \definecolor{drawColor}{RGB}{51,51,51}
@@
 
-\path[draw=drawColor,draw opacity=0.70,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.70] (123.96, 40.25) circle (  1.96);
+\path[draw=drawColor,draw opacity=0.70,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.70] (123.96, 50.12) circle (  1.96);
 
-\path[draw=drawColor,draw opacity=0.70,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.70] (123.96, 48.90) circle (  1.96);
+\path[draw=drawColor,draw opacity=0.70,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.70] (123.96, 43.36) circle (  1.96);
 
-\path[draw=drawColor,draw opacity=0.70,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.70] (123.96, 46.58) circle (  1.96);
+\path[draw=drawColor,draw opacity=0.70,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.70] (123.96, 55.84) circle (  1.96);
 
-\path[draw=drawColor,draw opacity=0.70,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.70] (123.96, 43.27) circle (  1.96);
+\path[draw=drawColor,draw opacity=0.70,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.70] (123.96, 89.07) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.70,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.70] (123.96, 45.41) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.70,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.70] (123.96, 48.98) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.70,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.70] (123.96, 48.74) circle (  1.96);
+
+\path[draw=drawColor,draw opacity=0.70,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.70] (123.96, 39.67) circle (  1.96);
 \definecolor{drawColor}{gray}{0.20}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (123.96, 73.30) -- (123.96, 85.57);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (123.96, 71.37) -- (123.96, 76.88);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (123.96, 63.82) -- (123.96, 55.13);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (123.96, 65.29) -- (123.96, 60.68);
 \definecolor{fillColor}{gray}{0.60}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (112.49, 73.30) --
-	(112.49, 63.82) --
-	(135.43, 63.82) --
-	(135.43, 73.30) --
-	(112.49, 73.30) --
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (112.49, 71.37) --
+	(112.49, 65.29) --
+	(135.43, 65.29) --
+	(135.43, 71.37) --
+	(112.49, 71.37) --
 	cycle;
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (112.49, 68.49) -- (135.43, 68.49);
+\path[draw=drawColor,line width= 1.1pt,line join=round] (112.49, 67.86) -- (135.43, 67.86);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (149.45,106.12) -- (149.45,122.35);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (149.45,106.97) -- (149.45,134.19);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (149.45, 87.88) -- (149.45, 62.14);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (149.45, 88.51) -- (149.45, 73.42);
 \definecolor{fillColor}{RGB}{230,159,0}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (137.98,106.12) --
-	(137.98, 87.88) --
-	(160.92, 87.88) --
-	(160.92,106.12) --
-	(137.98,106.12) --
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (137.98,106.97) --
+	(137.98, 88.51) --
+	(160.92, 88.51) --
+	(160.92,106.97) --
+	(137.98,106.97) --
 	cycle;
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (137.98, 99.28) -- (160.92, 99.28);
+\path[draw=drawColor,line width= 1.1pt,line join=round] (137.98,100.56) -- (160.92,100.56);
 \definecolor{drawColor}{RGB}{51,51,51}
@@
 
-\path[draw=drawColor,draw opacity=0.70,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.70] (191.94, 89.45) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.70,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.70] (191.94, 90.50) circle (  1.96);
-
-\path[draw=drawColor,draw opacity=0.70,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.70] (191.94, 53.69) circle (  1.96);
+\path[draw=drawColor,draw opacity=0.70,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.70] (191.94, 94.02) circle (  1.96);
 \definecolor{drawColor}{gray}{0.20}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (191.94, 73.09) -- (191.94, 80.70);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (191.94, 76.40) -- (191.94, 86.33);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (191.94, 67.49) -- (191.94, 60.23);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (191.94, 68.57) -- (191.94, 59.83);
 \definecolor{fillColor}{gray}{0.60}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (180.47, 73.09) --
-	(180.47, 67.49) --
-	(203.41, 67.49) --
-	(203.41, 73.09) --
-	(180.47, 73.09) --
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (180.47, 76.40) --
+	(180.47, 68.57) --
+	(203.41, 68.57) --
+	(203.41, 76.40) --
+	(180.47, 76.40) --
 	cycle;
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (180.47, 71.06) -- (203.41, 71.06);
-\definecolor{drawColor}{RGB}{51,51,51}
-\definecolor{fillColor}{RGB}{51,51,51}
+\path[draw=drawColor,line width= 1.1pt,line join=round] (180.47, 72.60) -- (203.41, 72.60);
 
-\path[draw=drawColor,draw opacity=0.70,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.70] (217.43,132.84) circle (  1.96);
-\definecolor{drawColor}{gray}{0.20}
+\path[draw=drawColor,line width= 0.6pt,line join=round] (217.43,119.36) -- (217.43,134.82);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (217.43,114.32) -- (217.43,122.03);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (217.43,103.13) -- (217.43, 86.49);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (217.43,102.67) -- (217.43, 79.18);
 \definecolor{fillColor}{RGB}{230,159,0}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (205.96,114.32) --
-	(205.96,103.13) --
-	(228.90,103.13) --
-	(228.90,114.32) --
-	(205.96,114.32) --
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (205.96,119.36) --
+	(205.96,102.67) --
+	(228.90,102.67) --
+	(228.90,119.36) --
+	(205.96,119.36) --
 	cycle;
 
-\path[draw=drawColor,line width= 1.1pt,line join=round] (205.96,109.09) -- (228.90,109.09);
+\path[draw=drawColor,line width= 1.1pt,line join=round] (205.96,112.22) -- (228.90,112.22);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 23.90, 36.70) {1.5};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 23.90, 39.37) {1.5};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 23.90, 64.76) {2.0};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 23.90, 71.11) {2.0};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 23.90, 92.82) {2.5};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 23.90,102.86) {2.5};
 
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 23.90,120.88) {3.0};
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 23.90,134.60) {3.0};
 \end{scope}

### 2021-05-12 paper/main.tex
Add some labels
Cosmetic changes
Fix some spelling mistakes

@@
 
-\section{Introduction}
+\section{Introduction}\label{sec:introduction}
 
@@
   \label{eq:primal}
-  \operatorname*{minimize}_{\beta \in \mathbb{R}^p} P(\beta; \lambda)
-  = \frac 1 2 \lVert y - X\beta \rVert_2^2 + \lambda \lVert \beta \rVert_1
+  \operatorname*{minimize}_{\beta \in \mathbb{R}^p} \left\{P(\beta; \lambda)
+  = \frac 1 2 \lVert y - X\beta \rVert_2^2 + \lambda \lVert \beta \rVert_1\right\}
 \end{equation}
@@
   \label{eq:dual}
-  \operatorname*{maximize}_{\theta \in \mathbb{R}^n} D(\theta; \lambda) =
+  \operatorname*{maximize}_{\theta \in \mathbb{R}^n} \left\{ D(\theta; \lambda) =
   \frac 12 y^T y - \frac{\lambda^2}{2} \left\lVert \theta
-  - \frac y \lambda \right\rVert_2^2
+  - \frac y \lambda \right\rVert_2^2\right\}
 \end{equation}
@@
 In the case of the lasso, strong duality holds, which means that
-\(G(\tilde\beta_\lambda, \tilde\theta_\lambda; \lambda) = 0\) for any
+\(G(\hat\beta_\lambda, \hat\theta_\lambda; \lambda) = 0\) for any
 choice of \(\lambda\).
@@
 
-To illustrate the effectiveness of this screening method,
-we consider an instance of employing look-ahead screening for fitting
-a full lasso path to the \emph{leukemia} dataset~\citep{golub1999}.
-At the first step of
-the path, the screening method discards 99.6\% of the
-predictors for the steps up to and including
-step 5. The respective figures for steps 10 and 15 are 99.3\% and 57\%.
-At step 20, however, the
-rule does the rule not discard a single predictor.
-
-In \autoref{fig:case-study}, we have visualized the screening performance
-of look-ahead screening for a random sample of 25 predictors from this
-dataset.
+To illustrate the effectiveness of this screening method, we consider an
+instance of employing look-ahead screening for fitting a full lasso path to the
+\emph{leukemia} dataset~\citep{golub1999}.  At the first step of the path, the
+screening method discards 99.6\% of the predictors for the steps up to and
+including step 5. The respective figures for steps 10 and 15 are 99.3\% and
+57\%.  At step 20, however, the rule does not discard a single predictor.  In
+\autoref{fig:case-study}, we have visualized the screening performance of
+look-ahead screening for a random sample of 25 predictors from this dataset.
 
@@
 
-As is typical for all screening methods,
-the effectiveness of look-ahead screening is strongest at the
-start of the path and diminishes as the strength of
-penalization decreases further up on the
-path. Note, however, that all of the quantities involved in the rule are
-available as a by-product of solving the problem at the previous step, which
-means that the costs of the look-ahead screening method are negligible.
+As is typical for all screening methods, the effectiveness of look-ahead
+screening is greatest at the start of the path and diminishes as the strength
+of penalization decreases later on in the path. Note, however, that all of the
+quantities involved in the rule are available as a by-product of solving the
+problem at the previous step, which means that the costs of look-ahead
+screening are diminutive.
 
@@
 solver.
-
-Throughout the experiments, we center the response vector by its mean. In
-addition, we center and scale the predictors by their means and uncorrected
+Throughout the experiments, we center the response vector by its mean, as
+well as center and scale the predictors by their means and uncorrected
 sample standard deviations respectively.
@@
 
-\section{Discussion}
+\section{Discussion}\label{sec:discussion}
 
@@
 }
+
 \bibliography{LookAheadScreening.bib}

### 2021-06-24 paper/figures/simulated-data-timings.tex
Revise paper based on reviewer comments

% Created by tikzDevice version 0.12.3.1 on 2021-06-24 15:58:06
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

\usepackage[active,tightpage,psfixbb]{preview}

\PreviewEnvironment{pgfpicture}

\setlength\PreviewBorder{0pt}
\begin{document}

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (325.21,130.09);
\begin{scope}
\path[clip] ( 27.95, 25.11) rectangle (245.47,125.59);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 27.95, 25.87) --
	(245.47, 25.87);

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 27.95, 53.62) --
	(245.47, 53.62);

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 27.95, 81.37) --
	(245.47, 81.37);

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 27.95,109.12) --
	(245.47,109.12);

\path[draw=drawColor,line width= 0.5pt,line join=round] ( 27.95, 39.75) --
	(245.47, 39.75);

\path[draw=drawColor,line width= 0.5pt,line join=round] ( 27.95, 67.50) --
	(245.47, 67.50);

\path[draw=drawColor,line width= 0.5pt,line join=round] ( 27.95, 95.25) --
	(245.47, 95.25);

\path[draw=drawColor,line width= 0.5pt,line join=round] ( 27.95,123.00) --
	(245.47,123.00);

\path[draw=drawColor,line width= 0.5pt,line join=round] ( 68.73, 25.11) --
	( 68.73,125.59);

\path[draw=drawColor,line width= 0.5pt,line join=round] (136.71, 25.11) --
	(136.71,125.59);

\path[draw=drawColor,line width= 0.5pt,line join=round] (204.68, 25.11) --
	(204.68,125.59);
\definecolor{drawColor}{RGB}{51,51,51}
\definecolor{fillColor}{RGB}{51,51,51}

\path[draw=drawColor,draw opacity=0.70,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.70] ( 55.99, 30.02) circle (  1.96);

\path[draw=drawColor,draw opacity=0.70,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.70] ( 55.99, 35.95) circle (  1.96);

\path[draw=drawColor,draw opacity=0.70,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.70] ( 55.99, 30.44) circle (  1.96);

\path[draw=drawColor,draw opacity=0.70,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.70] ( 55.99, 29.67) circle (  1.96);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 55.99, 62.12) -- ( 55.99, 70.32);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 55.99, 51.85) -- ( 55.99, 40.30);
\definecolor{fillColor}{gray}{0.60}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 44.52, 62.12) --
	( 44.52, 51.85) --
	( 67.46, 51.85) --
	( 67.46, 62.12) --
	( 44.52, 62.12) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 44.52, 58.90) -- ( 67.46, 58.90);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 81.48, 87.61) -- ( 81.48,119.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 81.48, 65.47) -- ( 81.48, 48.62);
\definecolor{fillColor}{RGB}{230,159,0}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 70.01, 87.61) --
	( 70.01, 65.47) --
	( 92.95, 65.47) --
	( 92.95, 87.61) --
	( 70.01, 87.61) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 70.01, 75.57) -- ( 92.95, 75.57);
\definecolor{drawColor}{RGB}{51,51,51}
\definecolor{fillColor}{RGB}{51,51,51}

\path[draw=drawColor,draw opacity=0.70,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.70] (123.96, 46.98) circle (  1.96);

\path[draw=drawColor,draw opacity=0.70,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.70] (123.96, 41.07) circle (  1.96);

\path[draw=drawColor,draw opacity=0.70,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.70] (123.96, 51.98) circle (  1.96);

\path[draw=drawColor,draw opacity=0.70,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.70] (123.96, 81.03) circle (  1.96);

\path[draw=drawColor,draw opacity=0.70,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.70] (123.96, 42.85) circle (  1.96);

\path[draw=drawColor,draw opacity=0.70,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.70] (123.96, 45.98) circle (  1.96);

\path[draw=drawColor,draw opacity=0.70,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.70] (123.96, 45.77) circle (  1.96);

\path[draw=drawColor,draw opacity=0.70,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.70] (123.96, 37.84) circle (  1.96);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] (123.96, 65.55) -- (123.96, 70.37);

\path[draw=drawColor,line width= 0.6pt,line join=round] (123.96, 60.24) -- (123.96, 56.21);
\definecolor{fillColor}{gray}{0.60}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (112.49, 65.55) --
	(112.49, 60.24) --
	(135.43, 60.24) --
	(135.43, 65.55) --
	(112.49, 65.55) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (112.49, 62.49) -- (135.43, 62.49);

\path[draw=drawColor,line width= 0.6pt,line join=round] (149.45, 96.67) -- (149.45,120.47);

\path[draw=drawColor,line width= 0.6pt,line join=round] (149.45, 80.54) -- (149.45, 67.34);
\definecolor{fillColor}{RGB}{230,159,0}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (137.98, 96.67) --
	(137.98, 80.54) --
	(160.92, 80.54) --
	(160.92, 96.67) --
	(137.98, 96.67) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (137.98, 91.07) -- (160.92, 91.07);
\definecolor{drawColor}{RGB}{51,51,51}
\definecolor{fillColor}{RGB}{51,51,51}

\path[draw=drawColor,draw opacity=0.70,line width= 0.4pt,line join=round,line cap=round,fill=fillColor,fill opacity=0.70] (191.94, 85.35) circle (  1.96);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] (191.94, 69.95) -- (191.94, 78.63);

\path[draw=drawColor,line width= 0.6pt,line join=round] (191.94, 63.10) -- (191.94, 55.46);
\definecolor{fillColor}{gray}{0.60}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (180.47, 69.95) --
	(180.47, 63.10) --
	(203.41, 63.10) --
	(203.41, 69.95) --
	(180.47, 69.95) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (180.47, 66.63) -- (203.41, 66.63);

\path[draw=drawColor,line width= 0.6pt,line join=round] (217.43,107.50) -- (217.43,121.02);

\path[draw=drawColor,line width= 0.6pt,line join=round] (217.43, 92.91) -- (217.43, 72.38);
\definecolor{fillColor}{RGB}{230,159,0}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (205.96,107.50) --
	(205.96, 92.91) --
	(228.90, 92.91) --
	(228.90,107.50) --
	(205.96,107.50) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (205.96,101.27) -- (228.90,101.27);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,130.09);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 23.90, 37.27) {1.5};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 23.90, 65.02) {2.0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 23.90, 92.77) {2.5};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 23.90,120.52) {3.0};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,130.09);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 68.73, 16.10) {0.1};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (136.71, 16.10) {1};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (204.68, 16.10) {6};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,130.09);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (136.71,  6.25) {Signal-to-Noise Ratio};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,130.09);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 10.70, 75.35) {Time (s)};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,130.09);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (266.20, 74.54) --
	(266.20, 76.71);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (266.20, 83.94) --
	(266.20, 86.10);
\definecolor{fillColor}{gray}{0.60}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (260.78, 76.71) rectangle (271.62, 83.94);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (260.78, 80.32) --
	(271.62, 80.32);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,130.09);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (266.20, 60.09) --
	(266.20, 62.26);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (266.20, 69.48) --
	(266.20, 71.65);
\definecolor{fillColor}{RGB}{230,159,0}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (260.78, 62.26) rectangle (271.62, 69.48);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (260.78, 65.87) --
	(271.62, 65.87);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,130.09);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at (277.92, 77.84) {Look-Ahead};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,130.09);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at (277.92, 63.39) {Standard};
\end{scope}
\end{tikzpicture}

\end{document}

### 2021-06-24 paper/main.tex
Revise paper based on reviewer comments

@@
   \thanks{%
-    \href{mailto:johan.larsson@stat.lu.se}{\url{johan.larsson@stat.lu.se}}
+    Corresponding author: \href{mailto:johan.larsson@stat.lu.se}{\url{johan.larsson@stat.lu.se}}
   }%
@@
   thereby screening predictors along the remainder of the path.
-  In experiments we show that these look-ahead screening rules improve the
-  performance of existing screening strategies.
+  In experiments we show that these look-ahead screening rules outperform the
+  active warm-start version of the Gap Safe rules.
 \end{abstract}
@@
 is the \emph{primal} objective. We let \(\hat \beta_\lambda\) be the solution to
-\eqref{eq:primal} for a given \(\lambda\) and \(\tilde
-\beta_\lambda\) an estimate of \(\hat\beta_\lambda\).\footnote{Such as
-  the current estimate in an iterative solver tasked with solving
-  \eqref{eq:primal}.}
-
-% The Karush--Kuhn--Tucker (KKT) stationarity condition for \eqref{eq:primal}
-% holds that
-% \begin{equation}
-%   \label{eq:stationarity}
-%   0 \in X^T(X\beta - y) + \lambda\partial,
-% \end{equation}
-% where \(\partial\) is the subdifferential of the \(\ell_1\)-norm, with
-% its \(j\)th element corresponding to
-% \begin{equation}
-%   \label{eq:subdifferential}
-%   \partial_j \in
-%   \begin{cases}
-%     \{\sign(\beta_j)\} & \text{if } \beta_j \neq 0 \\
-%     [-1,1]             & \text{otherwise.}
-%   \end{cases}
-% \end{equation}
+\eqref{eq:primal} for a given \(\lambda\).
 Moreover, the dual problem of \eqref{eq:primal} is
@@
   \label{eq:gap-safe-rule}
-  |X^T \tilde \theta_\lambda|_j + \lVert x_j\rVert_2
+  |X^T \theta_\lambda|_j + \lVert x_j\rVert_2
   \sqrt{\frac{1}{\lambda_*^2}
-    G(\tilde \beta_\lambda, \tilde \theta_\lambda; \lambda^*)}
+    G(\beta_\lambda, \theta_\lambda; \lambda^*)}
   < 1
@@
 \[
-  \tilde\theta_\lambda = \frac{y - X\tilde\beta_\lambda}{
-    \max\big( |X^T(y - X\tilde\beta_\lambda)|, \lambda\big)}
+  \theta_\lambda = \frac{y - X\beta_\lambda}{
+    \max\big( |X^T(y - X\beta_\lambda)|, \lambda\big)}
 \]
@@
 
-Next, observe that \eqref{eq:gap-safe-rule} is a quadratic inequality with
+Observe that \eqref{eq:gap-safe-rule} is a quadratic inequality with
 respect to \(\lambda_*\), which
@@
 \[
-  \lambda_* = \frac{-b \pm \sqrt{b^2 - 4ac}}{2a}
-\]
-where
-\[
+  \lambda_* = \frac{-b \pm \sqrt{b^2 - 4ac}}{2a} \quad \text{where} \quad
   \begin{aligned}
-    a & = \big( 1 - | x_j^T \tilde\theta_\lambda|\big)^2 -
-    \frac 12 \tilde\theta_\lambda^T \tilde\theta_\lambda \lVert x_j\rVert_2^2      \\
-    b & = \big(\tilde\theta_\lambda^T y - \lVert \tilde\beta_\lambda \rVert_1\big)
-    \lVert x_j \rVert_2^2                                                          \\
-    c & = - \frac 12 \lVert y - X\tilde\beta_\lambda\rVert_2^2
+    a & = \big( 1 - | x_j^T \theta_\lambda|\big)^2 -
+    \frac 12 \theta_\lambda^T \theta_\lambda \lVert x_j\rVert_2^2,      \\
+    b & = \big(\theta_\lambda^T y - \lVert \beta_\lambda \rVert_1\big)
+    \lVert x_j \rVert_2^2,                                                          \\
+    c & = - \frac 12 \lVert y - X\beta_\lambda\rVert_2^2
     \lVert x_j\rVert_2^2.                                                          \\
@@
 instance of employing look-ahead screening for fitting a full lasso path to the
-\emph{leukemia} dataset~\citep{golub1999}.  At the first step of the path, the
+\emph{leukemia} data set~\citep{golub1999}.  At the first step of the path, the
 screening method discards 99.6\% of the predictors for the steps up to and
@@
 \autoref{fig:case-study}, we have visualized the screening performance of
-look-ahead screening for a random sample of 25 predictors from this dataset.
+look-ahead screening for a random sample of 25 predictors from this data set.
 
@@
     20 predictors from the \emph{leukemia}
-    dataset. A blue square indicates that the corresponding predictor can
+    data set. A blue square indicates that the corresponding predictor can
     be discarded at the respective step.\label{fig:case-study}}
@@
 for the null model is less than or equal to \(10^{-6}\) and the amount of
-\emph{infeasibility}, which we define as \(\max_i\big( |c_i| -
-\lambda\big)\), as a fraction of \(\lambda_\text{max}\) is lower than or
+\emph{infeasibility}, which we define as
+\(\max_j\big( |x_j^T(y - X\beta_\lambda)| -\lambda\big)\), as a
+fraction of \(\lambda_\text{max}\) is lower than or
 equal to \(10^{-5}\).
 
-The code used in these experiments is programmed in \textsf{C++}.
-We use a combination of the \textsf{renv} R
-package and Singularity to set up a
-reproducible environment for the experiments. All
-source code
-can be found at \url{https://github.com/jolars/LookAheadScreening/}. An HPC
+Source code for the experiments, including a container to facilitate
+reproducibility, can be found at
+\url{https://github.com/jolars/LookAheadScreening/}. An HPC
 cluster node with two Intel Xeon E5-2650 v3 processors (Haswell, 20 compute
@@
 
-We
-run experiments on a design with \(n = 100\) and \(p = 50\,000\),
-drawing the rows of \(X\) i.i.d.
-from \(\mathcal{N}(0, \Sigma)\) and \(y\)
+We run experiments on a design with \(n = 100\) and \(p = 50\,000\),
+drawing the rows of \(X\) i.i.d. from \(\mathcal{N}(0, \Sigma)\) and \(y\)
 from \(\mathcal{N}(X\beta, \sigma^2I)\) with \(\sigma^2 =
@@
 \(5\) coefficients, equally spaced throughout the coefficient vector, to 1 and
-the rest to zero. Taking inspriation from \citet{hastie2020}, we
+the rest to zero. Taking inspiration from \citet{hastie2020}, we
 consider SNR values of 0.1, 1, and 6.
@@
   \caption{Standard box plots of timings to fit a full lasso path to
-    a simulated dataset with \(n = 100\), \(p = 50\,000\), and five true
+    a simulated data set with \(n = 100\), \(p = 50\,000\), and five true
     signals.}
@@
 
-\section{Discussion}\label{sec:discussion}
+\section{Discussion}%
+\label{sec:discussion}
 
-In this paper, we have presented \emph{look-ahead screening}, which is a
-novel method to screen predictors for a range of penalization values along
-the lasso regularization path using Gap Safe screening. Our results show that
-this type of screening can yield considerable improvements in performance.
+In this paper, we have presented \emph{look-ahead screening}, which is a novel
+method to screen predictors for a range of penalization values along the lasso
+regularization path using Gap Safe screening. Our results show that this type of
+screening can yield considerable improvements in performance for the standard
+lasso. For other loss functions,
+\eqref{eq:gap-safe-rule} may no longer reduce to a quadratic inequality and will
+hence require more computation. Nevertheless, we believe
+that applying these rules in these cases is feasible and likely to result
+in comparable results.
 
-The idea is general and can therefore be extended to any type of safe screening
-rule and also used in tandem with heuristic screening rules in order to avoid
-expensive KKT computations.
+Moreover, the idea is general and can therefore be extended to any type of safe
+screening rule and also used in tandem with heuristic screening rules in order
+to avoid expensive KKT computations. Finally, although we only cover one type of
+solver in our experiments, note that our screening method is
+agnostic to the solver used to solve the lasso and that we therefore expect our
+results to be generalizable.
 

### 2021-06-24 paper/revision-comments.tex
Revise paper based on reviewer comments

\PassOptionsToPackage{unicode,pdfusetitle}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}

\documentclass[english,a4paper]{article}

\usepackage{lmodern}
\usepackage{amssymb,amsmath,amsthm,mathtools,isomath}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{textcomp} % provide euro and other symbols
\usepackage{babel}

\usepackage{upquote} % straight quotes in verbatim environments
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts

\usepackage{xcolor}
\usepackage{xurl}
\usepackage{bookmark}
\usepackage{csquotes}

\usepackage{listings}

\lstset{
  basicstyle=\ttfamily, % print whole listing small
  %keywordstyle=\color{black}\bfseries\underbar, % underlined bold black keywords
  %commentstyle=\color{grey}, % white comments
  keepspaces = true % no special string spaces
}

\usepackage{hyperref}
\hypersetup{
  colorlinks=true,
  linkcolor=Maroon,
  filecolor=Maroon,
  citecolor=Blue,
  urlcolor=Blue
}

\usepackage{longtable,booktabs}

\usepackage{etoolbox}

% nice tables out of csv files
\usepackage{csvsimple}

% format units nicely
\usepackage{siunitx}

% Allow footnotes in longtable head/foot
\usepackage{footnotehyper}
\makesavenoteenv{longtable}

\usepackage{graphicx}
\usepackage{subcaption}

% tikz and pgfplots
\usepackage{pgfplots}
\pgfplotsset{width=7cm,compat=1.16}
\usepgfplotslibrary{external}
\tikzexternalize

\usepackage{pdfpages}

% algorithms
\usepackage{algorithm,algpseudocode}

% bibliography
\makeatletter
\def\blx@nowarnpolyglossia{}
\makeatother
\usepackage[style=alphabetic,backend=biber,sorting=anyt]{biblatex}
% \addbibresource{}

% \setlength{\emergencystretch}{3em} % prevent overfull lines

% nice author blocks
\usepackage[]{authblk}
\renewcommand\Affilfont{\itshape\small}

% title block
\title{Response to Referee}

\author{Johan Larsson}
\affil{The Department of Statistics, Lund University}

\date{\today}

\begin{document}

\maketitle

\noindent I would like to begin by thanking the referee for their valuable and insightful
comments on the paper. Here, I will outline all edits made to the paper based on
their comments, as well as any other changes to the paper.

\begin{displayquote}
  However, in Section 3, just one method (active warm start version of the Gap
  Safe rules) is used to compare the performance of the proposed strategy. The
  author should rephrase the last sentence of the abstract accordingly, e.g.:
  ``In experiments we show that these look-ahead screening rules outperform the
  active warm start version of the Gap Safe rules.''
\end{displayquote}
The last sentence of the abstract has been modified accordingly.

\begin{displayquote}
  Only the Gaussian case is considered. Is the method applicable to Generalized
  Linear Models?
\end{displayquote}
We have added a couple of sentences in the discussion discussing this.

\begin{displayquote}
  There are two options in the glmnet package for computing the path to Gaussian
  linear models: \texttt{type.gaussian="covariance"} and \texttt{type.gaussian="naive"}.
  Depending on the setting, these options have a large impact on timing. The
  latter can be far more efficient for p > n situations, or when p > 500. Are
  the results reported in simulations consistent under both settings?
\end{displayquote}
A sentence in the discussion has been added regarding this.

In addition to these changes, we have also replaced \(\tilde\beta\)
throughout the paper with \(\beta\), since the distinction made with the former
notation made no difference to the results.

We have moreover hade a few minor cosmetic changes to math environments,
figures, and text in order to maintain the page limit requirement. The
description of the experiment setup was also shortened somewhat for the same
reason.

\end{document}

### 2021-06-24 figures/simulated.R

@@ -5,12 +5,13 @@ library(forcats)
 library(tikzDevice)
 library(ggplot2)
 library(readr)
+library(here)
 
-source("R/utils.R")
+source(here("R", "utils.R"))
 
 theme_set(theme_minimal(base_size = 9))
 
-d1 <- read_rds("results/simulateddata.rds") %>%
+d1 <- read_rds(here("results", "simulateddata.rds")) %>%
   select(-(screened:step)) %>%
   unnest(time) %>%
   mutate(
@@ -27,8 +28,8 @@ cols <- c(
   "#0072B2", "#D55E00", "#CC79A7"
 )
 
-file <- "paper/figures/simulateddata-timings.tex"
-tikz(file, width = 4.5, height = 2, standAlone = TRUE)
+file <- here("paper", "figures", "simulated-data-timings.tex")
+tikz(file, width = 4.5, height = 1.8, standAlone = TRUE)
 ggplot(d1, aes(
   snr,
   time,
@@ -39,4 +40,4 @@ ggplot(d1, aes(
   labs(fill = NULL, x = "Signal-to-Noise Ratio", y = "Time (s)")
 dev.off()
 
-renderPdf("paper/figures/simulateddata-timings.tex")
+renderPdf(file)

### 2021-06-29 paper/main.tex
Update revision

@@
 Suppose, now, that we have solved the lasso for \(\lambda\); then
-for any given \(\lambda^* \leq \lambda\);
+for any given \(\lambda^* \leq \lambda\),
 the Gap Safe rule~\citep{ndiaye2017} discards the \(j\)th
 predictor if
-\begin{equation}
-  \label{eq:gap-safe-rule}
+\begin{equation} \label{eq:gap-safe-rule}
   |X^T \theta_\lambda|_j + \lVert x_j\rVert_2
@@
   \centering
-  \includegraphics{figures/simulateddata-timings.pdf}
+  \includegraphics{figures/simulated-data-timings.pdf}
   \caption{Standard box plots of timings to fit a full lasso path to
@@
 screening rule and also used in tandem with heuristic screening rules in order
-to avoid expensive KKT computations. Finally, although we only cover one type of
-solver in our experiments, note that our screening method is
-agnostic to the solver used to solve the lasso and that we therefore expect our
-results to be generalizable.
+to avoid expensive KKT computations. Finally, although we only cover one type
+of cyclical
+coordinate descent in our experiments, note that our screening method is
+agnostic to the solver used and that we expect the results
+hold for any solver that benefits from predictor screening.
 
